### 2013-02-18 paper/main.tex
retrieved tex

\documentclass[usenatbib]{mn2e} 
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsfig}  
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

% To highlight comments 
\usepackage{color}
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{blue}{rgb}{0.1,0.3,0.9}
\newcommand{\blue}{\color{blue}}

\usepackage[normalem]{ulem}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}

\newcommand{\LCDM}{$\Lambda$CDM~}
\newcommand{\beq}{\begin{eqnarray}}  
\newcommand{\eeq}{\end{eqnarray}}  
\newcommand{\zz}{$z\sim 3$} 
\newcommand{\apj}{ApJ}  
\newcommand{\apjs}{ApJS}  
\newcommand{\apjl}{ApJL}  
\newcommand{\aj}{AJ}  
\newcommand{\mnras}{MNRAS}  
\newcommand{\mnrassub}{MNRAS accepted}  
\newcommand{\aap}{A\&A}  
\newcommand{\aaps}{A\&AS}  
\newcommand{\araa}{ARA\&A}  
\newcommand{\nat}{Nature}  
\newcommand{\physrep}{PhR}
\newcommand{\pasp}{PASP}    
\newcommand{\pasj}{PASJ}    
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman$\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
\newcommand{\hs}{{\hspace{1mm}}}

% definition to produce a "less than or similar to" symbol
\def\lsim{~\rlap{$<$}{\lower 1.0ex\hbox{$\sim$}}}

% definition to produce a "greater than or similar to" symbol
\def\gsim{~\rlap{$>$}{\lower 1.0ex\hbox{$\sim$}}}

\begin{document}

\title[Vweb \& Tweb]{Halo alignments with large scale tidal and velocity fields}
\author[J.E. Forero-Romero and M. Dijkstra]{
\parbox[t]{\textwidth}{\raggedright 
  A.A.$^{1}$ 
  B.B.$^{1}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

\begin{abstract}

\end{abstract}
\begin{keywords}
galaxies: high-redshift - galaxies: star formation - line: formation
\end{keywords}

\section{Introduction}
\label{sec:introduction}

\citep[e.g.][]{Pritchard10}.  
%-------

\section{Theoretical Antecedents}
\label{sec:theory}

\section{The algorithms}
\label{sec:algorithms}

\begin{figure}
\includegraphics[width=0.50\textwidth]{../plots/JT256.ps}
\caption{
}
\label{fig:JT256}
\end{figure}

\section{Discussion}
\label{sec:discussion}

\section{Conclusions}
\label{sec:conclusions}

\section*{Acknowledgments}

\bibliographystyle{mn2e}
\bibliography{references}

\end{document}

### 2013-02-19 paper/main.tex
added sections

@@
 
+\section{Results}
+
+\subsection{Volume and Mass filling fractions}
+
+\subsection{Interweb Alignment}
+... We compute the pair-wise allignment between the eigenvectors in
+the two web finders.
+
+... We also compute the alignment between the eigenvectors in cells
+occupied by dark matter halos. This will be a key element in the
+interpretation of the results for halo-based allignments in the next
+sections: shape, angular momentum and peculiar velocities.
+
+\subsection{Shape Alignment}
 \begin{figure}
@@
 \end{figure}
+
+\subsection{Angular Momentum Alignment}
+
+\subsection{Peculiar velocity Alignment}
 

### 2013-02-19 paper/main.tex
outlines

@@
 
-\section{The algorithms}
+... There is abundant literature on the issue of shape and angular momentum
+aligmnent of dark matter haloe with respect to the cosmic we.
+
+... This alignment is often measured from the distribution of the
+$\cos\theta$ where $\theta$ is the angle between the two axes of
+interest.
+
+... Table 1 summarizes recent results found in the literature for
+shape and angular momentum alignment.
+
+\section{N-body simulation and halo finding}
+
+... In this paper we use groups found with a FOF halo finder.
+
+\section{The cosmic web algorithms}
 \label{sec:algorithms}
 
+\subsection{The Tidal Web}
+
+\subsection{The Velocity Web}
+
+\subsection{Numerical considerations}
+
+... In this paper we compute the cosmic web on grids of two different
+resolutions $256^3$ and $512^3$.
+
 \section{Results}
-
-\subsection{Volume and Mass filling fractions}
 
@@
 sections: shape, angular momentum and peculiar velocities.
+
+...
 

### 2013-02-24 paper/main.tex
all new plots integrated

@@
 \title[Vweb \& Tweb]{Halo alignments with large scale tidal and velocity fields}
-\author[J.E. Forero-Romero and M. Dijkstra]{
+\author[S. Contreras et al.]{
 \parbox[t]{\textwidth}{\raggedright 
-  A.A.$^{1}$ 
-  B.B.$^{1}$ 
+  Sergio Contreras$^{1}$ 
+  Jaime E. Forero-Romero$^{1}$ 
 }
@@
 
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V3.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V3.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V3.ps}
+\caption{Interweb alignment for $256^3$ grid resolution.}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V3.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V3.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V3.ps}
+\caption{Interweb alignment for $512^3$ grid resolution.}
+\end{figure*}
+
 \subsection{Shape Alignment}
-\begin{figure}
-\includegraphics[width=0.50\textwidth]{../plots/JT256.ps}
-\caption{
-}
-\label{fig:JT256}
-\end{figure}
 
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V3.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V3.ps}
+\caption{Shape alignment for the vweb at $256^3$ resolution.}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T3.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T3.ps}
+\caption{Shape alignment for the tweb at $256^3$ resolution.}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V3.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V3.ps}
+\caption{Shape alignment for the vweb at $512^3$ resolution.}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T3.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T3.ps}
+\caption{Shape alignment for the tweb at $512^3$ resolution.}
+\end{figure*}
+
+\newpage
 \subsection{Angular Momentum Alignment}
 
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V3.ps}
+\caption{Angular momentum alignment with the Vweb for $256^3$ grid resolution.}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V3.ps}
+\caption{Angular momentum alignment with the Vweb for $512^3$ grid resolution.}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T3.ps}
+\caption{Angular momentum alignment with the Tweb for $256^3$ grid resolution.}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T3.ps}
+\caption{Angular momentum alignment with the Tweb for $512^3$ grid resolution.}
+\end{figure*}
+
 \subsection{Peculiar velocity Alignment}
+
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V3.ps}
+\caption{Peculiar velocity alignment with the Vweb for $256^3$ grid resolution.}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V3.ps}
+\caption{Peculiar velocity alignment with the Vweb for $512^3$ grid resolution.}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T3.ps}
+\caption{Peculiar velocity alignment with the Tweb for $256^3$ grid resolution.}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T1.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T2.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T3.ps}
+\caption{Peculiar velocity alignment with the Tweb for $512^3$ grid resolution.}
+\end{figure*}
 

### 2013-02-26 paper/main.tex
added basic theoretical references to compare with
historical data

@@
 \begin{keywords}
-galaxies: high-redshift - galaxies: star formation - line: formation
+methods: N-body simulations, galaxies: haloes, cosmology: theory, dark matter, large-scale structure of Universe
 \end{keywords}
@@
 
-\citep[e.g.][]{Pritchard10}.  
 %-------
@@
 
+\citep{Libeskind2013} %various alignments
+\citep{Codis2012}
+\citep{Faltenbacher2009} %galaxy alignments with mocks
+\citep{Paz2008} %angular momentum alignments
+\citep{Platen2008} %alignment in voids
+\citep{AragonCalvo2007} %Spin alignment
+\citep{Lee2007}%Obs. spin alignment
+\citep{Hahn2007}% various alignments with the Tweb
+
+\begin{itemize}
+\item 
+\citep{Lee2002}%Obs. spin alignment
+Observational measurement for the alignment of galaxy spin axes with
+the local tidal shear field. For the measurement of shear, we have used
+the Point Source Catalog Redshift (PSCz) survey (a complete redshift survey
+from the IRAS Point Source Catalog) data. This was done down to a
+radial comoving distance of $\sim 150$\hMpc.
+\item
+\citep{Hatton2001} %angular momentum alignment
+DM matter only simulation. $256^3$ particles, $100$\hMpc, particle
+mass. Look for mutual alignment of angular momentum vectors, and
+alignment with structure. halos on any escale by close pair
+statistics. They don't find any evidence for a statistically significant mutual
+alignment of haloes on any scale,
+\end{itemize}
 \section{N-body simulation and halo finding}

### 2013-02-26 paper/main.tex
historical comments

@@
 \citep{Platen2008} %alignment in voids
-\citep{AragonCalvo2007} %Spin alignment
 \citep{Lee2007}%Obs. spin alignment
-\citep{Hahn2007}% various alignments with the Tweb
 
@@
 \item
+\citep{AragonCalvo2007} %Spin alignment
+The method is the Multi-scale Morphology Filter which is based on the
+Hessian matrix of the density field, where the density field is
+computed from the particle distribution using a Delaunay tesselation
+field estimatior (DTFE), which is self-adaptive. This allows them to
+identify clusters, filaments and walls.
+
+The simulation has $512^3$ particles in a cubic box of $150$\hMpc. The
+mass per particle is $2\times 10^{9}$\hMsun. 
+Halo identitification is done with the HOP algorithm. They keep halos with more
+than $50$ partices and less than $5000$, defining a mass range of
+$1-100\times 10^{11}$\hMsun.
+
+The principal
+axes of each halo are computed from the non-normalized inertia
+tensor. The inertian tensor and the angular momentum are computed with
+respect to the center of mass of the halo.
+
+They compute two angles, one with respect to the direction
+defining the filaments and the other the walls. Their results make a
+distinction between halos of more massive and less massive than
+$10^{12}$\hMsun.
+
+The halo spins tend to lie on the plane of the wall. This is stronger
+for massive halos.The effect for filaments is weaker: low mass halos
+tend to lieparallel to their host filament, while high mass halos tend
+to be perpendicular.
+
+Theres is a very strong effect for the principal axes of halos in
+filaments to be strongly correlated with the direction of the
+filaments. The minor axis tend to be perpendicular to the
+filament. This effect is stronger for larger halos.
+
+The effect in walls is less strong ,but still the minor axis tend to
+lie perpendicular to the wall, while the other axis then to lie over
+the wall. The effect is stronger for massive halos.
+
+They find that spins and shapes of dark matter halos are significantly
+correlated with each other and with the orientation of their host
+structures.
+
+\item 
+\citep{Hahn2007}% various alignments with the Tweb
+The method is the Tweb. They use three simulations each of $512^3$
+particles, with sizes $L_1=45$\hMpc, $L_2=90$\hMpc and
+$L_3=180$\hMpc, this corresponds to particle masses of $4.7, 38.0,
+300\times 10^7$\hMsun. The normalization is $\sigma_8=0.9$. Halo
+identification was done with a FOF algorithm with 0.2 times the
+interparticle distance. They consider halos of at least 300
+particles.
+
+The web is obtained for a grid of $1024^3$ cells, the density field is
+obtained with a CIC interpolation and smoothed using a Gaussian
+Kernel. In the rest of the paper all the results correspond to a
+smoothing scale of $R_{s}=2.1$\hMpc.
+
+They Report on the angle between the halo
+angular momentum vector and the eigenvector corresponding to
+perpendicular directions to the sheets and the direction of the
+filaments. This is divided in two halo populations: $5\times 10^{10} -
+1.0\times 10^{12}$ and $>10^{12}$. There is a weak antialignment in
+the case of the filaments and a stronger anti-alignment in the case of
+the sheets. For the sheets the effect is stronger for the massive
+bin. In the filaments the alignment is weak regardless of the
+mass. They do not report any other significan statistic, but recognize
+that they suffer from small-number statistics in voids).
+
+They do not see any strong dependance of the environment in the
+shape. They do not measure the shape alinment.
+
 \citep{Lee2002}%Obs. spin alignment

### 2013-02-27 paper/main.tex
new references

@@
 \citep{Libeskind2013} %various alignments
-\citep{Codis2012}
+
 \citep{Faltenbacher2009} %galaxy alignments with mocks
@@
 \begin{itemize}
+\item 
+\citep{Codis2012}
+Studies the alignment of the sping of dark matter halos realtive to
+the surrounding large scale structure and to the tidal tensor
+eigenvalues.
+
+They use a dark matter simulation with $4096^3$ DM particles in a
+cubic periodic box of $2000$\hMpc on a side, which corresponds to a
+particle mass of $7.7\times 10^9$\Msun. Halos are identified
+using a FoF algorithm with a linking legth of 0.2 keeping all halos
+with more than 40 particles, which sets the minimum halo mass to be
+$3\times 10^{11}$\Msun. In their work the particles were sampled on a
+$2048^3$ grid and the density field was smoothed with a gaussian
+fileter over a scale of $5$\hMpc corresponding to a mass of $1.9\times
+10^{14}$. The skeleton was computed over $6^{3}$ overlapping subcubes
+and then reconnected.
+
+The filament finder algorithm is based on Morse theory and defines a
+Skeleton to be the set of critical lines joining the maxima of the
+densit field through saddle points following the gradient. They also
+compute the hessinan of the potential over the smoothed density field
+to get their eigenvectors.
+
+The spin of the halo is defined as $m_{p}\sum_{i}(r_i-\bar{r})\times
+(v_i-\bar{v})$ where $\bar{r}$ is the center of mass of the halo and
+$\bar{v}$ is the average velocity.
+
+They measure the sping alignment with each one of the
+eigenvectors. With repecto to the first eigenvector $e_{1}$ there is
+antialignement for masses $M>10^{12}$\Msun and alignment for masses
+$<10^{12}$\Msun
+
 \item 
@@
 shape. They do not measure the shape alinment.
+\item
+\citep{Basilakos2006}
+Use a cosmological SPH+N-body simulation to measure the alignment of
+cluster halos with their parent supercluster. For both the cluster
+halos and parent super-cluster they define the shape via the
+non-normalized inertia tensor.  The find that strenght of the
+alignments increases with the degree of filamentarity of the
+supercluster.
 
+The simulation has $2\times 512^3$ particles in a box of side
+$500$\hMpc. The dark matter particle mass is $6.6\times
+10^{10}$\hMsun while for SPH particles is $1.2\times
+10^{10}$\hMsun. The halo finding is done with a FOF algorithm with a
+linking length of 0.17 and keep objects with more than 100 partcles.
+
+\item
 \citep{Lee2002}%Obs. spin alignment

### 2013-02-27 paper/main.tex
new references

@@
 \citep{Libeskind2013} %various alignments
-
+\citep{Libeskind2012} %varios alignments
 \citep{Faltenbacher2009} %galaxy alignments with mocks
@@
 They measure the sping alignment with each one of the
-eigenvectors. With repecto to the first eigenvector $e_{1}$ there is
-antialignement for masses $M>10^{12}$\Msun and alignment for masses
-$<10^{12}$\Msun
+eigenvectors. With repecto to the minor eigenvector $e_{1}$ there is
+antialignement for masses $M>5\times10^{12}$\Msun and alignment for masses
+$<5\times 10^{12}$\Msun. With respect to the intermediate eigenvector $e_2$
+there is a strong alignment at high masses and no alignment for low
+masses, with respecto the major eigenvector $e_{3}$ there is an
+anti-alignment signal at all masses. The results from the Skeleton
+algorithm are in perfect agreement with the results from the Tidal
+web.  The transitional mass is weakly dependent on the smoothing scale,
+varing between $1-5\times 10^{12}$\hMsun for smoothing scales between
+  $1.0-5.0$\hMpc.
 

### 2013-03-03 paper/main.tex
New Mass Relation Plots

@@
   Jaime E. Forero-Romero$^{1}$ 
+  Nelson Padilla$^{1}$ 
 }
@@
 
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/Mass/Web.ps}
+\caption{Median of the interweb alignment for the two grid resolution.}
+\end{figure*}
+
 \subsection{Shape Alignment}
@@
 
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/Mass/VWeb.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Mass/TWeb.ps}
+\caption{Median of the shape alignment for the two web  and the two grid resolution.}
+\end{figure*}
+
 \newpage
@@
 \caption{Angular momentum alignment with the Tweb for $512^3$ grid resolution.}
+\end{figure*}
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/Mass/jVWeb.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Mass/jTWeb.ps}
+\caption{Median of the angular momentum for the two web  and the two grid resolution.}
 \end{figure*}
@@
 \end{figure*}
+\begin{figure*}
+\includegraphics[width=0.30\textwidth]{../plot2/Mass/vVWeb.ps}
+\includegraphics[width=0.30\textwidth]{../plot2/Mass/vTWeb.ps}
+\caption{Median of the peculiar velocity for the two web  and the two grid resolution.}
+\end{figure*}
 

### 2013-03-13 paper/main.tex
more text on previous work

@@
 \citep{Libeskind2012} %varios alignments
+
 \citep{Faltenbacher2009} %galaxy alignments with mocks
@@
 \item
+\citep{Zhang2009}
+Study the spin and shape alignment against filaments.
+
+They use a dark matter simulation with $1024^3$ DM particles in a
+periodic box of $100$ \hMpc on a side. The particle mass is
+$6.92\times10^{7}$\hMsun. Dark matter haloes are found using a FOF
+algorithm with a linking length of 0.2 times the interparticle
+distance. Only halos with more than 500 particles are retained for
+further analysis.
+
+The angular momentum is measured with positions repect to the center
+of mass and the shape is determined using the non-normalized moment of
+inertia tensor.
+
+The environment is found using the hessian of the density. The density
+field was interpolated over a $1024^3$ grid and then smoothed with a
+Gaussian filter of scale $R_{s}2.1$\hMpc. There are two methods to
+define the direction of a filament. The first method uses the
+eigenvalues of the hessian density, howevere they define the filament
+direction with the eigenvector corresponding the single positive
+eigenvalue of the hessian. The second method used a line that
+connects the two terminal halos in a filament segment.
+
+The characterization of the alingment with the $\cos(\theta)$
+statistic. For the method that uses the eigenvectors, they find that
+the strenght of the spin alignment decreases with halo mass. For the
+shape they study the alingment of the major axis with the
+filament. The find an alignment signal in all mass bins, with an stronger
+effect for more massive halos.
+
+In a final experiment they measure the spin alignment in four
+different samples that separated by the strength of the shape
+alignment. They find that halos anticorrelated in shape, show a strong
+sping correlation going to the extreme where there is a strong spin
+anticorrelation for halos with a strong shape correlation. This means
+that the halos with strong spin alignment are not the same halos
+showing strong shape alignment.
+
+\item 
 \citep{Codis2012}
-Studies the alignment of the sping of dark matter halos realtive to
+Studies the alignment of the spin of dark matter halos relative to
 the surrounding large scale structure and to the tidal tensor

### 2013-03-15 paper/main.tex
more text on previous work

@@
 
-\citep{Libeskind2013} %various alignments
-\citep{Libeskind2012} %varios alignments
-
 \citep{Faltenbacher2009} %galaxy alignments with mocks
@@
 \begin{itemize}
+
 \item
-\citep{Zhang2009}
-Study the spin and shape alignment against filaments.
+\citep{Libeskind2013} %various alignments
+Studies shape and spin alignment with the cosmic web defined by the
+velocity shear tensor method described in this paper.
 
-They use a dark matter simulation with $1024^3$ DM particles in a
-periodic box of $100$ \hMpc on a side. The particle mass is
-$6.92\times10^{7}$\hMsun. Dark matter haloes are found using a FOF
-algorithm with a linking length of 0.2 times the interparticle
-distance. Only halos with more than 500 particles are retained for
-further analysis.
+The simulation has $2048^3$ particles in a bos of $250$\hMpc,
+corresponding to a particles mass of $1.3\times 10^{8}$\hMsun.  Halos
+are found using a FOF halo finder with $b=0.17$. The catalog only
+include halos more massiven than $3\times 10^{9}$\hMsun.
 
-The angular momentum is measured with positions repect to the center
-of mass and the shape is determined using the non-normalized moment of
-inertia tensor.
+The shape is defined from the reduced inertia tensor. Results are
+reported for three mass bins $M_{\rm vir}<10^{11.5}$\hMsun,
+$11^{11.5}<M_{\rm vir}<12^{12.5}\hMsun$ and $M_{\rm vir}>12^{12.5}\hMsun$.
 
-The environment is found using the hessian of the density. The density
-field was interpolated over a $1024^3$ grid and then smoothed with a
-Gaussian filter of scale $R_{s}2.1$\hMpc. There are two methods to
-define the direction of a filament. The first method uses the
-eigenvalues of the hessian density, howevere they define the filament
-direction with the eigenvector corresponding the single positive
-eigenvalue of the hessian. The second method used a line that
-connects the two terminal halos in a filament segment.
+THe identification of the cosmic web is done on a grid of $256^3$ with
+a gaussian smoothing of $\sim 1$\hMpc over the velocity field. The
+details of this smoothing are different from ours. This is decribed in
+detail in the Appendix.
 
-The characterization of the alingment with the $\cos(\theta)$
-statistic. For the method that uses the eigenvectors, they find that
-the strenght of the spin alignment decreases with halo mass. For the
-shape they study the alingment of the major axis with the
-filament. The find an alignment signal in all mass bins, with an stronger
-effect for more massive halos.
+The aligmnet signal of the spin is very weak while the shape alignment
+signal is very strong. The alignment is such that the eigenvector
+corresponding to the smalles eigenvalue is aligned with the major
+axis. This effect is stronger for more massive halos. 
+In other words the major axis of a halo is aligned with a filament,
+and lies on the plane that define a sheet.
 
-In a final experiment they measure the spin alignment in four
-different samples that separated by the strength of the shape
-alignment. They find that halos anticorrelated in shape, show a strong
-sping correlation going to the extreme where there is a strong spin
-anticorrelation for halos with a strong shape correlation. This means
-that the halos with strong spin alignment are not the same halos
-showing strong shape alignment.
+\item
+\citep{Trowland2013}
+
+The simulation is the millennium simulation, which has $2160^3$
+particles in a volume of $500$\hMpc on a side. This corresponds to a
+particle mass of $8.6\times 10^{8}$\hMsun. The catalog uses both halos
+and subhalos which were identified with SUBFIND. Only halos with more
+than 500 particles were kept to get a robust computation for the spin.
+
+However the analysis are reported ona box of $300$\hMpc on a
+side. Four different gaussian smoothing scales are used:
+
+The method to define the filamentary structure is based on the
+eigenvalues of the hessian of the density.
 
@@
   $1.0-5.0$\hMpc.
+
+\item
+\citep{Zhang2009}
+Study the spin and shape alignment against filaments.
+
+They use a dark matter simulation with $1024^3$ DM particles in a
+periodic box of $100$ \hMpc on a side. The particle mass is
+$6.92\times10^{7}$\hMsun. Dark matter haloes are found using a FOF
+algorithm with a linking length of 0.2 times the interparticle
+distance. Only halos with more than 500 particles are retained for
+further analysis.
+
+The angular momentum is measured with positions repect to the center
+of mass and the shape is determined using the non-normalized moment of
+inertia tensor.
+
+The environment is found using the hessian of the density. The density
+field was interpolated over a $1024^3$ grid and then smoothed with a
+Gaussian filter of scale $R_{s}2.1$\hMpc. There are two methods to
+define the direction of a filament. The first method uses the
+eigenvalues of the hessian density, howevere they define the filament
+direction with the eigenvector corresponding the single positive
+eigenvalue of the hessian. The second method used a line that
+connects the two terminal halos in a filament segment.
+
+The characterization of the alingment with the $\cos(\theta)$
+statistic. For the method that uses the eigenvectors, they find that
+the strenght of the spin alignment decreases with halo mass. For the
+shape they study the alingment of the major axis with the
+filament. The find an alignment signal in all mass bins, with an stronger
+effect for more massive halos.
+
+In a final experiment they measure the spin alignment in four
+different samples that separated by the strength of the shape
+alignment. They find that halos anticorrelated in shape, show a strong
+sping correlation going to the extreme where there is a strong spin
+anticorrelation for halos with a strong shape correlation. This means
+that the halos with strong spin alignment are not the same halos
+showing strong shape alignment.
 
@@
 shape. They do not measure the shape alinment.
+
+\item
+\citep{Brunino2007}
+
 \item

### 2013-04-08 paper/main.tex
more text on other people's results

@@
 
-\title[Vweb \& Tweb]{Halo alignments with large scale tidal and velocity fields}
+\title[Vweb \& Tweb]{Halo alignments with large scale tidal and
+  velocity fields} 
 \author[S. Contreras et al.]{
@@
 \begin{keywords}
-methods: N-body simulations, galaxies: haloes, cosmology: theory, dark matter, large-scale structure of Universe
+methods: N-body simulations, galaxies: haloes, cosmology: theory, dark
+matter, large-scale structure of Universe 
 \end{keywords}
@@
 \citep{Lee2007}%Obs. spin alignment
+
+\begin{table}
+\begin{tabular}{llll}
+Author & Web Method & Halo Finder & SPIN \\
+\end{tabular}
+SPIN
+\end{table}
 
@@
 and subhalos which were identified with SUBFIND. Only halos with more
-than 500 particles were kept to get a robust computation for the spin.
-
-However the analysis are reported ona box of $300$\hMpc on a
-side. Four different gaussian smoothing scales are used:
+than 500 particles were kept to get a robust computation for the
+spin. For each halo the spin is defined as the sum of the angular momentum
+of each particle with respect to the center of mass.
 
 The method to define the filamentary structure is based on the
-eigenvalues of the hessian of the density.
+eigenvalues of the hessian of the density.However the analysis are
+reported ona box of $300$\hMpc on a side. Four different gaussian
+smoothing scales are used: $2.0$, $3.0$ and $5.0$\hMpc.
+
+The authors report a slight alignment signal of spin against the
+principal filament axis. By fitting the following functional form to
+the $\cos(\theta)$ distribution
+
+\begin{equation}
+P(\cos\theta) =
+(1-c)\sqrt{1+\frac{c}{2}}\left[1-c\left(1-\frac{3}{2}\cos^{2}\theta \right)\right]^{-3/2},
+\end{equation}
+
+they are able to quantify the degree of alignment ($c<0$) or
+antialignment ($c>0$).  This parameterization is based on theoretical
+expectactions of Tidal Torque Theory (TTT) \citep{Lee2005}. At $z=0$, the reported
+value is $c = −0.035 \pm 0.004$, where the uncertainty was calculated
+using bootstraping and resampling.
+
+When the halo sample is divided between low mass and high mass halos
+with a transition scale $M_{\star}=5.9\times 10^{12}$\Msun, there is
+an anti-alignment above this mass and an alignment below it.
 

### 2013-04-12 paper/main.tex
new two last figures

@@
 \end{figure*}
+
 \begin{figure*}
@@
 
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T3.ps}
+%\caption{Peculiar velocity alignment with the Tweb for $512^3$ grid resolution.}
+%\end{figure*}
+
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/Mass/vVWeb.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Mass/vTWeb.ps}
+%\caption{Median of the peculiar velocity for the two web  and the two grid resolution.}
+%\end{figure*}
+
 \begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T3.ps}
-\caption{Peculiar velocity alignment with the Tweb for $512^3$ grid resolution.}
+\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_256.ps}
+\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_256.ps}
+\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_256.ps}
+\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_256.ps}
+\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_256.ps}
+\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_256.ps}
+\caption{From top to bottom: Shape, J, velocities. 256 resolution. Left Tweb, right Vweb}
 \end{figure*}
+
 \begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/Mass/vVWeb.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Mass/vTWeb.ps}
-\caption{Median of the peculiar velocity for the two web  and the two grid resolution.}
+\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_512.ps}
+\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_512.ps}
+\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_512.ps}
+\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_512.ps}
+\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_512.ps}
+\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_512.ps}
+\caption{From top to bottom: Shape, J, velocities. 512 resolution. Left Tweb, right Vweb}
 \end{figure*}
+
+Possible conclusion.
+Prolateness follow concentration.
+In the Tweb Angular momentum alignment is influenced by spin at higher masses.
+In the Vweb angular momentum alginment is influenced by all factors.
+In the peculiar velocity alginment only spin seemss to have an effect.
 

### 2013-05-01 paper/main.tex
adding text to the tables

@@
 
-... Table 1 summarizes recent results found in the literature for
-shape and angular momentum alignment.
+... Table 1 and Table 2 summariz recent results found in the literature for
+shape and angular momentum alignment, respectively.
 
@@
 \begin{table}
-\begin{tabular}{llll}
-Author & Web Method & Halo Finder & SPIN \\
+\begin{tabular}{lllll}
+Author & Web Method & Halo Finder & Major Axis & Correlation\\
 \end{tabular}
-SPIN
+SHAPE
 \end{table}
+
+TABLA
+\begin{table*}
+\begin{tabular}{ccccccc}\hline\hline
+Author & Web Method & Halo Finder & Spatial Scale & Test Direction &
+Alignment & Mass dependence\\\hline
+\cite{Hahn2007} & Tidal Web & FOF & $2.1$\hMpc & along
+the filament & $-$& none\\
+\cite{Hahn2007} & Tidal Web & FOF & $2.1$\hMpc &
+perpendicular to sheet & $-$$-$ & stronger $>10^{12}$\hMsun\\
+\cite{Hatton2001} & Neighbors$^1$ & FOF & & & 0\\\hline\hline
+\end{tabular}\\
+\caption{Summary of previous theoretical results.
+NOTES:
+$^1$ They do not use a web finder method. They look for correlations
+with neightborig structures on any escale.
+Angular Momentum}
+\end{table*}
 
@@
 DM matter only simulation. $256^3$ particles, $100$\hMpc, particle
-mass. Look for mutual alignment of angular momentum vectors, and
-alignment with structure. halos on any escale by close pair
-statistics. They don't find any evidence for a statistically significant mutual
-alignment of haloes on any scale,
+mass.
+Look for alignment of angular momentum vectors with neighbohring structures or other massive structures.
+They match halos using close pair statistics.
+They do not find any evidence for a statistically significant mutual alignment of halos on any escale.
 \end{itemize}

### 2013-05-15 paper/main.tex
extending the table with the summary

@@
 \begin{table*}
-\begin{tabular}{ccccccc}\hline\hline
-Author & Web Method & Halo Finder & Spatial Scale & Test Direction &
+\begin{tabular}{cccccc}\hline\hline
+Author & Web Method & Spatial Scale & Test Direction &
 Alignment & Mass dependence\\\hline
-\cite{Hahn2007} & Tidal Web & FOF & $2.1$\hMpc & along
+
+\cite{AragonCalvo2007} & Hessian density field & - &
+perpendicular to sheet & $-$$-$ & $>10^{12}$\hMsun\\
+
+& & - &
+perpendicular to sheet & $-$ & $<10^{12}$\hMsun\\
+
+& & - &
+along the filament& $-$ & $>10^{12}$\hMsun\\
+
+& & - &
+along the filament& $+$ & $<10^{12}$\hMsun\\
+
+\cite{Hahn2007} & Tidal Web & $2.1$\hMpc & along
 the filament & $-$& none\\
-\cite{Hahn2007} & Tidal Web & FOF & $2.1$\hMpc &
+
+& &  $2.1$\hMpc &
 perpendicular to sheet & $-$$-$ & stronger $>10^{12}$\hMsun\\
-\cite{Hatton2001} & Neighbors$^1$ & FOF & & & 0\\\hline\hline
+
+\cite{Hatton2001} & Neighbors$^1$ &  & & 0\\\hline\hline
+
 \end{tabular}\\
@@
 reported for three mass bins $M_{\rm vir}<10^{11.5}$\hMsun,
-$11^{11.5}<M_{\rm vir}<12^{12.5}\hMsun$ and $M_{\rm vir}>12^{12.5}\hMsun$.
+$11^{11.5}<M_{\rm vir}<12^{12.5}\hMsun$ and $M_{\rm
+  vir}>12^{12.5}\hMsun$.
 
-THe identification of the cosmic web is done on a grid of $256^3$ with
-a gaussian smoothing of $\sim 1$\hMpc over the velocity field. The
-details of this smoothing are different from ours. This is decribed in
-detail in the Appendix.
+The identification of the cosmic web is done on a grid of $256^3$ with
+a gaussian smoothing of $\sim 1$\hMpc over the velocity field. We
+define this velocity field as the ratio of a momentum density to the
+matter density field. The details of this approach are described in
+the Appendix .
 
@@
 
-The simulation is the millennium simulation, which has $2160^3$
+The simulation is the millennium run, which has $2160^3$
 particles in a volume of $500$\hMpc on a side. This corresponds to a
@@
 than 500 particles were kept to get a robust computation for the
-spin. For each halo the spin is defined as the sum of the angular momentum
-of each particle with respect to the center of mass.
+spin. For each halo the spin is defined as the sum of the angular
+momentum of each particle with respect to the center of mass.
 

### 2013-05-16 paper/main.tex
complete table for the spin alignment

@@
 \begin{table*}
+SPIN
 \begin{tabular}{cccccc}\hline\hline
-Author & Web Method & Spatial Scale & Test Direction &
+Author & Web Method & Spatial Scale & Along &
 Alignment & Mass dependence\\\hline
 
+\cite{Libeskind2013} & V-Web & $1 \hMpc$ & 
+filament &$-$ & $>10^{12}$\hMsun\\
+
+&   & & 
+filament &$+$ & $<10^{12}$\hMsun\\
+
+&   & & 
+wall & $++$ & all masses\\
+
+\cite{Trowland2013} & Hessian density & $2-5\hMpc$ & 
+filament & $-$ & $> 5\times 10^{12}$\hMsun\\
+&   & & 
+filament & $+$ & $< 5\times 10^{12}$\hMsun\\
+
+\cite{Codis2012} & Morse Theory \& Tidal Web & $1-5\hMpc$ & 
+filament & $--$ & $>10^{12}$\hMsun \\
+
+&   & & 
+filament & $++$ & $<10^{12}$\hMsun \\
+
+& & & 
+wall & $++$ & all masses\\
+
+\cite{Zhang2009}  & Hessian density field &  $2.1$\hMpc & 
+filament & $++$ & only if anticorrelated with shape\\
+
+& &  & 
+filament & $--$ & only if correlated with shape\\
+
 \cite{AragonCalvo2007} & Hessian density field & - &
-perpendicular to sheet & $-$$-$ & $>10^{12}$\hMsun\\
+wall & $++$ & $>10^{12}$\hMsun\\
 
 & & - &
-perpendicular to sheet & $-$ & $<10^{12}$\hMsun\\
+wall & $+$ & $<10^{12}$\hMsun\\
 
 & & - &
-along the filament& $-$ & $>10^{12}$\hMsun\\
+filament& $-$ & $>10^{12}$\hMsun\\
 
 & & - &
-along the filament& $+$ & $<10^{12}$\hMsun\\
+filament& $+$ & $<10^{12}$\hMsun\\
 
-\cite{Hahn2007} & Tidal Web & $2.1$\hMpc & along
-the filament & $-$& none\\
+\cite{Hahn2007} & Tidal Web & $2.1$\hMpc & filament & $-$& none\\
 
 & &  $2.1$\hMpc &
-perpendicular to sheet & $-$$-$ & stronger $>10^{12}$\hMsun\\
-
-\cite{Hatton2001} & Neighbors$^1$ &  & & 0\\\hline\hline
+wall & $++$ & stronger $>10^{12}$\hMsun\\\hline \hline
 
@@
 \caption{Summary of previous theoretical results.
-NOTES:
-$^1$ They do not use a web finder method. They look for correlations
-with neightborig structures on any escale.
 Angular Momentum}
@@
 
-The simulation has $2048^3$ particles in a bos of $250$\hMpc,
+The simulation has $2048^3$ particles in a box of $250$\hMpc,
 corresponding to a particles mass of $1.3\times 10^{8}$\hMsun.  Halos
@@
 The aligmnet signal of the spin is very weak while the shape alignment
-signal is very strong. The alignment is such that the eigenvector
-corresponding to the smalles eigenvalue is aligned with the major
+signal is very strong. The shape alignment is such that the eigenvector
+corresponding to the smallest eigenvalue is aligned with the major
 axis. This effect is stronger for more massive halos. 
 In other words the major axis of a halo is aligned with a filament,
-and lies on the plane that define a sheet.
+and lies on the plane that define a sheet. However the spin is
+antialgined with the filament for massive halos and weakly aligned for
+low mass halos.
 
@@
 field was interpolated over a $1024^3$ grid and then smoothed with a
-Gaussian filter of scale $R_{s}2.1$\hMpc. There are two methods to
+Gaussian filter of scale $R_{s} = 2.1$\hMpc. There are two methods to
 define the direction of a filament. The first method uses the

### 2013-05-20 paper/main.tex
more text on the historical summary

@@
 
-\citep{Faltenbacher2009} %galaxy alignments with mocks
-\citep{Paz2008} %angular momentum alignments
-\citep{Platen2008} %alignment in voids
-\citep{Lee2007}%Obs. spin alignment
-
 \begin{table}
@@
 Alignment & Mass dependence\\\hline
+
+\citep{Faltenbacher2009} %galaxy alignments with mocks
+
+The tidal connection between voids in simulations \citep{Platen2008},
+the alignment of observed galaxies with the inferred tidal
+field\citep{Lee2007,Jones2010}
 
@@
 P(\cos\theta) =
-(1-c)\sqrt{1+\frac{c}{2}}\left[1-c\left(1-\frac{3}{2}\cos^{2}\theta \right)\right]^{-3/2},
+(1-c)\sqrt{1+\frac{c}{2}}\left[1-c\left(1-\frac{3}{2}\cos^{2}\theta
+  \right)\right]^{-3/2}, 
 \end{equation}
@@
 antialignment ($c>0$).  This parameterization is based on theoretical
-expectactions of Tidal Torque Theory (TTT) \citep{Lee2005}. At $z=0$, the reported
-value is $c = −0.035 \pm 0.004$, where the uncertainty was calculated
-using bootstraping and resampling.
+expectactions of Tidal Torque Theory (TTT) \citep{Lee2005}. At $z=0$,
+the reported value is $c = −0.035 \pm 0.004$, where the uncertainty
+was calculated using bootstraping and resampling.
 
@@
 \item
-\citep{AragonCalvo2007} %Spin alignment
+\citep{Paz2008} %angular momentum alignments
+Nelson? Puedes hacer un resumen?
+
+\item 
+\citep{AragonCalvo2007} %angular momentum alignment
 The method is the Multi-scale Morphology Filter which is based on the
@@
 \citep{Brunino2007}
+Uses a DM only N-body simulation (the Millennium Run) to study the
+shape and angular momentum alignment with respect to large
+cosmological voids.
+
+The voids are found with a spherical void finder. This algorithm first
+looks for potential void centers in the underdense regions of the
+simulation. These positions define the centers of spheres that are
+empty of halos above a given mass threshold. Only voids with radius
+larger than $10$\hMpc were considered for further analysis.
+
+Halos were identified by linking particles with density exceeding 900
+times the background density in order to keep the analysis of shape
+and angular momentum on the core of the halo. Only halos with masses
+in the range $8.6\times 10^{11}\hMsun < M_{\mathrm h}< 8.6\times
+10^{12}\hMsun$ were included analized to measure their angular
+momentum and the inertia tensor, both in a non-normalized way.
+
+For the purpose of measuring alignments a second cut is imposed
+whereby only halos within a shell of radius $R_{\mathrm void}<r<1.05R_{\mathrm
+void}$. The alignment is then measured between the vector connecting
+the center of the void to the halo in question and the vector of
+interest.
+
+The results show that there is a strong alignment of halo shape in
+such a way that the major axis is parallel to the shell surrounding
+the void. In the case of angular momentum there is not a significant
+signal for alignment.
 

### 2013-05-21 paper/main.tex
finished historical review + shape table

@@
 
+The tidal connection between voids in simulations \citep{Platen2008},
+the alignment of observed galaxies with the inferred tidal
+field\citep{Lee2007,Jones2010}. There are other kind of alignment
+statistics based on modifications of the correlation
+\citep{Paz2008,Faltenbacher2009} that go beyond a local computation
+and therefore are not reviewed in detail in this paper.
+
 \begin{table}
@@
 
-TABLA
 \begin{table*}
-SPIN
 \begin{tabular}{cccccc}\hline\hline
@@
 
-\citep{Faltenbacher2009} %galaxy alignments with mocks
+\cite{Libeskind2013} & V-Web & $1 \hMpc$ & 
+filament &$++$ & $>10^{12}$\hMsun\\
 
-The tidal connection between voids in simulations \citep{Platen2008},
-the alignment of observed galaxies with the inferred tidal
-field\citep{Lee2007,Jones2010}
+&   & & 
+filament &$+$ & $<10^{12}$\hMsun\\
+
+&   & & 
+wall & $++$ & all masses\\
+
+\cite{Zhang2009}  & Hessian density field &  $2.1$\hMpc & 
+filament & $++$ & $>10^{12}\hMsun$\\
+
+& &  & 
+filament & $+$ & $<10^{12}\hMsun$\\
+
+\cite{AragonCalvo2007} & Hessian density field & - &
+wall & $++$ & $>10^{12}$\hMsun\\
+
+& & - &
+wall & $+$ & $<10^{12}$\hMsun\\
+
+& & - &
+filament& $++$ & $>10^{12}$\hMsun\\
+
+& & - &
+filament& $+$ & $<10^{12}$\hMsun\\\hline \hline
+
+\end{tabular}\\
+\caption{Summary of previous theoretical results.
+Shape. Indicates the alignment of the halo's major axis along a
+filament or a sheet.} 
+\end{table*}
+
+\begin{table*}
+\begin{tabular}{cccccc}\hline\hline
+Author & Web Method & Spatial Scale & Along &
+Alignment & Mass dependence\\\hline
 
@@
 
-\end{tabular}\\
+\end{tabular}
 \caption{Summary of previous theoretical results.
@@
 \item 
-\citep{Paz2008} %angular momentum alignments
-Nelson? Puedes hacer un resumen?
-
-\item 
 \citep{AragonCalvo2007} %angular momentum alignment
@@
 The simulation has $512^3$ particles in a cubic box of $150$\hMpc. The
-mass per particle is $2\times 10^{9}$\hMsun. 
-Halo identitification is done with the HOP algorithm. They keep halos with more
-than $50$ partices and less than $5000$, defining a mass range of
-$1-100\times 10^{11}$\hMsun.
+mass per particle is $2\times 10^{9}$\hMsun.  Halo identitification is
+done with the HOP algorithm. They keep halos with more than $50$
+partices and less than $5000$, defining a mass range of$1-100\times
+10^{11}$\hMsun.
 
-The principal
-axes of each halo are computed from the non-normalized inertia
-tensor. The inertian tensor and the angular momentum are computed with
-respect to the center of mass of the halo.
+The principal axes of each halo are computed from the non-normalized
+inertia tensor. The inertian tensor and the angular momentum are
+computed with respect to the center of mass of the halo.
 
@@
 DM matter only simulation. $256^3$ particles, $100$\hMpc, particle
-mass.
-Look for alignment of angular momentum vectors with neighbohring structures or other massive structures.
-They match halos using close pair statistics.
-They do not find any evidence for a statistically significant mutual alignment of halos on any escale.
+mass. Look for alignment of angular momentum vectors with neighbohring
+structures or other massive structures. They match halos using close
+pair statistics. They do not find any evidence for a statistically
+significant mutual alignment of halos on any escale. 
 \end{itemize}

### 2013-06-07 paper/main.tex
3 new paragraphs

@@
 
-\title[Vweb \& Tweb]{Halo alignments with large scale tidal and
-  velocity fields} 
+\title[Vweb \& Tweb]{Cosmic web correlations with the shape, spin and
+  peculiar velocties of dark matter halos}  
 \author[S. Contreras et al.]{
@@
 
-... In this paper we use groups found with a FOF halo finder.
+In this paper we use groups found with a FOF halo finder.
 
@@
 \label{sec:algorithms}
+We use two algorithms to define the cosmic web on cosmological N-body
+simulations. Both are based on the same algorithmic principle, which
+is determining locally a symmetric tensor which can be diagonalized to yield
+three real eigenvalues $\lambda_1>\lambda_2>\lambda_3$ and their
+corresponding eigenvectors ${\bf e}_{1}$, ${\bf e}_2$ and ${\bf
+  e}_3$. This allows for a local classification into one of the
+following four categories: void, sheet, filament and peak depending
+whether the number of eigenvalues larger than a given threshold
+$\lambda_{th}$ is $3$, $2$, $1$ or $0$, respectively.
 
-\subsection{The Tidal Web}
+We use two different symmetric tensors. The first is the shear tensor,
+defined as the hessian of the gravitational potential, normalized in
+such a way as to be dimensionless:
 
-\subsection{The Velocity Web}
+\begin{equation}
+T_{\alpha\beta} = \frac{\partial^2\phi}{\partial
+  r_{\alpha}\partial r_{\beta}}, 
+\end{equation}
+where $\phi$ is the gravitational potential rescaled by a factor $4\pi
+G\bar{\rho}=3/2\Omega_m H_{0}^2$ in such a way that the Poission
+equation can be written as:
+
+\begin{equation}
+\nabla^{2}\phi  = \delta, 
+\end{equation}
+
+where $\delta$ is the matter overdensity, $\bar{\rho}$ is the average
+matter density, $H_{0}$ is the Hubble constant at present time and
+$\Omega_m$ is the matter density parameter.
+
+The second tensor is the velocity shear:
+
+\begin{equation}
+\Sigma_{\alpha\beta} = -\frac{1}{2H_{0}}\left(\frac{\partial
+  v_{\alpha}}{\partial r_{\beta}}+ \frac{\partial v_{\beta}}{\partial
+  r_{\alpha}}\right) 
+\end{equation}
 
@@
 
-... In this paper we compute the cosmic web on grids of two different
-resolutions $256^3$ and $512^3$.
+In this paper we compute the cosmic web on grids of two different
+resolutions $256^3$ and $512^3$...
 
@@
 
+\subsection{Mass dependency and other conditions for stronger alignment}
+
+We wish to understand what other selection criteria on halo
+properties can produce a stronger local alignment for the shape, spin
+and peculiar velocities. We split the halo population into low and
+high mass halos imposing a cut at $M_{\rm halo}=10^{11}$\hMsun. This
+allows us to have robust statistics on the high mass end. We have also
+computed these results for a cut at $M_{\rm halo}=10^{12}$\hMsun and
+checked that the results we report below are not affected by this
+change.
+
+For each mass interval we perform cuts in the following properties:
+spin, concentration, triaxiallity, circularity  and density. We
+measure the web alignments in two sets, each one including the $30\%$
+of halos in the lower/higher end of the corresponding property.
+
 \section{Discussion}

### 2013-07-11 paper/main.tex
removing redundant plots

@@
 \newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}
-\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
-\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
+        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
+\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
+        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
 \newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
@@
 
-\begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V3.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V3.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V3.ps}
-\caption{Interweb alignment for $256^3$ grid resolution.}
-\end{figure*}
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V3.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V3.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V3.ps}
+%\caption{Interweb alignment for $256^3$ grid resolution.}
+%\end{figure*}
 
-\begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V3.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V3.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V3.ps}
-\caption{Interweb alignment for $512^3$ grid resolution.}
-\end{figure*}
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V3.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V3.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V3.ps}
+%\caption{Interweb alignment for $512^3$ grid resolution.}
+%\end{figure*}
 
-\begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/Mass/Web.ps}
-\caption{Median of the interweb alignment for the two grid resolution.}
-\end{figure*}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{../plot2/Mass/Web.ps}
+\caption{Median of the interweb alignment for the two grid
+  resolutions as a function of the dark matter mass corresponding to
+  the halos where the measurement was made. The error bars indicate
+  the lower and upper quartiles (Figure in color in the web version).} 
+\end{figure}
 
@@
 \begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V3.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V3.ps}
-\caption{Shape alignment for the vweb at $256^3$ resolution.}
+\includegraphics[width=0.48\textwidth]{../plot2/Mass/VWeb.ps}
+\includegraphics[width=0.48\textwidth]{../plot2/Mass/TWeb.ps}
+\includegraphics[width=0.48\textwidth]{../plot2/Mass/VWebV2.ps}
+\includegraphics[width=0.48\textwidth]{../plot2/Mass/TWebV2.ps}
+\caption{Median of $\cos\theta$ quantifying the shape alignment for
+  the Vweb (left) and the Tweb (right) at two different grid
+  resolutions. In the upper (lower) panels the angle $\theta$ is
+  measured between the halo minor (major) axis and the first (third)
+  eigenvector.} 
 \end{figure*}
 
-\begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T3.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T3.ps}
-\caption{Shape alignment for the tweb at $256^3$ resolution.}
-\end{figure*}
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V3.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V3.ps}
+%\caption{Shape alignment for the vweb at $256^3$ resolution.}
+%\end{figure*}
 
-\begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V3.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V3.ps}
-\caption{Shape alignment for the vweb at $512^3$ resolution.}
-\end{figure*}
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T3.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T3.ps}
+%\caption{Shape alignment for the tweb at $256^3$ resolution.}
+%\end{figure*}
 
-\begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T3.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T3.ps}
-\caption{Shape alignment for the tweb at $512^3$ resolution.}
-\end{figure*}
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V3.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V3.ps}
+%\caption{Shape alignment for the vweb at $512^3$ resolution.}
+%\end{figure*}
 
-\begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/Mass/VWeb.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Mass/TWeb.ps}
-\caption{Median of the shape alignment for the two web  and the two grid resolution.}
-\end{figure*}
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T3.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T3.ps}
+%\caption{Shape alignment for the tweb at $512^3$ resolution.}
+%\end{figure*}
 
@@
 
-\begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V3.ps}
-\caption{Angular momentum alignment with the Vweb for $256^3$ grid resolution.}
-\end{figure*}
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V3.ps}
+%\caption{Angular momentum alignment with the Vweb for $256^3$ grid resolution.}
+%\end{figure*}
+
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V3.ps}
+%\caption{Angular momentum alignment with the Vweb for $512^3$ grid resolution.}
+%\end{figure*}
+
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T3.ps}
+%\caption{Angular momentum alignment with the Tweb for $256^3$ grid resolution.}
+%\end{figure*}
+
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T3.ps}
+%\caption{Angular momentum alignment with the Tweb for $512^3$ grid resolution.}
+%\end{figure*}
 
 \begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V3.ps}
-\caption{Angular momentum alignment with the Vweb for $512^3$ grid resolution.}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T3.ps}
-\caption{Angular momentum alignment with the Tweb for $256^3$ grid resolution.}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T3.ps}
-\caption{Angular momentum alignment with the Tweb for $512^3$ grid resolution.}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/Mass/jVWeb.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Mass/jTWeb.ps}
-\caption{Median of the angular momentum for the two web  and the two grid resolution.}
+\includegraphics[width=0.48\textwidth]{../plot2/Mass/jVWeb.ps}
+\includegraphics[width=0.48\textwidth]{../plot2/Mass/jTWeb.ps}
+\includegraphics[width=0.48\textwidth]{../plot2/Mass/jVWebV2.ps}
+\includegraphics[width=0.48\textwidth]{../plot2/Mass/jTWebV2.ps}
+\caption{Median of $\cos\theta$ quantifying the angular momentum
+  alingment for the Vweb (left) and the Tweb (right) at two different
+  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
+  measured between the first (third) eivenvector and the angular
+  momentum vector.} 
 \end{figure*}
@@
 \subsection{Peculiar velocity Alignment}
+
+\begin{figure*}
+\includegraphics[width=0.48\textwidth]{../plot2/Mass/vVWeb.ps}
+\includegraphics[width=0.48\textwidth]{../plot2/Mass/vTWeb.ps}
+\includegraphics[width=0.48\textwidth]{../plot2/Mass/vVWebV2.ps}
+\includegraphics[width=0.48\textwidth]{../plot2/Mass/vTWebV2.ps}
+\caption{Median of $\cos\theta$ quantifying the peculiar velocity
+  alignment with the Vweb (left) and the Tweb (right) at two different
+  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
+  measured between the first (third) eivenvector and the peculiar
+  velocity of each halo.} 
+\end{figure*}
 

### 2013-07-11 paper/main.tex
reduced the total number of figures

@@
 \def\ea{\end{eqnarray}}
-
 % To highlight comments 
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{../plot2/Mass/Web.ps}
+\includegraphics[width=0.45\textwidth]{../plot2/Mass/Web.pdf}
 \caption{Median of the interweb alignment for the two grid
@@
 \begin{figure*}
-\includegraphics[width=0.48\textwidth]{../plot2/Mass/VWeb.ps}
-\includegraphics[width=0.48\textwidth]{../plot2/Mass/TWeb.ps}
-\includegraphics[width=0.48\textwidth]{../plot2/Mass/VWebV2.ps}
-\includegraphics[width=0.48\textwidth]{../plot2/Mass/TWebV2.ps}
+\includegraphics[width=0.45\textwidth]{../plot2/Mass/VWeb.pdf}
+\includegraphics[width=0.45\textwidth]{../plot2/Mass/TWeb.pdf}
+\includegraphics[width=0.45\textwidth]{../plot2/Mass/VWebV2.pdf}
+\includegraphics[width=0.45\textwidth]{../plot2/Mass/TWebV2.pdf}
 \caption{Median of $\cos\theta$ quantifying the shape alignment for
@@
 \begin{figure*}
-\includegraphics[width=0.48\textwidth]{../plot2/Mass/jVWeb.ps}
-\includegraphics[width=0.48\textwidth]{../plot2/Mass/jTWeb.ps}
-\includegraphics[width=0.48\textwidth]{../plot2/Mass/jVWebV2.ps}
-\includegraphics[width=0.48\textwidth]{../plot2/Mass/jTWebV2.ps}
+\includegraphics[width=0.45\textwidth]{../plot2/Mass/jVWeb.pdf}
+\includegraphics[width=0.45\textwidth]{../plot2/Mass/jTWeb.pdf}
+\includegraphics[width=0.45\textwidth]{../plot2/Mass/jVWebV2.pdf}
+\includegraphics[width=0.45\textwidth]{../plot2/Mass/jTWebV2.pdf}
 \caption{Median of $\cos\theta$ quantifying the angular momentum
@@
 \begin{figure*}
-\includegraphics[width=0.48\textwidth]{../plot2/Mass/vVWeb.ps}
-\includegraphics[width=0.48\textwidth]{../plot2/Mass/vTWeb.ps}
-\includegraphics[width=0.48\textwidth]{../plot2/Mass/vVWebV2.ps}
-\includegraphics[width=0.48\textwidth]{../plot2/Mass/vTWebV2.ps}
+\includegraphics[width=0.45\textwidth]{../plot2/Mass/vVWeb.pdf}
+\includegraphics[width=0.45\textwidth]{../plot2/Mass/vTWeb.pdf}
+\includegraphics[width=0.45\textwidth]{../plot2/Mass/vVWebV2.pdf}
+\includegraphics[width=0.45\textwidth]{../plot2/Mass/vTWebV2.pdf}
 \caption{Median of $\cos\theta$ quantifying the peculiar velocity
@@
   grid resolutions. In the upper (lower)  panels the angle $\theta$ is
-  measured between the first (third) eivenvector and the peculiar
-  velocity of each halo.} 
+  measured between the first (third) eivenvector and a halo's peculiar
+  velocity.} 
 \end{figure*}
 
-\begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V3.ps}
-\caption{Peculiar velocity alignment with the Vweb for $256^3$ grid resolution.}
-\end{figure*}
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V3.ps}
+%\caption{Peculiar velocity alignment with the Vweb for $256^3$ grid resolution.}
+%\end{figure*}
 
-\begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V3.ps}
-\caption{Peculiar velocity alignment with the Vweb for $512^3$ grid resolution.}
-\end{figure*}
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V3.ps}
+%\caption{Peculiar velocity alignment with the Vweb for $512^3$ grid resolution.}
+%\end{figure*}
 
-\begin{figure*}
-\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T1.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T2.ps}
-\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T3.ps}
-\caption{Peculiar velocity alignment with the Tweb for $256^3$ grid resolution.}
-\end{figure*}
+%\begin{figure*}
+%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T1.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T2.ps}
+%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T3.ps}
+%\caption{Peculiar velocity alignment with the Tweb for $256^3$ grid resolution.}
+%\end{figure*}
 
@@
 
-\begin{figure*}
-\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_256.ps}
-\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_256.ps}
-\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_256.ps}
-\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_256.ps}
-\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_256.ps}
-\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_256.ps}
-\caption{From top to bottom: Shape, J, velocities. 256 resolution. Left Tweb, right Vweb}
-\end{figure*}
+%\begin{figure*}
+%\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_256.ps}
+%\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_256.ps}
+%\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_256.ps}
+%\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_256.ps}
+%\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_256.ps}
+%\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_256.ps}
+%\caption{From top to bottom: Shape, J, velocities. 256 resolution. Left Tweb, right Vweb}
+%\end{figure*}
 
-\begin{figure*}
-\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_512.ps}
-\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_512.ps}
-\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_512.ps}
-\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_512.ps}
-\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_512.ps}
-\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_512.ps}
-\caption{From top to bottom: Shape, J, velocities. 512 resolution. Left Tweb, right Vweb}
-\end{figure*}
+%\begin{figure*}
+%\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_512.ps}
+%\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_512.ps}
+%\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_512.ps}
+%\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_512.ps}
+%\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_512.ps}
+%\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_512.ps}
+%\caption{From top to bottom: Shape, J, velocities. 512 resolution. Left Tweb, right Vweb}
+%\end{figure*}
 
@@
 
-\subsection{Mass dependency and other conditions for stronger alignment}
+\subsection{What drives the alignment}
 
@@
 
+\begin{figure*}
+\includegraphics[width=0.48\textwidth]{../plot3/Type/256_All.png}
+\includegraphics[width=0.48\textwidth]{../plot3/Type/256_Big.png}
+\caption{Busy plot. Hard to describe.}
+\end{figure*}
+
 \section{Discussion}

### 2013-09-18 paper/main.tex
main.pdf
important note in a figure's caption
paper updated with new plots on what drives the alignment
text describing the simulation

@@
 \definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
-\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
-\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
 
+\newcommand{\documentname}{paper~}
 \newcommand{\LCDM}{$\Lambda$CDM~}
@@
 filament &$++$ & $>10^{12}$\hMsun\\
-
 &   & & 
 filament &$+$ & $<10^{12}$\hMsun\\
-
 &   & & 
@@
 
-In this paper we use groups found with a FOF halo finder.
+In this \documentname we use the Bolshoi volume. This is a simulation
+that follows the non-linear evolution of a dark matter density field
+on cosmological scales. The volume is a cubic box with 250\hMpc on a
+side, the matter density field is sampled with $2048^3$ particles. The
+cosmological parameters in the simulation correspond to the results
+inferred from WMAP5 data, which are also consistent with the more
+recent results of WMAP9. These parameters are $\Omega_m=0.27$,
+$\Omega_{\Lambda} =0.73$, $\sigma_8=0.82$, $n_s=0.95$ and $h=0.70$ for the
+matter density, cosmological constant, normalization of the power
+spectrum, the slope in the spectrum of the primordial matter
+fluctuation and the dimensionless Hubble constant. With this
+conditions the mass of each dark matter particle in the simulation
+corresponds to $m_p=1.4\times 10^{8}$\hMsun.
+
+In this paper we use groups found with a Friends-Of-Friends (FOF) halo
+finder using a linking length of $b=0.17$ times the mean interparticle
+separation. This choice translates into halos with a density of $570$
+times the mean density at $z=0$. The measurements for the shape,
+angular momentum and peculiar velocity are done using the set of
+particles in each dark matter halo. The definition we use in this
+\documentname for the shape comes from the diagonalization of the
+reduced inertia tensor.
+
+\begin{equation}
+{\mathcal T}_{lm} = \sum_{i}\frac{x_{i,l}x_{i,m}}{R_i^2}, 
+\end{equation}
+where $i$ is the particle index in the halo and $l,m$ run over the
+three spatial indexes  and $R_i^2 = x_{i,1}^2 + x_{i,2}^2 +
+x_{i,3}^2$, where the positions are measured with respect to the
+center of mass.
+
+The spin is calculated as
+\begin{equation}
+\vec{J} = \sum_{i}m_p{R_i}\vec{v}_i, 
+\end{equation}
+where the velocities are also measured with respect to the center of
+mass velocity. Finally the peculiar velocity of a halo is computed as the center of
+mass velocity.
 
@@
 In this paper we compute the cosmic web on grids of two different
-resolutions $256^3$ and $512^3$...
+resolutions $256^3$ and $512^3$. In the case for the Tweb we interpolate
 
@@
 ...
-
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V3.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V3.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V3.ps}
-%\caption{Interweb alignment for $256^3$ grid resolution.}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V3.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V3.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V3.ps}
-%\caption{Interweb alignment for $512^3$ grid resolution.}
-%\end{figure*}
 
@@
 
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V3.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V3.ps}
-%\caption{Shape alignment for the vweb at $256^3$ resolution.}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T3.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T3.ps}
-%\caption{Shape alignment for the tweb at $256^3$ resolution.}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V3.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V3.ps}
-%\caption{Shape alignment for the vweb at $512^3$ resolution.}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T3.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T3.ps}
-%\caption{Shape alignment for the tweb at $512^3$ resolution.}
-%\end{figure*}
-
 \newpage
 \subsection{Angular Momentum Alignment}
-
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V3.ps}
-%\caption{Angular momentum alignment with the Vweb for $256^3$ grid resolution.}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V3.ps}
-%\caption{Angular momentum alignment with the Vweb for $512^3$ grid resolution.}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T3.ps}
-%\caption{Angular momentum alignment with the Tweb for $256^3$ grid resolution.}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T3.ps}
-%\caption{Angular momentum alignment with the Tweb for $512^3$ grid resolution.}
-%\end{figure*}
 
@@
 
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V3.ps}
-%\caption{Peculiar velocity alignment with the Vweb for $256^3$ grid resolution.}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V3.ps}
-%\caption{Peculiar velocity alignment with the Vweb for $512^3$ grid resolution.}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T3.ps}
-%\caption{Peculiar velocity alignment with the Tweb for $256^3$ grid resolution.}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T1.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T2.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T3.ps}
-%\caption{Peculiar velocity alignment with the Tweb for $512^3$ grid resolution.}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=0.30\textwidth]{../plot2/Mass/vVWeb.ps}
-%\includegraphics[width=0.30\textwidth]{../plot2/Mass/vTWeb.ps}
-%\caption{Median of the peculiar velocity for the two web  and the two grid resolution.}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_256.ps}
-%\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_256.ps}
-%\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_256.ps}
-%\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_256.ps}
-%\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_256.ps}
-%\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_256.ps}
-%\caption{From top to bottom: Shape, J, velocities. 256 resolution. Left Tweb, right Vweb}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_512.ps}
-%\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_512.ps}
-%\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_512.ps}
-%\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_512.ps}
-%\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_512.ps}
-%\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_512.ps}
-%\caption{From top to bottom: Shape, J, velocities. 512 resolution. Left Tweb, right Vweb}
-%\end{figure*}
-
 Possible conclusion.
@@
 \begin{figure*}
-\includegraphics[width=0.48\textwidth]{../plot3/Type/256_All.png}
-\includegraphics[width=0.48\textwidth]{../plot3/Type/256_Big.png}
-\caption{Busy plot. Hard to describe.}
+\includegraphics[width=0.48\textwidth]{ax_T_cut.pdf}
+\includegraphics[width=0.48\textwidth]{ax_V_cut.pdf}
+\includegraphics[width=0.48\textwidth]{J_T_cut.pdf}
+\includegraphics[width=0.48\textwidth]{J_V_cut.pdf}
+\includegraphics[width=0.48\textwidth]{v_T_cut.pdf}
+\includegraphics[width=0.48\textwidth]{v_V_cut.pdf}
+\caption{The alignment is always taken with respect to the first eigenvector.}
 \end{figure*}

### 2013-10-18 paper/main.tex
updated figures
updated paper
new references + new paragraph to discuss spin and vorticity
darfting the abstract

@@
 \begin{abstract}
+
+We study
+the alignment of DM halos with the cosmic web as described by the
+tidal and velocity shear fields. We focus on the alignment of halos
+shape, spin and peculiar velocities. We use a cosmological N-body
+simulation that allows to study dark matter halos spanning four orders
+of magnitude in mass ($(10^{10}$-$10^{14}$) \hMsun and spatial
+scales of $(0.5$-$1.0)$\hMpc to define the cosmic web. After varying
+the numerical parameters in our experiments we find that the tidal
+field provides a robust description for the different kinds of
+alignments.  We measure a strong here is a strong alignment of the
+peculiar velocity field and the halo shape with the cosmic web defined
+by the tidal field. The results for the spin alignment are less
+significant. The shape alignment is stronger for halos that are either
+ massive ($M>10^{12}$\hMsun), have large or are located in high
+ density regions.
 
@@
 \end{table*}
+
+\section{N-body simulation and halo finding}
+
+In this \documentname we use the Bolshoi volume. This is a simulation
+that follows the non-linear evolution of a dark matter density field
+on cosmological scales. The volume is a cubic box with 250\hMpc on a
+side, the matter density field is sampled with $2048^3$ particles. The
+cosmological parameters in the simulation correspond to the results
+inferred from WMAP5 data, which are also consistent with the more
+recent results of WMAP9. These parameters are $\Omega_m=0.27$,
+$\Omega_{\Lambda} =0.73$, $\sigma_8=0.82$, $n_s=0.95$ and $h=0.70$ for the
+matter density, cosmological constant, normalization of the power
+spectrum, the slope in the spectrum of the primordial matter
+fluctuation and the dimensionless Hubble constant. With this
+conditions the mass of each dark matter particle in the simulation
+corresponds to $m_p=1.4\times 10^{8}$\hMsun.
+
+In this paper we use groups found with a Friends-Of-Friends (FOF) halo
+finder using a linking length of $b=0.17$ times the mean interparticle
+separation. This choice translates into halos with a density of $570$
+times the mean density at $z=0$. The measurements for the shape,
+angular momentum and peculiar velocity are done using the set of
+particles in each dark matter halo. The definition we use in this
+\documentname for the shape comes from the diagonalization of the
+reduced inertia tensor.
+
+\begin{equation}
+{\mathcal T}_{lm} = \sum_{i}\frac{x_{i,l}x_{i,m}}{R_i^2}, 
+\end{equation}
+where $i$ is the particle index in the halo and $l,m$ run over the
+three spatial indexes  and $R_i^2 = x_{i,1}^2 + x_{i,2}^2 +
+x_{i,3}^2$, where the positions are measured with respect to the
+center of mass.
+
+The spin is calculated as
+\begin{equation}
+\vec{J} = \sum_{i}m_p{R_i}\vec{v}_i, 
+\end{equation}
+where the velocities are also measured with respect to the center of
+mass velocity. Finally the peculiar velocity of a halo is computed as
+the center of mass velocity.
+
+\section{The cosmic web algorithms}
+\label{sec:algorithms}
+We use two algorithms to define the cosmic web on cosmological N-body
+simulations. Both are based on the same algorithmic principle, which
+is determining locally a symmetric tensor which can be diagonalized to yield
+three real eigenvalues $\lambda_1>\lambda_2>\lambda_3$ and their
+corresponding eigenvectors ${\bf e}_{1}$, ${\bf e}_2$ and ${\bf
+  e}_3$. This allows for a local classification into one of the
+following four categories: void, sheet, filament and peak depending
+whether the number of eigenvalues larger than a given threshold
+$\lambda_{th}$ is $3$, $2$, $1$ or $0$, respectively.
+
+We use two different symmetric tensors. The first is the shear tensor,
+defined as the hessian of the gravitational potential, normalized in
+such a way as to be dimensionless:
+
+\begin{equation}
+T_{\alpha\beta} = \frac{\partial^2\phi}{\partial
+  r_{\alpha}\partial r_{\beta}}, 
+\end{equation}
+where $\phi$ is the gravitational potential rescaled by a factor $4\pi
+G\bar{\rho}=3/2\Omega_m H_{0}^2$ in such a way that the Poission
+equation can be written as:
+
+\begin{equation}
+\nabla^{2}\phi  = \delta, 
+\end{equation}
+
+where $\delta$ is the matter overdensity, $\bar{\rho}$ is the average
+matter density, $H_{0}$ is the Hubble constant at present time and
+$\Omega_m$ is the matter density parameter.
+
+The second tensor is the velocity shear:
+
+\begin{equation}
+\Sigma_{\alpha\beta} = -\frac{1}{2H_{0}}\left(\frac{\partial
+  v_{\alpha}}{\partial r_{\beta}}+ \frac{\partial v_{\beta}}{\partial
+  r_{\alpha}}\right) 
+\end{equation}
+
+\subsection{Numerical considerations}
+
+In this paper we compute the cosmic web on grids of two different
+resolutions $256^3$ and $512^3$. In the case for the Tweb we interpolate
+
+\section{Results}
+
+\subsection{Interweb Alignment}
+... We compute the pair-wise allignment between the eigenvectors in
+the two web finders.
+
+... We also compute the alignment between the eigenvectors in cells
+occupied by dark matter halos. This will be a key element in the
+interpretation of the results for halo-based allignments in the next
+sections: shape, angular momentum and peculiar velocities.
+
+...
+
+\begin{figure}
+\includegraphics[width=0.40\textwidth]{web.pdf}
+\caption{Median of the interweb alignment for the two grid
+  resolutions as a function of the dark matter mass corresponding to
+  the halos where the measurement was made. The error bars indicate
+  the lower and upper quartiles (Figure in color in the web version).} 
+\end{figure}
+
+\subsection{Shape Alignment}
+
+\begin{figure*}
+\includegraphics[width=0.80\textwidth]{Fig2.pdf}
+\caption{Median of $\cos\theta$ quantifying the shape alignment for
+  the Vweb (left) and the Tweb (right) at two different grid
+  resolutions. In the upper (lower) panels the angle $\theta$ is
+  measured between the halo minor (major) axis and the first (third)
+  eigenvector.} 
+\end{figure*}
+
+\newpage
+\subsection{Angular Momentum Alignment}
+
+\begin{figure*}
+\includegraphics[width=0.80\textwidth]{Fig3.pdf}
+\caption{Median of $\cos\theta$ quantifying the angular momentum
+  alingment for the Vweb (left) and the Tweb (right) at two different
+  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
+  measured between the first (third) eivenvector and the angular
+  momentum vector.} 
+\end{figure*}
+
+\subsection{Peculiar velocity Alignment}
+
+\begin{figure*}
+\includegraphics[width=0.80\textwidth]{Fig4.pdf}
+\caption{Median of $\cos\theta$ quantifying the peculiar velocity
+  alignment with the Vweb (left) and the Tweb (right) at two different
+  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
+  measured between the first (third) eivenvector and a halo's peculiar
+  velocity.} 
+\end{figure*}
+
+Possible conclusion.
+Prolateness follow concentration.
+In the Tweb Angular momentum alignment is influenced by spin at higher masses.
+In the Vweb angular momentum alginment is influenced by all factors.
+In the peculiar velocity alginment only spin seemss to have an effect.
+
+\subsection{What drives the alignment}
+
+We wish to understand what other selection criteria on halo
+properties can produce a stronger local alignment for the shape, spin
+and peculiar velocities. We split the halo population into low and
+high mass halos imposing a cut at $M_{\rm halo}=10^{11}$\hMsun. This
+allows us to have robust statistics on the high mass end. We have also
+computed these results for a cut at $M_{\rm halo}=10^{12}$\hMsun and
+checked that the results we report below are not affected by this
+change.
+
+For each mass interval we perform cuts in the following properties:
+spin, concentration, triaxiallity, circularity  and density. We
+measure the web alignments in two sets, each one including the $30\%$
+of halos in the lower/higher end of the corresponding property.
+
+\begin{figure*}
+\includegraphics[width=0.48\textwidth]{ax_T_cut.pdf}
+\includegraphics[width=0.48\textwidth]{ax_V_cut.pdf}
+\includegraphics[width=0.48\textwidth]{J_T_cut.pdf}
+\includegraphics[width=0.48\textwidth]{J_V_cut.pdf}
+\includegraphics[width=0.48\textwidth]{v_T_cut.pdf}
+\includegraphics[width=0.48\textwidth]{v_V_cut.pdf}
+\caption{The alignment is always taken with respect to the first eigenvector.}
+\end{figure*}
+
+\section{Discussion}
+\label{sec:discussion}
+
+We do not find a strong signal for the alignment of spin and the
+cosmic web. A significant correlation signal has been recently
+measured between the spin and the cosmic vorticity
+\citep{Libeskind2013a,Laigle2013}. This two facts are consistent with
+spin being produced by the non-symmetric part of the shear and tidal
+tensors.
+
+\section{Conclusions}
+\label{sec:conclusions}
+
+\section*{Acknowledgments}
+
+\section*{Appendix A. Detailed description of previous theoretical results}
 
@@
 \end{itemize}
-\section{N-body simulation and halo finding}
-
-In this \documentname we use the Bolshoi volume. This is a simulation
-that follows the non-linear evolution of a dark matter density field
-on cosmological scales. The volume is a cubic box with 250\hMpc on a
-side, the matter density field is sampled with $2048^3$ particles. The
-cosmological parameters in the simulation correspond to the results
-inferred from WMAP5 data, which are also consistent with the more
-recent results of WMAP9. These parameters are $\Omega_m=0.27$,
-$\Omega_{\Lambda} =0.73$, $\sigma_8=0.82$, $n_s=0.95$ and $h=0.70$ for the
-matter density, cosmological constant, normalization of the power
-spectrum, the slope in the spectrum of the primordial matter
-fluctuation and the dimensionless Hubble constant. With this
-conditions the mass of each dark matter particle in the simulation
-corresponds to $m_p=1.4\times 10^{8}$\hMsun.
-
-In this paper we use groups found with a Friends-Of-Friends (FOF) halo
-finder using a linking length of $b=0.17$ times the mean interparticle
-separation. This choice translates into halos with a density of $570$
-times the mean density at $z=0$. The measurements for the shape,
-angular momentum and peculiar velocity are done using the set of
-particles in each dark matter halo. The definition we use in this
-\documentname for the shape comes from the diagonalization of the
-reduced inertia tensor.
-
-\begin{equation}
-{\mathcal T}_{lm} = \sum_{i}\frac{x_{i,l}x_{i,m}}{R_i^2}, 
-\end{equation}
-where $i$ is the particle index in the halo and $l,m$ run over the
-three spatial indexes  and $R_i^2 = x_{i,1}^2 + x_{i,2}^2 +
-x_{i,3}^2$, where the positions are measured with respect to the
-center of mass.
-
-The spin is calculated as
-\begin{equation}
-\vec{J} = \sum_{i}m_p{R_i}\vec{v}_i, 
-\end{equation}
-where the velocities are also measured with respect to the center of
-mass velocity. Finally the peculiar velocity of a halo is computed as the center of
-mass velocity.
-
-\section{The cosmic web algorithms}
-\label{sec:algorithms}
-We use two algorithms to define the cosmic web on cosmological N-body
-simulations. Both are based on the same algorithmic principle, which
-is determining locally a symmetric tensor which can be diagonalized to yield
-three real eigenvalues $\lambda_1>\lambda_2>\lambda_3$ and their
-corresponding eigenvectors ${\bf e}_{1}$, ${\bf e}_2$ and ${\bf
-  e}_3$. This allows for a local classification into one of the
-following four categories: void, sheet, filament and peak depending
-whether the number of eigenvalues larger than a given threshold
-$\lambda_{th}$ is $3$, $2$, $1$ or $0$, respectively.
-
-We use two different symmetric tensors. The first is the shear tensor,
-defined as the hessian of the gravitational potential, normalized in
-such a way as to be dimensionless:
-
-\begin{equation}
-T_{\alpha\beta} = \frac{\partial^2\phi}{\partial
-  r_{\alpha}\partial r_{\beta}}, 
-\end{equation}
-where $\phi$ is the gravitational potential rescaled by a factor $4\pi
-G\bar{\rho}=3/2\Omega_m H_{0}^2$ in such a way that the Poission
-equation can be written as:
-
-\begin{equation}
-\nabla^{2}\phi  = \delta, 
-\end{equation}
-
-where $\delta$ is the matter overdensity, $\bar{\rho}$ is the average
-matter density, $H_{0}$ is the Hubble constant at present time and
-$\Omega_m$ is the matter density parameter.
-
-The second tensor is the velocity shear:
-
-\begin{equation}
-\Sigma_{\alpha\beta} = -\frac{1}{2H_{0}}\left(\frac{\partial
-  v_{\alpha}}{\partial r_{\beta}}+ \frac{\partial v_{\beta}}{\partial
-  r_{\alpha}}\right) 
-\end{equation}
-
-\subsection{Numerical considerations}
-
-In this paper we compute the cosmic web on grids of two different
-resolutions $256^3$ and $512^3$. In the case for the Tweb we interpolate
-
-\section{Results}
-
-\subsection{Interweb Alignment}
-... We compute the pair-wise allignment between the eigenvectors in
-the two web finders.
-
-... We also compute the alignment between the eigenvectors in cells
-occupied by dark matter halos. This will be a key element in the
-interpretation of the results for halo-based allignments in the next
-sections: shape, angular momentum and peculiar velocities.
-
-...
-
-\begin{figure}
-\includegraphics[width=0.45\textwidth]{../plot2/Mass/Web.pdf}
-\caption{Median of the interweb alignment for the two grid
-  resolutions as a function of the dark matter mass corresponding to
-  the halos where the measurement was made. The error bars indicate
-  the lower and upper quartiles (Figure in color in the web version).} 
-\end{figure}
-
-\subsection{Shape Alignment}
-
-\begin{figure*}
-\includegraphics[width=0.45\textwidth]{../plot2/Mass/VWeb.pdf}
-\includegraphics[width=0.45\textwidth]{../plot2/Mass/TWeb.pdf}
-\includegraphics[width=0.45\textwidth]{../plot2/Mass/VWebV2.pdf}
-\includegraphics[width=0.45\textwidth]{../plot2/Mass/TWebV2.pdf}
-\caption{Median of $\cos\theta$ quantifying the shape alignment for
-  the Vweb (left) and the Tweb (right) at two different grid
-  resolutions. In the upper (lower) panels the angle $\theta$ is
-  measured between the halo minor (major) axis and the first (third)
-  eigenvector.} 
-\end{figure*}
-
-\newpage
-\subsection{Angular Momentum Alignment}
-
-\begin{figure*}
-\includegraphics[width=0.45\textwidth]{../plot2/Mass/jVWeb.pdf}
-\includegraphics[width=0.45\textwidth]{../plot2/Mass/jTWeb.pdf}
-\includegraphics[width=0.45\textwidth]{../plot2/Mass/jVWebV2.pdf}
-\includegraphics[width=0.45\textwidth]{../plot2/Mass/jTWebV2.pdf}
-\caption{Median of $\cos\theta$ quantifying the angular momentum
-  alingment for the Vweb (left) and the Tweb (right) at two different
-  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
-  measured between the first (third) eivenvector and the angular
-  momentum vector.} 
-\end{figure*}
-
-\subsection{Peculiar velocity Alignment}
-
-\begin{figure*}
-\includegraphics[width=0.45\textwidth]{../plot2/Mass/vVWeb.pdf}
-\includegraphics[width=0.45\textwidth]{../plot2/Mass/vTWeb.pdf}
-\includegraphics[width=0.45\textwidth]{../plot2/Mass/vVWebV2.pdf}
-\includegraphics[width=0.45\textwidth]{../plot2/Mass/vTWebV2.pdf}
-\caption{Median of $\cos\theta$ quantifying the peculiar velocity
-  alignment with the Vweb (left) and the Tweb (right) at two different
-  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
-  measured between the first (third) eivenvector and a halo's peculiar
-  velocity.} 
-\end{figure*}
-
-Possible conclusion.
-Prolateness follow concentration.
-In the Tweb Angular momentum alignment is influenced by spin at higher masses.
-In the Vweb angular momentum alginment is influenced by all factors.
-In the peculiar velocity alginment only spin seemss to have an effect.
-
-\subsection{What drives the alignment}
-
-We wish to understand what other selection criteria on halo
-properties can produce a stronger local alignment for the shape, spin
-and peculiar velocities. We split the halo population into low and
-high mass halos imposing a cut at $M_{\rm halo}=10^{11}$\hMsun. This
-allows us to have robust statistics on the high mass end. We have also
-computed these results for a cut at $M_{\rm halo}=10^{12}$\hMsun and
-checked that the results we report below are not affected by this
-change.
-
-For each mass interval we perform cuts in the following properties:
-spin, concentration, triaxiallity, circularity  and density. We
-measure the web alignments in two sets, each one including the $30\%$
-of halos in the lower/higher end of the corresponding property.
-
-\begin{figure*}
-\includegraphics[width=0.48\textwidth]{ax_T_cut.pdf}
-\includegraphics[width=0.48\textwidth]{ax_V_cut.pdf}
-\includegraphics[width=0.48\textwidth]{J_T_cut.pdf}
-\includegraphics[width=0.48\textwidth]{J_V_cut.pdf}
-\includegraphics[width=0.48\textwidth]{v_T_cut.pdf}
-\includegraphics[width=0.48\textwidth]{v_V_cut.pdf}
-\caption{The alignment is always taken with respect to the first eigenvector.}
-\end{figure*}
-
-\section{Discussion}
-\label{sec:discussion}
-
-\section{Conclusions}
-\label{sec:conclusions}
-
-\section*{Acknowledgments}
 

### 2013-10-23 paper/main.tex
adding some text to the introduction

@@
 \def\ea{\end{eqnarray}}
+
 % To highlight comments 
@@
 
-%-------
+The formation of large scale structure in the Universe proceeds by
+gravitational instability. This is an intrinsic anisotropic
+process. [Pancake formation ...]
 
-\section{Theoretical Antecedents}
+Numerical simulations allow the exploration of a deep nonlinear
+regime, following the formation of virialized dark matter halos, which
+host observable galaxies. Some characteristics of these halos have to
+be linked to the environment in which they formed. One way to studty
+the connection halo-environment is to quantify the degree of
+correlation between different halo properties and their surrounding
+density and velocity fields.
+
+Among the properties that are of interest we find the shape, spin and
+peculiar velocity. [Relevanc of dark matter halo shapes ...]
+[Relevance of halo spin ...] [Relevance of peculiar velocities]
+
+There is large tradition of theoretical precedents for the
+measurements of shape and spin alignment. In this \documentname we
+review most of these studyes and offer our own study with
+complementary numerical techniques and simulations. [Brief summary of
+  the appendix ...]
+
+We also present the results for the alignment of peculiar velocities
+with large scale structure. Such a study has received less atention in
+the literature. However, we consider that it presents relevant
+insights for the study of cosmic flows.
+
+The structure of this \documentname is the following.
+
+\section{Theoretical Precedents}
 \label{sec:theory}
@@
 
-... Table 1 and Table 2 summariz recent results found in the literature for
-shape and angular momentum alignment, respectively.
+... Table 1 and Table 2 summarizes recent results found in the literature for
+shape and angular momentum alignment.
 
@@
 
+{\bf Contreras et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
+filament &$?$ & $>10^{12}$\hMsun\\
+&   & & 
+filament &$?$ & $<10^{12}$\hMsun\\
+&   & & 
+wall & $?$ & all masses\\\hline
+
+{\bf Contreras et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ & 
+filament &$?$ & $>10^{12}$\hMsun\\
+&   & & 
+filament &$?$ & $<10^{12}$\hMsun\\
+&   & & 
+wall & $?$ & all masses\\\hline
+
 \cite{Libeskind2013} & V-Web & $1 \hMpc$ & 
@@
 &   & & 
-wall & $++$ & all masses\\
+wall & $++$ & all masses\\\hline
 
@@
 & &  & 
-filament & $+$ & $<10^{12}\hMsun$\\
+filament & $+$ & $<10^{12}\hMsun$\\\hline
 
@@
 \end{tabular}\\
-\caption{Summary of previous theoretical results.
-Shape. Indicates the alignment of the halo's major axis along a
-filament or a sheet.} 
+\caption{Shape alignment with the cosmic web. Summary of theoretical
+  results provided by methods comparable to ours.}
 \end{table*}
@@
 Alignment & Mass dependence\\\hline
+
+{\bf Contreras et al. (2014)} & V-Web & $1 \hMpc$ & 
+filament &$?$ & $>10^{12}$\hMsun\\
+
+&   & & 
+filament &$?$ & $<10^{12}$\hMsun\\
+
+&   & & 
+wall & $?$ & all masses\\\hline
+
+{\bf Contreras et al. (2014)} & Vp-Web & $1 \hMpc$ & 
+filament &$?$ & $>10^{12}$\hMsun\\
+
+&   & & 
+filament &$?$ & $<10^{12}$\hMsun\\
+
+&   & & 
+wall & $?$ & all masses\\\hline
 
@@
 &   & & 
-filament & $+$ & $< 5\times 10^{12}$\hMsun\\
+filament & $+$ & $< 5\times 10^{12}$\hMsun\\\hline
 
@@
 & & & 
-wall & $++$ & all masses\\
+wall & $++$ & all masses\\\hline
 
@@
 & &  & 
-filament & $--$ & only if correlated with shape\\
+filament & $--$ & only if correlated with shape\\\hline
 
@@
 & & - &
-filament& $-$ & $>10^{12}$\hMsun\\
+filament& $-$ & $>10^{12}$\hMsun\\\hline
 
 & & - &
-filament& $+$ & $<10^{12}$\hMsun\\
+filament& $+$ & $<10^{12}$\hMsun\\\hline
 
@@
 \end{tabular}
-\caption{Summary of previous theoretical results.
-Angular Momentum}
+\caption{Spin alignment with the cosmic web. Summary of theoretical
+  results provided by methods comparable to ours.}
+
 \end{table*}

### 2013-11-06 paper/main.tex
new figure in paper
first take on the interweb alignment

@@
 
-In this \documentname we use the Bolshoi volume. This is a simulation
-that follows the non-linear evolution of a dark matter density field
-on cosmological scales. The volume is a cubic box with 250\hMpc on a
-side, the matter density field is sampled with $2048^3$ particles. The
+In this \documentname we use the Bolshoi simulation that follows the
+non-linear evolution of a dark matter density field on cosmological
+scales. The volume is a cubic box with 250\hMpc on a side, the matter
+density field is sampled with $2048^3$ particles. The  
 cosmological parameters in the simulation correspond to the results
@@
 \subsection{Interweb Alignment}
-... We compute the pair-wise allignment between the eigenvectors in
-the two web finders.
 
-... We also compute the alignment between the eigenvectors in cells
-occupied by dark matter halos. This will be a key element in the
-interpretation of the results for halo-based allignments in the next
-sections: shape, angular momentum and peculiar velocities.
+In the first place we wish to directly compare the results of the two
+algorithms. For the two algorithms we have the information for the
+eigenvectors and the eigenvalues on exactly the same positions defined
+by the grids. This allows us tocompute the pair-wise allignment
+between the eigenvectors in the two web finders.
 
-...
+We are mainly interested in the alginment of the web with
+the halos. Therefore we restrict our analysis to the grid cells that are
+occupied by halos. If we had decided to perform this kind of analysis
+on all the grid cells, the statistics would be dominated by the void
+regions, because the dominate in number the fraction of cells in the
+simuation.
+
+Figure \ref{fig:interweb} shows the results of the inter-web alignment
+as a function of halo mass. It clearly stands out that the
+eigenvectors are aligned for low mass halos but are close perpendicular to
+each other at the location of the most massive halos. There is a
+transition scale around $(10^{11.5}-10^{12.5})$\hMsun depending on the
+grid resolution. The coarse grid $(256^3)$shows the transition at higher masses
+than the fine grid $(512^3)$.
+
+For both resolutions, the halos more massiven than $10^{13}$\hMsun are
+locate in regions where the fastest momentum-weighted collapse
+direction (defined by the V-web) is perpendicular to the direction
+where the tidal compression is the highest.
+
+The fact that this trend is less evident at low resolution and low
+masses, hints that the flip is actually related to the overdensity
+values, i.e. to the degree of non-linearity, in the corresponding
+spatial scales.
 
@@
   the halos where the measurement was made. The error bars indicate
-  the lower and upper quartiles (Figure in color in the web version).} 
+  the lower and upper quartiles (Figure in color in the web version).
+\label{fig:interweb}} 
 \end{figure}
@@
 \begin{figure*}
-\includegraphics[width=0.48\textwidth]{ax_T_cut.pdf}
-\includegraphics[width=0.48\textwidth]{ax_V_cut.pdf}
-\includegraphics[width=0.48\textwidth]{J_T_cut.pdf}
-\includegraphics[width=0.48\textwidth]{J_V_cut.pdf}
-\includegraphics[width=0.48\textwidth]{v_T_cut.pdf}
-\includegraphics[width=0.48\textwidth]{v_V_cut.pdf}
+\includegraphics[width=0.90\textwidth,angle=90]{all_cuts.pdf}
 \caption{The alignment is always taken with respect to the first eigenvector.}
 \end{figure*}
-
 \section{Discussion}

### 2013-11-06 paper/main.tex
first words on spin alignment

@@
 
-{\bf Contreras et al. (2014)} & V-Web & $1 \hMpc$ & 
-filament &$?$ & $>10^{12}$\hMsun\\
+{\bf Contreras et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
+filament &none & $<10^{12}$\hMsun\\
 
 &   & & 
-filament &$?$ & $<10^{12}$\hMsun\\
+filament & - & $>10^{12}$\hMsun\\
 
 &   & & 
-wall & $?$ & all masses\\\hline
-
-{\bf Contreras et al. (2014)} & Vp-Web & $1 \hMpc$ & 
-filament &$?$ & $>10^{12}$\hMsun\\
+wall & none & $<10^{12}$\hMsun\\
 
 &   & & 
-filament &$?$ & $<10^{12}$\hMsun\\
+wall & - & $>10^{12}$\hMsun\\\hline
+
+{\bf Contreras et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ & 
+filament &none & $<10^{12}$\hMsun\\
 
 &   & & 
-wall & $?$ & all masses\\\hline
+filament & none & $>10^{12}$\hMsun\\
+
+&   & & 
+wall & none & $<10^{12}$\hMsun\\
+
+&   & & 
+wall & + & $>10^{12}$\hMsun\\\hline
 
@@
 
+\subsection{Angular Momentum Alignment}
+
+\begin{figure*}
+\includegraphics[width=0.80\textwidth]{Fig3.pdf}
+\caption{Median of $\cos\theta$ quantifying the angular momentum
+  alingment for the Vweb (left) and the Tweb (right) at two different
+  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
+  measured between the first (third) eivenvector and the angular
+  momentum vector.
+  \label{fig:spin_alignment}
+} 
+\end{figure*}
+
+We now take a look at the alignment of the halo spin with the cosmic
+web. This characterization is done in terms of the angle between the
+angular momentum vector and the first/third eigenvector.
+
+Figure \ref{fig:spin_alignnment} shows the results as a function of
+the halo mass. In the case of the V-web the trends can be summarized
+as follows. Low mass halos $10^{12}$\hMsun do not show any
+preferential alignment with the cosmic web. Halos more massive than
+this threshold have their spin slightly perpendicular to the
+direction defined by the first eigenvector (defining sheets) and
+uncorrelated to the third eigenvector (filament direction). This
+translates into a weak tendency for the spin to lie on the
+sheet-plane.
+
+In the case of the T-web there is a similar trend for low mass halos
+$10^{12}$\hMsun not to have any preferential direction with respect to
+the cosmic web. High mass halos present a weak alignment with the
+first eigen vector and anti-alignment with the third
+eigenvector. Summarizing, the spin of massive halos tends to be
+slightly perpendicular to filaments and sheets.
+
 \subsection{Shape Alignment}
@@
   eigenvector.} 
-\end{figure*}
-
-\newpage
-\subsection{Angular Momentum Alignment}
-
-\begin{figure*}
-\includegraphics[width=0.80\textwidth]{Fig3.pdf}
-\caption{Median of $\cos\theta$ quantifying the angular momentum
-  alingment for the Vweb (left) and the Tweb (right) at two different
-  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
-  measured between the first (third) eivenvector and the angular
-  momentum vector.} 
 \end{figure*}

### 2013-11-06 paper/main.tex
reference updated

@@
   measured between the first (third) eivenvector and the angular
-  momentum vector.
-  \label{fig:spin_alignment}
-} 
+  momentum vector.\label{fig:spin_alignment}} 
 \end{figure*}
@@
 
-Figure \ref{fig:spin_alignnment} shows the results as a function of
+Figure \ref{fig:spin_alignment} shows the results as a function of
 the halo mass. In the case of the V-web the trends can be summarized

### 2013-11-08 paper/main.tex
updates on the shape alignment

@@
 {\bf Contreras et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
-filament &$?$ & $>10^{12}$\hMsun\\
+filament &$++$ & all masses\hMsun\\
 &   & & 
-filament &$?$ & $<10^{12}$\hMsun\\
-&   & & 
-wall & $?$ & all masses\\\hline
+wall & $--$ & all masses\\\hline
 
@@
   measured between the halo minor (major) axis and the first (third)
-  eigenvector.} 
+  eigenvector.\label{fig:shape_alignment}} 
 \end{figure*}
+
+The shape alignment shows stronger trends. Figure
+\ref{fig:shape_alignment} presents the main results as a function of
+halo mass. In this case we characterize the shape by the direction
+determined by the major axis.
+
+In the case of the V-web we have a clear anti-alignment with respect
+to both first and third eigenvectors for massive halos
+$>10^{12}$\hMsun. This implies that a halo is typically perpendicular to 
+filaments and lies along the plane defined by a sheet. For low mass
+halos $<10^{12}$\hMsun we do not find any correlation with the
+cosmic web.
+
+The T-web shows alignment/anti-alignment trends starting at masses of
+$10^{10}$\hMsun, two orders of magnitude less than the V-web. In this
+case we see an alignment along the first and third eigenvectors. It
+means that halos in filamentary environments tend to be aligned with
+the filament, while halos in pancake environments are perpendicular to
+the sheet.
 

### 2013-11-08 paper/main.tex
adding confusing non-sense

@@
 
-The T-web shows alignment/anti-alignment trends starting at masses of
+The T-web shows alignment  trends starting at masses of
 $10^{10}$\hMsun, two orders of magnitude less than the V-web. In this
@@
 the sheet.
+
+The most massive halos showing the strongets alignment trends are not
+usually located in regions classified as peaks where all the
+eigenvectors are are positive, meaning that thre is
+collapse/compressive stress in all directions.
+
+In this situation we
+can interpret alignment both along the first and third eigenvector as
+a signature that most massive halos tend to be aligned midway between
+the first and second eigenvector, lying along the plane defined by the
+second eigenvector.
 

### 2014-01-08 paper/main.tex
structure paragraph, methods description, new references

@@
 \parbox[t]{\textwidth}{\raggedright 
-  Sergio Contreras$^{1}$ 
-  Jaime E. Forero-Romero$^{1}$ 
-  Nelson Padilla$^{1}$ 
+  Jaime E. Forero-Romero$^{1}$,
+  Sergio Contreras$^{2}$,
+  Nelson Padilla$^{2}$ 
 }
@@
 
-The structure of this \documentname is the following.
+The structure of this \documentname is the following. In \S
+\ref{sec:theory} we present the theoretical antecedendts for the
+alignment studies we present in this paper. In \S
+\ref{sec:nbody} we present the N-body
+cosmological simulation and halo catalogs next to describe in
+\S\ref{sec:algorithms} the two web-finding algorithms we use. In
+\S\ref{sec:results} we present our main results about the alignment
+of shape, spin and peculiar velocities with respect to the cosmic
+web. We continue with a discussion of these results in
+\S\ref{sec:discussion} paying special attention to resolution effects
+and the conditions that might drive the strong alignment signals
+observed in the precedent section. In \S\ref{sec:conclusions} we
+present our conclusions.
 
@@
 ... There is abundant literature on the issue of shape and angular momentum
-aligmnent of dark matter haloe with respect to the cosmic we.
+aligmnent of dark matter haloe with respect to the cosmic web.
 
@@
 ... Table 1 and Table 2 summarizes recent results found in the literature for
-shape and angular momentum alignment.
+shape and angular momentum alignment. The Appendix includes a detailed
+description of each one the algorithms.
 
-The tidal connection between voids in simulations \citep{Platen2008},
-the alignment of observed galaxies with the inferred tidal
-field\citep{Lee2007,Jones2010}. There are other kind of alignment
-statistics based on modifications of the correlation
-\citep{Paz2008,Faltenbacher2009} that go beyond a local computation
-and therefore are not reviewed in detail in this paper.
+The main summary from these results can be done in three points. (i)
+The halo mass of $1-5\times 10^{12}$\hMsun is a threshold mass between
+different behaviours.  (ii) Halo shape is strongly aligned along
+filaments, more so for massive haloes and (iii) Halo spin tends to be
+perpendicular with respect to filaments, but it is a weak.
 
@@
 \section{N-body simulation and halo finding}
+\label{sec:nbody}
 
@@
 \end{equation}
+%
 where $\phi$ is the gravitational potential rescaled by a factor $4\pi
 G\bar{\rho}=3/2\Omega_m H_{0}^2$ in such a way that the Poission
-equation can be written as:
-
-\begin{equation}
-\nabla^{2}\phi  = \delta, 
-\end{equation}
-
-where $\delta$ is the matter overdensity, $\bar{\rho}$ is the average
-matter density, $H_{0}$ is the Hubble constant at present time and
-$\Omega_m$ is the matter density parameter.
+equation can be written as $\nabla^{2}\phi  = \delta$, where $\delta$
+is the matter overdensity, $\bar{\rho}$ is the averagematter density,
+$H_{0}$ is the Hubble constant at present time and $\Omega_m$ is the
+matter density parameter. A detailed presentation of this algorithm
+can be found in \citep{Tweb}.
 
@@
   v_{\alpha}}{\partial r_{\beta}}+ \frac{\partial v_{\beta}}{\partial
-  r_{\alpha}}\right) 
+  r_{\alpha}}\right), 
 \end{equation}
+%
+where $v_{\alpha}$ correspond to the components of the peculiar
+comoving velocities. With this definition the trace of the shear
+tensor is minus the divergence of the velocity field normalized by the
+Hubble constant $-\nabla\cdot {\bf}v /H_{0}$. A detailed description
+of this algorithm can be found in \citep{Vweb}.
 
@@
 In this paper we compute the cosmic web on grids of two different
-resolutions $256^3$ and $512^3$. In the case for the Tweb we interpolate
+resolutions $256^3$ and $512^3$. In the V-Web computations we compute
+the velocity field as follows. First we compute the momentum density field
+over a grid and the normalize it by the matter density field. We follow the
+same procedure for the gaussian smoothed fields. It means that a
+smoothed velocity fields is the ratio of the smoothed momentum density
+and matter density fields.
 
 \section{Results}
+\label{sec:results}
 
@@
 
-Possible conclusion.
-Prolateness follow concentration.
-In the Tweb Angular momentum alignment is influenced by spin at higher masses.
-In the Vweb angular momentum alginment is influenced by all factors.
-In the peculiar velocity alginment only spin seemss to have an effect.
+Possible conclusion. Prolateness follow concentration. In the Tweb
+Angular momentum alignment is influenced by spin at higher masses. In
+the Vweb angular momentum alginment is influenced by all factors. In
+the peculiar velocity alginment only spin seemss to have an effect.
 
@@
 \section*{Appendix A. Detailed description of previous theoretical results}
+
+The tidal connection between voids in simulations \citep{Platen2008},
+the alignment of observed galaxies with the inferred tidal
+field\citep{Lee2007,Jones2010}. There are other kind of alignment
+statistics based on modifications of the correlation
+\citep{Paz2008,Faltenbacher2009} that go beyond a local computation
+and therefore are not reviewed in detail in this paper.
 

### 2014-01-08 paper/main.tex
minor modifications in tables

@@
 
-{\bf Contreras et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
+{\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
 filament &$++$ & all masses\hMsun\\
@@
 
-{\bf Contreras et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ & 
+{\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ & 
 filament &$?$ & $>10^{12}$\hMsun\\
@@
 \begin{tabular}{cccccc}\hline\hline
-Author & Web Method & Spatial Scale & Along &
-Alignment & Mass dependence\\\hline
+Author & Web Method & Spatial Scale& Along &
+Alignment & Mass dependence\\
+ & & ($\hMpc$)& & & \\\hline
 
-{\bf Contreras et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
+{\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1$ & 
 filament &none & $<10^{12}$\hMsun\\
@@
 
-{\bf Contreras et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ & 
+{\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1$ & 
 filament &none & $<10^{12}$\hMsun\\
@@
 
-\cite{Libeskind2013} & V-Web & $1 \hMpc$ & 
+\cite{Libeskind2013} & V-Web & $1$ & 
 filament &$-$ & $>10^{12}$\hMsun\\
@@
 
-\cite{Trowland2013} & Hessian density & $2-5\hMpc$ & 
+\cite{Trowland2013} & Hessian density & $2-5$ & 
 filament & $-$ & $> 5\times 10^{12}$\hMsun\\
@@
 
-\cite{Codis2012} & Morse Theory \& Tidal Web & $1-5\hMpc$ & 
+\cite{Codis2012} & Morse Theory \& T-Web & $1-5$ & 
 filament & $--$ & $>10^{12}$\hMsun \\
@@
 
-\cite{Zhang2009}  & Hessian density field &  $2.1$\hMpc & 
-filament & $++$ & only if anticorrelated with shape\\
+\cite{Zhang2009}  & Hessian density &  $2.1$ & 
+filament & $++$ & if anticorrelated with shape\\
 
 & &  & 
-filament & $--$ & only if correlated with shape\\\hline
+filament & $--$ & if correlated with shape\\\hline
 
-\cite{AragonCalvo2007} & Hessian density field & - &
+\cite{AragonCalvo2007} & Hessian density & - &
 wall & $++$ & $>10^{12}$\hMsun\\
@@
 
-\cite{Hahn2007} & Tidal Web & $2.1$\hMpc & filament & $-$& none\\
+\cite{Hahn2007} & Tidal Web & $2.1$ & filament & $-$& none\\
 
 & &  $2.1$\hMpc &
-wall & $++$ & stronger $>10^{12}$\hMsun\\\hline \hline
+wall & $++$ & stronger $>10^{12}$\\\hline \hline
 

### 2014-01-30 paper/main.tex
new plot included in the paper

@@
 \label{sec:results}
+
+\begin{figure*}
+\includegraphics[width=0.9\textwidth]{Fig0.pdf}
+\caption{Fraction of halos in a mass bin that show a preferential
+  alignment with respect to an eigenvector for the three properties
+  studies in this paper: shape (major axis), angular momentum and
+  peculiar velocity. Left column presents the results against the Tweb
+  and the right the Vweb. Strong colors refer to $256^3$ grid
+  resolutions and lighter colors to a $512^3$ grid.
+\label{fig:preferential}}
+\end{figure*}
 

### 2014-02-04 paper/main.tex
first dump section 1

@@
 
-\section{Theoretical Precedents}
+\section{Theoretical Considerations: Notation and Precendents}
 \label{sec:theory}
 
-... There is abundant literature on the issue of shape and angular momentum
-aligmnent of dark matter haloe with respect to the cosmic web.
+There is abundant literature on the issue of shape and angular momentum
+aligmnent of dark matter haloe with respect to the cosmic web. In this
+paper we focus our attention on results published during the last
+decade that have made use of large N-body dark matter only
+cosmological simulations. There are many works that have addressed
+this problem using observational data from large surveys such as the
+Sloan Digital Sky Survey (SDSS), however we choose to narrow our
+discussion to simulation based studies which are prone to comparison.
 
-... This alignment is often measured from the distribution of the
-$\cos\theta$ where $\theta$ is the angle between the two axes of
-interest.
+Out of the three alignments that we study in this paper -shape,
+angular momentum and peculiar velocity- only the the first two have
+received wide attention in the literature, being angular momentum the
+most popular with twice the number of studies for shape alignment.
 
-... Table 1 and Table 2 summarizes recent results found in the literature for
-shape and angular momentum alignment. The Appendix includes a detailed
-description of each one the algorithms.
+These alignments are often measured from the distribution of the
+$\mu=\vert\cos\theta\vert$ where $\theta$ is the angle between the two axes of
+interest. This is often directly measuered as the absolute value of
+the dot product between the two unit vectors along the directions
+being tested, for instance in the case of angular momentum one would compute
+$\mu=\vert\hat{j}\cdot\hat{n}\vert$ In the case of shape alignments the major
+axis is the chosen direction to compare against the cosmic web.
 
-The main summary from these results can be done in three points. (i)
-The halo mass of $1-5\times 10^{12}$\hMsun is a threshold mass between
-different behaviours.  (ii) Halo shape is strongly aligned along
-filaments, more so for massive haloes and (iii) Halo spin tends to be
-perpendicular with respect to filaments, but it is a weak.
+For an isotropic ditribution of the vector around the direction defined by
+$\hat{n}$ the $\mu$ distribution, ranging between $0$ and $1$, should
+be flat and its mean value shoud be
+$\langle|mu|\rangle=0.5$. If a distribution is biased towards $1$
+($\langle\vert\mu\vert\rangle>0.5$) we call this an statistical
+alignment along $\hat{n}$, while in the case of a bias towards $0$
+($\langle\vert\mu\vert\rangle<0.5$) we talk about an anti-alignment,
+meaning an perpendicular orientations with respecto to the $\hat{n}$
+direction.
+
+\cite{Trowland2013} presented a parameterization for the $\mu$
+distribution in the case of angular momentm alignment based on
+theoretical considerations by \cite{Lee2005} (Eq. \ref{eq:distro} in
+the Appendix A). Under this parameterization it was found a unique
+correspondece between the full shape of the $\vert\mu\vert$
+distribution and its average. In this paper we use that result to only
+present the results for the average $\langle\vert\mu\vert\rangle$.
+
+Table 1 and Table 2 summarize recent results found in the literature for
+shape and angular momentum alignment. The Appendix A includes a detailed
+description of the definitions, algorithms and simulations used in
+each one of these studies. In these tables the first column describe
+the reference, the second column summarizes the web finding method
+with a single name, the third scale associates an spatial scale to the
+web finding methods, in most cases it corresponds to the grid size or
+smoothing scale used to interpolate the underlying matter density or
+velocity field; The fourth column indicates along which web element
+(filament or wall) was measured the alignment; the fifth scale
+indicates the strenght of the alignment/anti-alignment, $++$/$--$
+indicate a strong alignement/anti-alignment while $+$/$-$ indicate a
+weaker signal; the last columns indicates whether the described signal
+is only present in a defined range of halo mass.
+
+These results can be summarized in three important points:
+\begin{itemize}
+\item The halo mass of $1-5\times 10^{12}$\hMsun is a threshold mass between
+behaviours of no-alignment, alignment or anti-alignment.
+\item Halo shape provides a strong alignment signal along filaments
+  and sheets, more so for massive haloes. 
+\item Halo spin tends to be oriented perpendicular to filaments and
+parallel to sheets, but it is a weaker than shape alignment. 
+\end{itemize}
 
@@
   \right)\right]^{-3/2}, 
+\label{eq:distro}
 \end{equation}

### 2014-02-04 paper/main.tex
fixing references

@@
-\documentclass[usenatbib]{mn2e} 
+\documentclass[useAMS,usenatbib]{mn2e} 
 \usepackage{amsmath} 
@@
 \usepackage{epsfig}  
+\usepackage{hyperref} 
 \def\be{\begin{equation}}
@@
 \newcommand{\zz}{$z\sim 3$}
+
 \newcommand{\apj}{ApJ}  
@@
 
-\cite{Trowland2013} presented a parameterization for the $\mu$
+a \cite{Trowland2013} presented a parameterization for the $\mu$
 distribution in the case of angular momentm alignment based on
@@
 velocity field; The fourth column indicates along which web element
-(filament or wall) was measured the alignment; the fifth scale
+(filament or wall) was measured the alignment; the fifth colume
 indicates the strenght of the alignment/anti-alignment, $++$/$--$
@@
 weaker signal; the last columns indicates whether the described signal
-is only present in a defined range of halo mass.
+is present within a defined range of halo mass.
 
@@
 & & - &
-filament& $-$ & $>10^{12}$\hMsun\\\hline
+filament& $-$ & $>10^{12}$\hMsun\\
 
@@
 
-& &  $2.1$\hMpc &
-wall & $++$ & stronger $>10^{12}$\\\hline \hline
+& &  $2.1$ &
+wall & $++$ & stronger $>10^{12}$\hMsun\\\hline \hline
 
@@
 cosmological parameters in the simulation correspond to the results
-inferred from WMAP5 data, which are also consistent with the more
-recent results of WMAP9. These parameters are $\Omega_m=0.27$,
+inferred from WMAP5 data \citep{2009ApJS..180..306D}, which are also consistent with the more
+recent results of WMAP9 \citep{2013ApJS..208...19H}. These parameters are $\Omega_m=0.27$,
 $\Omega_{\Lambda} =0.73$, $\sigma_8=0.82$, $n_s=0.95$ and $h=0.70$ for the
@@
 conditions the mass of each dark matter particle in the simulation
-corresponds to $m_p=1.4\times 10^{8}$\hMsun.
+corresponds to $m_p=1.4\times 10^{8}$\hMsun. A more detailed
+description of the simulation can be found in
+\citep{2011ApJ...740..102K}.
 
@@
 the center of mass velocity.
+
+The halo data used in this paper is publicly available through the
+MultiDark
+database\footnote{\texttt{http://www.multidark.org/MultiDark/}} and is
+thoroughly described in \cite{2013AN....334..691R}.
 

### 2014-02-04 paper/main.tex
numerical considerations

@@
 
-\section{The cosmic web algorithms}
+\section{Web Finding Algorithms}
 \label{sec:algorithms}
-We use two algorithms to define the cosmic web on cosmological N-body
+
+We use two algorithms to define the cosmic web in cosmological N-body
 simulations. Both are based on the same algorithmic principle, which
-is determining locally a symmetric tensor which can be diagonalized to yield
+determines locally a symmetric tensor which can be diagonalized to yield
 three real eigenvalues $\lambda_1>\lambda_2>\lambda_3$ and their
@@
   e}_3$. This allows for a local classification into one of the
-following four categories: void, sheet, filament and peak depending
-whether the number of eigenvalues larger than a given threshold
+following four web types: void, sheet, filament and peak depending
+on the number of eigenvalues larger than a given threshold
 $\lambda_{th}$ is $3$, $2$, $1$ or $0$, respectively.
@@
 We use two different symmetric tensors. The first is the shear tensor,
-defined as the hessian of the gravitational potential, normalized in
+defined as the Hessian of the gravitational potential, normalized in
 such a way as to be dimensionless:
@@
 equation can be written as $\nabla^{2}\phi  = \delta$, where $\delta$
-is the matter overdensity, $\bar{\rho}$ is the averagematter density,
+is the matter overdensity, $\bar{\rho}$ is the average matter density,
 $H_{0}$ is the Hubble constant at present time and $\Omega_m$ is the
@@
 
-In this paper we compute the cosmic web on grids of two different
-resolutions $256^3$ and $512^3$. In the V-Web computations we compute
-the velocity field as follows. First we compute the momentum density field
-over a grid and the normalize it by the matter density field. We follow the
-same procedure for the gaussian smoothed fields. It means that a
-smoothed velocity fields is the ratio of the smoothed momentum density
-and matter density fields.
+In this paper we compute the cosmic web on cubic grids of two different
+resolutions $256^3$ and $512^3$. For the T-Web we interpolate first
+the matter density field using a Cloud-In-Cell (CIC) scheme. Then we
+smooth using a Gaussian kernel with a spatial variance equal to the
+size of one grid cell. This smoothed matter density field is
+transformed into Fourier space to solve the Poisson equation and find
+the gravitational potential $\phi$. The Hessian is computed a finite
+differences method. Finally, the eigenvalues and eigenvectors are
+computed on each grid point.
+
+For the V-Web we interpolate first the momentum density field over a
+grid using the CIC scheme and then apply a gaussian smoothing with a
+spatial variance of one grid cell. We use the matter density field,
+which is also CIC interpolated and gaussian smoothed, to normalize the
+momentum field. This ratio between the momentum and matter density
+field is what we consider as the velocity field to compute the shear
+tensor on each grid point. In this case we also compute the
+eigenvalues and eigenvectors on each grid point.
 

### 2014-02-04 paper/main.tex
section numerical experiments

@@
 
+\section{Our Numerical Experiments}
+In this paper we use the data and the methods described above to
+perform three diferent kinds of measurements.
+
+\subsection{Preferential Alignment}
+
+The first measurement is a rough approximation to find out along which
+axes are halos aligned. We call this Preferential Alignment (PA).
+
+We use the fact that for a given vector under study $\hat{a}$ and the
+tree eigenvectors the following identity holds
+
+\begin{equation}
+(\hat{s}\cdot\hat{e}_1)^2 +(\hat{s}\cdot\hat{e}_2)^2 +(\hat{s}\cdot\hat{e}_3)^2 =1.
+\end{equation}
+%
+Using this we know that all halos can be splitted into three groups:
+
+\begin{enumerate}
+\item Halos with $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_2)^2$
+  and $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_2)$, which can
+  be considered to aligned mostly along $\hat{e}_1$.
+\item Halos with $(\hat{s}\cdot\hat{e}_2)^2> (\hat{s}\cdot\hat{e}_2)^2$
+  and $(\hat{s}\cdot\hat{e}_2)^2> (\hat{s}\cdot\hat{e}_3)^2$, which can
+  be considered to aligned mostly along $\hat{e}_2$.
+\item Halos with $(\hat{s}\cdot\hat{e}_3)^2> (\hat{s}\cdot\hat{e}_1)^2$
+  and $(\hat{s}\cdot\hat{e}_3)^2> (\hat{s}\cdot\hat{e}_1)^2$, which can
+  be considered to aligned mostly along $\hat{e}_2$.
+\end{enumerate}
+
+If the halo population does not show any preferential alignment, then
+all the halos must be evenly distributed along these three
+populations. On the contrary, if there is more than one third of the
+halo population in one of these sets, then we can talk about a
+preferential alignment along one of the axis. However, this statistic 
+does not give a precise answer on the degree of the alignment
+
+\subsection{Average Alignment Angle}
+
+We emphasize that all the quantities that we compute in this paper are
+independent of any threshold on the eigenvalues that could be used to make a web
+clasification into web types. Instead, we focus on the alignments with
+respect to the eigenvectors regardless of the web type. In this
+context we recall that the eigenvector $\hat{e}_1$ is vector
+perpendicular to the plane defining a sheet and also a filamente and
+that $\hat{e}_3$ is the vector that marks the direction of a filament
+and lies on the plane of a sheet. Therefore we focus on quantifying
+the degree of alignment along these two eigenvectors.
+
+This experiment complements the results obtained by the PA satistic by
+computing the average and standard deviation of
+$\vert\langle\hat{s}\cdot\hat{e}_1\rangle\vert$ and
+$\vert\langle\hat{s}\cdot\hat{e}_3\rangle\vert$.  We perform this
+tests in differet populations split into different mass bins
+logarithmically spaced between $1\times 10^{9}$\hMsun and
+$1\times10^{14}$\hMsun.
+
+In a separate test we make the same measurements but this time
+splitting the halo sample by other properties such as:
+circularity, concentration, local matter density, spin and
+triaxiality. In this case we take the upper and lower $30\%$ of the
+halos according to each property and measure the strenght of the
+alignment by the average value of
+$\vert\langle\hat{s}\cdot\hat{e}_1\rangle\vert$ and
+$\vert\langle\hat{s}\cdot\hat{e}_3\rangle\vert$.
+
 \section{Results}
 \label{sec:results}
+
+\subsection{Preferential Alignment}
 
@@
 \end{figure*}
+
+Figure \ref{fig:preferential} presents all the results for the
+preferential alignment (PA).
 

### 2014-02-06 paper/main.tex
interweb alignment at the end
writing on preferential alignment

@@
 
-\title[Vweb \& Tweb]{Cosmic web correlations with the shape, spin and
-  peculiar velocties of dark matter halos}  
+\title[Cosmic web alignments with halos]{Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos}  
 \author[S. Contreras et al.]{
@@
 {\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
-filament &$++$ & all masses\hMsun\\
-&   & & 
-wall & $--$ & all masses\\\hline
+filament &$++$ & $>10^{12}$\hMsun\\
+&   & & 
+filament & $+$ & $<10^{12}$\hMsun\\
+
+&   & & 
+wall & $++$ & $>10^{12}$\hMsun\\
+
+&   & & 
+wall & $+$ & $<10^{12}$\hMsun\\\hline
 
 {\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ & 
-filament &$?$ & $>10^{12}$\hMsun\\
-&   & & 
-filament &$?$ & $<10^{12}$\hMsun\\
-&   & & 
-wall & $?$ & all masses\\\hline
+filament &$--$ & $>10^{12}$\hMsun\\
+&   & & 
+filament & none & $<10^{12}$\hMsun\\
+&   & & 
+wall & $--$ & $>10^{12}$\hMsun\\
+
+&   & & 
+wall & none & $<10^{12}$\hMsun\\\hline
 
@@
 \caption{Shape alignment with the cosmic web. Summary of theoretical
-  results provided by methods comparable to ours.}
+  results provided by methods similar to ours.}
 \end{table*}
@@
 \cite{Codis2012} & Morse Theory \& T-Web & $1-5$ & 
-filament & $--$ & $>10^{12}$\hMsun \\
-
-&   & & 
-filament & $++$ & $<10^{12}$\hMsun \\
+filament & $--$ & $>10^{12.5}$\hMsun \\
+
+&   & & 
+filament & $++$ & $<10^{12.5}$\hMsun \\
 
@@
 \caption{Spin alignment with the cosmic web. Summary of theoretical
-  results provided by methods comparable to ours.}
+  results provided by methods similar to ours.}
 
@@
   and the right the Vweb. Strong colors refer to $256^3$ grid
-  resolutions and lighter colors to a $512^3$ grid.
+  resolutions and lighter colors to a $512^3$ grid. The thick black
+  horizontal line at $0.33$ corresponds to the expected fraction for a
+  a random vector field.
 \label{fig:preferential}}
@@
 Figure \ref{fig:preferential} presents all the results for the
-preferential alignment (PA).
-
-\subsection{Interweb Alignment}
-
-In the first place we wish to directly compare the results of the two
-algorithms. For the two algorithms we have the information for the
-eigenvectors and the eigenvalues on exactly the same positions defined
-by the grids. This allows us tocompute the pair-wise allignment
-between the eigenvectors in the two web finders.
-
-We are mainly interested in the alginment of the web with
-the halos. Therefore we restrict our analysis to the grid cells that are
-occupied by halos. If we had decided to perform this kind of analysis
-on all the grid cells, the statistics would be dominated by the void
-regions, because the dominate in number the fraction of cells in the
-simuation.
-
-Figure \ref{fig:interweb} shows the results of the inter-web alignment
-as a function of halo mass. It clearly stands out that the
-eigenvectors are aligned for low mass halos but are close perpendicular to
-each other at the location of the most massive halos. There is a
-transition scale around $(10^{11.5}-10^{12.5})$\hMsun depending on the
-grid resolution. The coarse grid $(256^3)$shows the transition at higher masses
-than the fine grid $(512^3)$.
-
-For both resolutions, the halos more massiven than $10^{13}$\hMsun are
-locate in regions where the fastest momentum-weighted collapse
-direction (defined by the V-web) is perpendicular to the direction
-where the tidal compression is the highest.
-
-The fact that this trend is less evident at low resolution and low
-masses, hints that the flip is actually related to the overdensity
-values, i.e. to the degree of non-linearity, in the corresponding
-spatial scales.
-
-\begin{figure}
-\includegraphics[width=0.40\textwidth]{web.pdf}
-\caption{Median of the interweb alignment for the two grid
-  resolutions as a function of the dark matter mass corresponding to
-  the halos where the measurement was made. The error bars indicate
-  the lower and upper quartiles (Figure in color in the web version).
-\label{fig:interweb}} 
-\end{figure}
+preferential alignment (PA) summarizing to a good extent the main
+results of this paper.
+
+For shape alignment and the Tweb (upper row, right column) we find a strong
+preferential alignment along the third eigenvector $\vec{e}_{3}$. This
+signal incresases steadily with mass and is almost independent of the
+grid resolution. At high masses between $70\%$ and $100\%$ of the
+halos have their major axis aligned along $\vec{e}_{3}$ which means
+that they mostly lie along filaments and sheets.
+
+The shape alignment and the Vweb (upper row, left column) gives a
+different perspective. Firstly, there seems to be little evidence
+for an alignment for masses below $10^{11}-10^{12}$\hMsun, depending
+on the grid resolution. Secondly, the alignment at higher masses goes
+along the first eigenvector $\vec{e}_{1}$ meaning that they mostly lie
+perpendicular to the filaments and sheets. In the discussion section
+we clarify this result that at first might seem puzzling.
+
+For fhe angular momentum alignment and the Tweb (middle row, right
+column) we find that at low masses $<10^{12}$\hMsun no evidence for
+any alignment. At higher masses $>10^{12}$\hMsun there is weak signal
+of preferential alignment along the first and second eigenvectors,
+between $35\%$ to $45\%$ of the halos are aligned with respect to
+$\vec{e}_1$ and $\vec{e}_2$. Correspondingly, between $10\%$ to $20\%$
+of the halos are aligned along respect to $\vec{e}_{3}$. This means
+that most of the halos are perpendicular to the filaments and do not
+have a clear alignment with respect to walls.
+
+The angular momentum in the Vweb (middle row, left column) presents a
+a signal of alignment along the second eigenvector $\hat{e}_{2}$,
+between $45\%$ to $60\%$ of the halos are aligned along that
+direction. While there is a minority of halos aligned with
+$\vec{e}_{1}$.  There a clear change in trends around
+$10^{11}$\hMsun-$10^{12}$\hMsun depending on the grid resolution;
+below that mass range there is no evidence for alignment while at
+higher masses appear all the trends we describe. This means that most
+of the halos tend to lie along walls but do not have a clear alignment
+with respect to filaments.
 
@@
 tensors.
+
+\subsection{Interweb Alignment}
+
+In the first place we wish to directly compare the results of the two
+algorithms. For the two algorithms we have the information for the
+eigenvectors and the eigenvalues on exactly the same positions defined
+by the grids. This allows us tocompute the pair-wise allignment
+between the eigenvectors in the two web finders.
+
+We are mainly interested in the alginment of the web with
+the halos. Therefore we restrict our analysis to the grid cells that are
+occupied by halos. If we had decided to perform this kind of analysis
+on all the grid cells, the statistics would be dominated by the void
+regions, because the dominate in number the fraction of cells in the
+simuation.
+
+Figure \ref{fig:interweb} shows the results of the inter-web alignment
+as a function of halo mass. It clearly stands out that the
+eigenvectors are aligned for low mass halos but are close perpendicular to
+each other at the location of the most massive halos. There is a
+transition scale around $(10^{11.5}-10^{12.5})$\hMsun depending on the
+grid resolution. The coarse grid $(256^3)$shows the transition at higher masses
+than the fine grid $(512^3)$.
+
+For both resolutions, the halos more massiven than $10^{13}$\hMsun are
+locate in regions where the fastest momentum-weighted collapse
+direction (defined by the V-web) is perpendicular to the direction
+where the tidal compression is the highest.
+
+The fact that this trend is less evident at low resolution and low
+masses, hints that the flip is actually related to the overdensity
+values, i.e. to the degree of non-linearity, in the corresponding
+spatial scales.
+
+\begin{figure}
+\includegraphics[width=0.40\textwidth]{web.pdf}
+\caption{Median of the interweb alignment for the two grid
+  resolutions as a function of the dark matter mass corresponding to
+  the halos where the measurement was made. The error bars indicate
+  the lower and upper quartiles (Figure in color in the web version).
+\label{fig:interweb}} 
+\end{figure}
 

### 2014-02-06 paper/main.tex
starting to write the conclusions

@@
 \title[Cosmic web alignments with halos]{Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos}  
-\author[S. Contreras et al.]{
+\author[J.E. Forero-Romero et al.]{
 \parbox[t]{\textwidth}{\raggedright 
@@
 &   & & 
-wall & - & $>10^{12}$\hMsun\\\hline
+wall & none & $>10^{12}$\hMsun\\\hline
 
@@
 
-& &  $2.1$ &
-wall & $++$ & stronger $>10^{12}$\hMsun\\\hline \hline
+& & &
+wall& $+$ & $<10^{12}$\hMsun\\
+& &    &
+wall & $++$ & $>10^{12}$\hMsun\\\hline \hline
 
@@
 \begin{figure*}
-\includegraphics[width=0.9\textwidth]{Fig0.pdf}
+\includegraphics[width=0.8\textwidth]{Fig0.pdf}
 \caption{Fraction of halos in a mass bin that show a preferential
@@
   studies in this paper: shape (major axis), angular momentum and
-  peculiar velocity. Left column presents the results against the Tweb
-  and the right the Vweb. Strong colors refer to $256^3$ grid
+  peculiar velocity. Left column presents the results against the Vweb
+  and the right the Tweb. Strong colors refer to $256^3$ grid
   resolutions and lighter colors to a $512^3$ grid. The thick black
@@
 
+The peculiar velocities show a weak but consistent alignment along the
+third eigenvector $\vec{e}_{3}$ of the Tweb for all masses below
+$10^{13.0}$\hMsun-$10^{13.5}$\hMsun depending on the grid
+resolution. $45\%$ of the halos are aligned while only $25\%$ are
+aligned along the first eigenvector $\vec{e}_1$. This suggests that
+halos tend to move along filaments and parallel to the walls, except
+at higher masses where the alignments get randomized.  In contrast,
+the peculiar velocities with respect to the Vweb do not show any clear
+alignment trend.
+
+\subsection{Shape Alignment}
+
+\begin{figure*}
+\includegraphics[width=0.80\textwidth]{Fig2.pdf}
+\caption{Median of $\cos\theta$ quantifying the shape alignment for
+  the Vweb (left) and the Tweb (right) at two different grid
+  resolutions. In the upper (lower) panels the angle $\theta$ is
+  measured between the halo minor (major) axis and the first (third)
+  eigenvector.\label{fig:shape_alignment}} 
+\end{figure*}
+
+The shape alignment shows stronger trends. Figure
+\ref{fig:shape_alignment} presents the main results as a function of
+halo mass. In this case we characterize the shape by the direction
+determined by the major axis.
+
+In the case of the V-web we have a clear anti-alignment with respect
+to both first and third eigenvectors for massive halos
+$>10^{12}$\hMsun. This implies that a halo is typically perpendicular to 
+filaments and lies along the plane defined by a sheet. For low mass
+halos $<10^{12}$\hMsun we do not find any correlation with the
+cosmic web.
+
+The T-web shows alignment  trends starting at masses of
+$10^{10}$\hMsun, two orders of magnitude less than the V-web. In this
+case we see an alignment along the first and third eigenvectors. It
+means that halos in filamentary environments tend to be aligned with
+the filament, while halos in pancake environments are perpendicular to
+the sheet.
+
+The most massive halos showing the strongets alignment trends are not
+usually located in regions classified as peaks where all the
+eigenvectors are are positive, meaning that thre is
+collapse/compressive stress in all directions.
+
+In this situation we
+can interpret alignment both along the first and third eigenvector as
+a signature that most massive halos tend to be aligned midway between
+the first and second eigenvector, lying along the plane defined by the
+second eigenvector.
+
 \subsection{Angular Momentum Alignment}
@@
 
-\subsection{Shape Alignment}
-
-\begin{figure*}
-\includegraphics[width=0.80\textwidth]{Fig2.pdf}
-\caption{Median of $\cos\theta$ quantifying the shape alignment for
-  the Vweb (left) and the Tweb (right) at two different grid
-  resolutions. In the upper (lower) panels the angle $\theta$ is
-  measured between the halo minor (major) axis and the first (third)
-  eigenvector.\label{fig:shape_alignment}} 
-\end{figure*}
-
-The shape alignment shows stronger trends. Figure
-\ref{fig:shape_alignment} presents the main results as a function of
-halo mass. In this case we characterize the shape by the direction
-determined by the major axis.
-
-In the case of the V-web we have a clear anti-alignment with respect
-to both first and third eigenvectors for massive halos
-$>10^{12}$\hMsun. This implies that a halo is typically perpendicular to 
-filaments and lies along the plane defined by a sheet. For low mass
-halos $<10^{12}$\hMsun we do not find any correlation with the
-cosmic web.
-
-The T-web shows alignment  trends starting at masses of
-$10^{10}$\hMsun, two orders of magnitude less than the V-web. In this
-case we see an alignment along the first and third eigenvectors. It
-means that halos in filamentary environments tend to be aligned with
-the filament, while halos in pancake environments are perpendicular to
-the sheet.
-
-The most massive halos showing the strongets alignment trends are not
-usually located in regions classified as peaks where all the
-eigenvectors are are positive, meaning that thre is
-collapse/compressive stress in all directions.
-
-In this situation we
-can interpret alignment both along the first and third eigenvector as
-a signature that most massive halos tend to be aligned midway between
-the first and second eigenvector, lying along the plane defined by the
-second eigenvector.
-
 \subsection{Peculiar velocity Alignment}
@@
 \label{sec:conclusions}
+
+We have examined the alignment of shape, angular momentum and peculiar
+velocity of dark matter halos with respect to the cosmic
+web. We use publicly available data from two algorithms
+implemented on a large cosmological N-body simulation to study halo
+populations spanning five orders of magnitude in mass. The first
+algorithm uses the tidal field and the second the velocity shear, both
+present local results on scales of $0.5$\hMpc to $1.0$\hMpc.
 

### 2014-02-10 paper/main.tex
shape alignment subsection

@@
 \newcommand{\hs}{{\hspace{1mm}}} 
-
+\newcommand{\muavg}{\vert\langle\cos\theta\rangle\vert}
 % definition to produce a "less than or similar to" symbol
@@
 \caption{Fraction of halos in a mass bin that show a preferential
-  alignment with respect to an eigenvector for the three properties
-  studies in this paper: shape (major axis), angular momentum and
-  peculiar velocity. Left column presents the results against the Vweb
-  and the right the Tweb. Strong colors refer to $256^3$ grid
-  resolutions and lighter colors to a $512^3$ grid. The thick black
-  horizontal line at $0.33$ corresponds to the expected fraction for a
-  a random vector field.
+  alignment with respect to an eigenvector. Each row presents on of
+  the three properties studied in this paper: shape (major axis),
+  angular momentum and  peculiar velocity. Left column presents the
+  results against the Vweb   and the right the Tweb. Strong colors
+  refer to $256^3$ grid resolutions and lighter colors to a $512^3$
+  grid. The thick black horizontal line at $0.33$ corresponds to the
+  expected fraction for a random vector field.
 \label{fig:preferential}}
@@
 
+In the next subsections we present a complementary account of this
+results by presenting quantitative results of the average angle
+between vector pairs describing the alignments discussed so far.
+
 \subsection{Shape Alignment}
@@
   resolutions. In the upper (lower) panels the angle $\theta$ is
-  measured between the halo minor (major) axis and the first (third)
+  measured between the halo major axis and the first (third)
   eigenvector.\label{fig:shape_alignment}} 
@@
 
-The shape alignment shows stronger trends. Figure
-\ref{fig:shape_alignment} presents the main results as a function of
-halo mass. In this case we characterize the shape by the direction
-determined by the major axis.
-
-In the case of the V-web we have a clear anti-alignment with respect
-to both first and third eigenvectors for massive halos
-$>10^{12}$\hMsun. This implies that a halo is typically perpendicular to 
-filaments and lies along the plane defined by a sheet. For low mass
-halos $<10^{12}$\hMsun we do not find any correlation with the
-cosmic web.
-
-The T-web shows alignment  trends starting at masses of
+Figure \ref{fig:shape_alignment} presents the main results for the
+angles between the first and third eigenvectors and the major shape
+axis as a function of halo mass.
+
+In the case of the Vweb (left column) we have a clear alignment with
+respect to the first eigenvector at high masses $>10^{12}\hMsun$, with
+values $\muavg\approx 0.8$ well above the expected value of $0.5$ for
+random distribution. With respect to the third eigenvector we measure
+an anti-alignment with $\muavg\approx0.3$. For low masses
+$<10^{12}\hMsun$ we do not detect any aligmnent signal. This is 
+consistent with the PA results of massive halos
+perpendicular to filaments and parallel to walls.
+
+The Tweb (right column) show alignment trends starting at masses of
 $10^{10}$\hMsun, two orders of magnitude less than the V-web. In this
-case we see an alignment along the first and third eigenvectors. It
-means that halos in filamentary environments tend to be aligned with
-the filament, while halos in pancake environments are perpendicular to
-the sheet.
-
-The most massive halos showing the strongets alignment trends are not
-usually located in regions classified as peaks where all the
-eigenvectors are are positive, meaning that thre is
-collapse/compressive stress in all directions.
-
-In this situation we
-can interpret alignment both along the first and third eigenvector as
-a signature that most massive halos tend to be aligned midway between
-the first and second eigenvector, lying along the plane defined by the
-second eigenvector.
+case we measure an alignment along the third eigenvectors and an
+antialignment along the first eigenvector. In the later case at the
+highest mases $\muavg\approx 0.8$ while in the former $\muavg\approx
+0.2$. This strong alignment/antialignment signal mirrors the
+interpretation from the PA results that describe halos lying parallel
+both to filaments and walls.
 
@@
 \includegraphics[width=0.80\textwidth]{Fig3.pdf}
-\caption{Median of $\cos\theta$ quantifying the angular momentum
-  alingment for the Vweb (left) and the Tweb (right) at two different
+\caption{Median of $|\cos\theta|$ quantifying the angular momentum
+  alingment for the Vweb (left) and the Tweb (right) for two different
   grid resolutions. In the upper (lower) panels the angle $\theta$ is
@@
 
-We now take a look at the alignment of the halo spin with the cosmic
+We now take a look at the alignment of the angularwith the cosmic
 web. This characterization is done in terms of the angle between the

### 2014-02-10 paper/main.tex
subsection on the angular momentum

@@
 \begin{figure*}
-\includegraphics[width=0.80\textwidth]{Fig2.pdf}
+\includegraphics[width=0.75\textwidth]{Fig2.pdf}
 \caption{Median of $\cos\theta$ quantifying the shape alignment for
@@
 \begin{figure*}
-\includegraphics[width=0.80\textwidth]{Fig3.pdf}
+\includegraphics[width=0.75\textwidth]{Fig3.pdf}
 \caption{Median of $|\cos\theta|$ quantifying the angular momentum
@@
 
-We now take a look at the alignment of the angularwith the cosmic
-web. This characterization is done in terms of the angle between the
-angular momentum vector and the first/third eigenvector.
-
-Figure \ref{fig:spin_alignment} shows the results as a function of
-the halo mass. In the case of the V-web the trends can be summarized
-as follows. Low mass halos $10^{12}$\hMsun do not show any
-preferential alignment with the cosmic web. Halos more massive than
-this threshold have their spin slightly perpendicular to the
-direction defined by the first eigenvector (defining sheets) and
-uncorrelated to the third eigenvector (filament direction). This
-translates into a weak tendency for the spin to lie on the
-sheet-plane.
-
-In the case of the T-web there is a similar trend for low mass halos
-$10^{12}$\hMsun not to have any preferential direction with respect to
-the cosmic web. High mass halos present a weak alignment with the
-first eigen vector and anti-alignment with the third
-eigenvector. Summarizing, the spin of massive halos tends to be
-slightly perpendicular to filaments and sheets.
+We now take a look at the angular momentum alignment. Figure
+\ref{fig:spin_alignment} shows the results as a function of halo mass
+following the same panel distributio as in Figure
+\ref{fig:shape_alignment}. In all cases we see that these alignment
+trends are weaker than shape alignments. For the Vweb low mass halos
+$<10^{12}$\hMsun do not show any preferential alignment with the
+cosmic web. Halos more massive than this threshold have their angular
+momentum slightly perpendicular to the direction defined by the first
+eigenvector and uncorrelated to the third eigenvector. This translates
+into a weak tendency for the angular momentum to lie parallel to walls.
+
+In the case of the Tweb, the alignment for low mass halos $<10^{12}$\hMsun 
+is also absent. More massive halos present a weak alignment along
+first eigen vector and anti-alignment with the third eigenvector. This
+provides a quantitative expression of the results derived from the
+preferential alignment whereby the angular momentum is weakly
+perpendicular to filaments.
 
@@
 \begin{figure*}
-\includegraphics[width=0.80\textwidth]{Fig4.pdf}
+\includegraphics[width=0.75\textwidth]{Fig4.pdf}
 \caption{Median of $\cos\theta$ quantifying the peculiar velocity

### 2014-02-10 paper/main.tex
peculiar velocities

@@
 at higher masses where the alignments get randomized.  In contrast,
-the peculiar velocities with respect to the Vweb do not show any clear
-alignment trend.
+the peculiar velocities with respect to the Vweb show the same trend
+but weaker and only for low mass halos $<10^{12}$.
 
@@
 \includegraphics[width=0.75\textwidth]{Fig4.pdf}
-\caption{Median of $\cos\theta$ quantifying the peculiar velocity
-  alignment with the Vweb (left) and the Tweb (right) at two different
+\caption{Median of $\vert\cos\theta\vert$ quantifying the peculiar velocity
+  alignment with the Vweb (left) and the Tweb (right) for two different
   grid resolutions. In the upper (lower) panels the angle $\theta$ is
   measured between the first (third) eivenvector and a halo's peculiar
-  velocity.} 
+  velocity.
+\label{fig:velocity_alignment}} 
 \end{figure*}
 
-Possible conclusion. Prolateness follow concentration. In the Tweb
-Angular momentum alignment is influenced by spin at higher masses. In
-the Vweb angular momentum alginment is influenced by all factors. In
-the peculiar velocity alginment only spin seemss to have an effect.
+Figure \ref{fig:velocity_alignment} shows the results for peculiar
+velocities alignments. In the case of the Vweb, the peculiar
+velocities show a weak signal of aligmnent ($\muavg\approx0.55$)
+along the third eigenvector for low masses $<10^{12}$\Msun and a weak
+antialigment at higher masses. The strengt of the alignment also shows
+clear dependency on the grid size used to compute the web.
+
+The Tweb shows a stronger alignment with the third eignenvecor at all
+masses with $\muavg\approx0.6$ and an antialignment with the first
+eigenvector with $\muavg\approx 0.4$. In contrast to the Vweb results,
+these trends remain baiscally unchanged at all masses and grid
+resolutions, with only minor change for halos masses $>10^{13}$\hMsun.
 
@@
 spatial scales.
+
+Possible conclusion. Prolateness follow concentration. In the Tweb
+Angular momentum alignment is influenced by spin at higher masses. In
+the Vweb angular momentum alginment is influenced by all factors. In
+the peculiar velocity alginment only spin seemss to have an effect.
 

### 2014-02-11 paper/main.tex
starting the conclusions

@@
 
+In the first place we wish to directly compare the results of the two
+algorithms. For the two algorithms we have the information for the
+eigenvectors and the eigenvalues on exactly the same positions defined
+by the grids. This allows us tocompute the pair-wise allignment
+between the eigenvectors in the two web finders.
+
+We are mainly interested in the alginment of the web with
+the halos. Therefore we restrict our analysis to the grid cells that are
+occupied by halos. If we had decided to perform this kind of analysis
+on all the grid cells, the statistics would be dominated by the void
+regions, because the dominate in number the fraction of cells in the
+simuation.
+
+\subsection{Interweb Alignment}
+
+Perhaps the most striking result so far is that the two webs give
+different results for the alignment of massive halos. This is not
+completely unexpected given that the two algorithms are based on
+different physical premises to obtain the directions defining the
+eigenvectors. However, we investigate the origin of the different
+alignment statistics by studying the inter-web alignment.
+
+Figure \ref{fig:interweb} shows the values for $\muavg$ between the
+two $\vec{e}_1$ eigenvectors in the Tweb and the Vweb.  The Figure
+shows that there is an alignment, $\muavg\approx 1.0$, for low mass
+halos and an antialignment, $\muavg\approx 0.2$ for massive.
+
+The transitional scale is located around $(10^{11.5}-10^{12.5})$\hMsun
+depending on the grid resolution. The coarse grid $(256^3)$ shows the
+transition at higher masses than the fine grid $(512^3)$.   We also
+note that the alignment is weaker in the finer grid, ($\muavg\approx
+0.7$) than in the coarser grid ($\muavg\approx1.0$).
+
+These two facts (alignment at low masses and low grid resolution)
+points towards an explanation in terms of the  linear / non-linear
+growth of structure. When the alignment is present on linear scales
+the divergence of the velocity field is proportional to the
+overdensity, i.e. the trace of the shear field is proportional to the
+trace of the tidal field.
+
+On the scale where the halos more massiven than $10^{13}$\hMsun are
+located, the relationshop between the velocity shear and the tidal
+field changes. There, the fastest momentum-weighted collapse direction
+(defined by the V-web) is perpendicular to the direction where the
+tidal compression is the highest.
+
+\begin{figure}
+\includegraphics[width=0.40\textwidth]{web.pdf}
+\caption{Median of the interweb alignment for the two grid
+  resolutions as a function of the dark matter mass corresponding to
+  the halos where the measurement was made. The error bars indicate
+  the lower and upper quartiles (Figure in color in the web version).
+\label{fig:interweb}} 
+\end{figure}
+
 \subsection{What drives the alignment}
@@
 
+Possible conclusion. Prolateness follow concentration. In the Tweb
+Angular momentum alignment is influenced by spin at higher masses. In
+the Vweb angular momentum alginment is influenced by all factors. In
+the peculiar velocity alginment only spin seemss to have an effect.
+
 \begin{figure*}
@@
 
-\subsection{Interweb Alignment}
-
-In the first place we wish to directly compare the results of the two
-algorithms. For the two algorithms we have the information for the
-eigenvectors and the eigenvalues on exactly the same positions defined
-by the grids. This allows us tocompute the pair-wise allignment
-between the eigenvectors in the two web finders.
-
-We are mainly interested in the alginment of the web with
-the halos. Therefore we restrict our analysis to the grid cells that are
-occupied by halos. If we had decided to perform this kind of analysis
-on all the grid cells, the statistics would be dominated by the void
-regions, because the dominate in number the fraction of cells in the
-simuation.
-
-Figure \ref{fig:interweb} shows the results of the inter-web alignment
-as a function of halo mass. It clearly stands out that the
-eigenvectors are aligned for low mass halos but are close perpendicular to
-each other at the location of the most massive halos. There is a
-transition scale around $(10^{11.5}-10^{12.5})$\hMsun depending on the
-grid resolution. The coarse grid $(256^3)$shows the transition at higher masses
-than the fine grid $(512^3)$.
-
-For both resolutions, the halos more massiven than $10^{13}$\hMsun are
-locate in regions where the fastest momentum-weighted collapse
-direction (defined by the V-web) is perpendicular to the direction
-where the tidal compression is the highest.
-
-The fact that this trend is less evident at low resolution and low
-masses, hints that the flip is actually related to the overdensity
-values, i.e. to the degree of non-linearity, in the corresponding
-spatial scales.
-
-Possible conclusion. Prolateness follow concentration. In the Tweb
-Angular momentum alignment is influenced by spin at higher masses. In
-the Vweb angular momentum alginment is influenced by all factors. In
-the peculiar velocity alginment only spin seemss to have an effect.
-
-\begin{figure}
-\includegraphics[width=0.40\textwidth]{web.pdf}
-\caption{Median of the interweb alignment for the two grid
-  resolutions as a function of the dark matter mass corresponding to
-  the halos where the measurement was made. The error bars indicate
-  the lower and upper quartiles (Figure in color in the web version).
-\label{fig:interweb}} 
-\end{figure}
-
 \section{Conclusions}
@@
 We have examined the alignment of shape, angular momentum and peculiar
-velocity of dark matter halos with respect to the cosmic
-web. We use publicly available data from two algorithms
-implemented on a large cosmological N-body simulation to study halo
-populations spanning five orders of magnitude in mass. The first
-algorithm uses the tidal field and the second the velocity shear, both
-present local results on scales of $0.5$\hMpc to $1.0$\hMpc.
+velocity of dark matter halos with respect to the cosmic web. We use
+publicly available data from two algorithms implemented on a large
+cosmological N-body simulation to study halo populations spanning five
+orders of magnitude in mass. The first algorithm uses the tidal field
+and the second the velocity shear, both present local results on
+scales of $0.5$\hMpc to $1.0$\hMpc.
+
+We quantify the alignments in two complementary ways. The first one
+measures the fraction of halos in a poulation that is preferentially
+aligned with either one of the eigenvectors $\vec{e}_1$, $\vec{e}_2$
+or $\vec{e}_3$. The second method measures the average value of the
+angle between an eigenvector and the quantity of interest. These two
+measurements give us a complete picture for the different degrees of
+alignment in the cosmic web.
+
+We find that the strongest alignment occurs for the halo shape with
+respect to the Tweb. In this case the halos tend to align with the
+third eigenvector, $\vec{e}_3$, meaning that they lie along filaments
+and walls. This trend is gets stronger as the halo mass
+increases and agrees with all the results published so far. Instead,
+for the Vweb, there is only an antialignment for halos more massive
+than $10^{12}$\hMsun, a result that is presented here for the first
+time.
+
+A much weaker alignment signal is present for the angular momentum. In
+the Tweb only the most massive halos $>10^{12}$\hMsun are antialigned
+with respect to the filaments, while for the Vweb the massive halos
+are alignment with sheets. These results broadly agree with the
+published literature. Nevertheless, in the same publications there is an
+alignment/anti-alignment signal reported at lower halo masses
+$<10^{12}$\hMsun that we do not detect in our measurements.
+
+A new result from our study is the alignment for the peculiar
+velocities. Here we find a relatively strong signal of alignment along
+the direction defined by the third eigenvector and perpendicular to
+the first. This signal is very strong in the Tweb for all masses below
+$<10^{13}$\hMsun. This can be interpreted as a flow parallel to walls
+and filaments. In the case of the Vweb similar signal, albeit weaker,
+is present only for the low mass halos $<10^{12}$\hMsun.
+
+The different behaviour for the alignments of massive halos in the
+Tweb and the Vweb was tracked to a corresponding anti-alignment
+between the eigenvectors in the two webs.
 

### 2014-02-11 paper/main.tex
working on the conclusions

@@
 Tweb and the Vweb was tracked to a corresponding anti-alignment
-between the eigenvectors in the two webs.
+between the eigenvectors in the two web grids for massive halos
+$>10^{12}$\hMsun. For low mass halos the directions defined by the two
+webs point in the same direction. This trends can be interpreted as
+non-linear effects that appear in the two different physical
+descriptions for the cosmic web.
 

### 2014-02-13 paper/main.tex
fixing the abstract

@@
 
-We study
-the alignment of DM halos with the cosmic web as described by the
-tidal and velocity shear fields. We focus on the alignment of halos
-shape, spin and peculiar velocities. We use a cosmological N-body
-simulation that allows to study dark matter halos spanning four orders
-of magnitude in mass ($(10^{10}$-$10^{14}$) \hMsun and spatial
-scales of $(0.5$-$1.0)$\hMpc to define the cosmic web. After varying
-the numerical parameters in our experiments we find that the tidal
-field provides a robust description for the different kinds of
-alignments.  We measure a strong here is a strong alignment of the
-peculiar velocity field and the halo shape with the cosmic web defined
-by the tidal field. The results for the spin alignment are less
-significant. The shape alignment is stronger for halos that are either
- massive ($M>10^{12}$\hMsun), have large or are located in high
- density regions.
+We study the alignment of dark matter halos with the cosmic web as described by
+the tidal and velocity shear fields. We focus on the alignment of their
+shape, angular momentum and peculiar velocities. We use a cosmological N-body
+simulation that allows to study dark matter halos spanning almost five orders
+of magnitude in mass ($10^{9}$-$10^{14}$) \hMsun over spatial scales
+of $(0.5$-$1.0)$\hMpc to define the cosmic web. After varying the
+numerical parameters in our experiments we find that the strongest
+alignment is measured for the halo shape with respect to the web
+defined by the tidal field, with a stronger signal as the halo mass
+increases. For the angular momentum we find weaker alignment signals for
+halos more massive than $10^{12}$\hMsun both in the tidal and velocity
+shear descriptions. The peculiar velocities of halos show a strong
+alignment signal for the tidal web at all halo masses, while in the
+velocity shear description the signal is weaker an only present for
+halos less massive than $10^{12}$\hMsun. We also find that the main
+directions of stronger tidal tension and velocity shear coincide for
+halos below $10^{12}$\hMpc but are perpendicular to each other for
+halos more massive than this threshold.
 

### 2014-02-13 paper/main.tex
comments from Sergio

@@
 \newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
-        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
+        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$~}\fi}}   
 \newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
@@
 
-a \cite{Trowland2013} presented a parameterization for the $\mu$
+\cite{Trowland2013} presented a parameterization for the $\mu$
 distribution in the case of angular momentm alignment based on
@@
 \item Halos with $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_2)^2$
-  and $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_2)$, which can
+  and $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_3)$, which can
   be considered to aligned mostly along $\hat{e}_1$.
-\item Halos with $(\hat{s}\cdot\hat{e}_2)^2> (\hat{s}\cdot\hat{e}_2)^2$
+\item Halos with $(\hat{s}\cdot\hat{e}_2)^2> (\hat{s}\cdot\hat{e}_1)^2$
   and $(\hat{s}\cdot\hat{e}_2)^2> (\hat{s}\cdot\hat{e}_3)^2$, which can
@@
 \item Halos with $(\hat{s}\cdot\hat{e}_3)^2> (\hat{s}\cdot\hat{e}_1)^2$
-  and $(\hat{s}\cdot\hat{e}_3)^2> (\hat{s}\cdot\hat{e}_1)^2$, which can
-  be considered to aligned mostly along $\hat{e}_2$.
+  and $(\hat{s}\cdot\hat{e}_3)^2> (\hat{s}\cdot\hat{e}_2)^2$, which can
+  be considered to aligned mostly along $\hat{e}_3$.
 \end{enumerate}
@@
 different perspective. Firstly, there seems to be little evidence
-for an alignment for masses below $10^{11}-10^{12}$\hMsun, depending
+for an alignment for masses below $10^{11}-10^{12}\hMsun$, depending
 on the grid resolution. Secondly, the alignment at higher masses goes
@@
 
-For fhe angular momentum alignment and the Tweb (middle row, right
-column) we find that at low masses $<10^{12}$\hMsun no evidence for
-any alignment. At higher masses $>10^{12}$\hMsun there is weak signal
+For the angular momentum alignment and the Tweb (middle row, right
+column) we find that at low masses $<10^{12}\hMsun$ no evidence for
+any alignment. At higher masses $>10^{12}\hMsun$ there is weak signal
 of preferential alignment along the first and second eigenvectors,
@@
 $\vec{e}_{1}$.  There a clear change in trends around
-$10^{11}$\hMsun-$10^{12}$\hMsun depending on the grid resolution;
+$10^{11}\hMsun-10^{12}\hMsun$ depending on the grid resolution;
 below that mass range there is no evidence for alignment while at
@@
 third eigenvector $\vec{e}_{3}$ of the Tweb for all masses below
-$10^{13.0}$\hMsun-$10^{13.5}$\hMsun depending on the grid
+$10^{13.0}\hMsun-10^{13.5}\hMsun$ depending on the grid
 resolution. $45\%$ of the halos are aligned while only $25\%$ are
@@
 measured between the spin and the cosmic vorticity
-\citep{Libeskind2013a,Laigle2013}. This two facts are consistent with
+\citep{Libeskind2013b,Laigle2013}. This two facts are consistent with
 spin being produced by the non-symmetric part of the shear and tidal

### 2014-02-13 paper/main.tex
more text in the conclusions

@@
 \includegraphics[width=0.90\textwidth,angle=90]{all_cuts.pdf}
-\caption{The alignment is always taken with respect to the first eigenvector.}
+\caption{The alignment is always taken with respect to the third eigenvector.}
 \end{figure*}
@@
 descriptions for the cosmic web.
+
+We also performed a simple study to find evidence of halo properties,
+other than mass, in driving the alignments. We find that in the case of
+shape, halos located in high density regions or with a low value of
+the reduced spin parameter tend to show a stronger signal. This is
+more pronounced in the Tweb than in the Vweb. Concerning angular
+momentum we find that the antialignment signal is stronger for halos
+with high spin values. In the peculiar velocities we do not find any
+affect in the Tweb alignments.
 

### 2014-02-13 paper/main.tex
small additions

@@
 shape, halos located in high density regions or with a low value of
-the reduced spin parameter tend to show a stronger signal. This is
+the reduced spin parameter tend to show a stronger signal. This trend is
 more pronounced in the Tweb than in the Vweb. Concerning angular
@@
 with high spin values. In the peculiar velocities we do not find any
-affect in the Tweb alignments.
+effect in the Tweb alignments, and the results for the Vweb show a
+wide variations with grid resolution that impedes driving any strong
+conclusion.
 

### 2014-02-17 paper/main.tex
feeding the introduction

@@
 
-\title[Cosmic web alignments with halos]{Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos}  
+\title[Halo alignments with the cosmic web]{Cosmic web alignments with
+  the shape, angular momentum and peculiar velocities of dark matter
+  halos}   
 \author[J.E. Forero-Romero et al.]{
@@
 of $(0.5$-$1.0)$\hMpc to define the cosmic web. After varying the
-numerical parameters in our experiments we find that the strongest
-alignment is measured for the halo shape with respect to the web
-defined by the tidal field, with a stronger signal as the halo mass
-increases. For the angular momentum we find weaker alignment signals for
-halos more massive than $10^{12}$\hMsun both in the tidal and velocity
-shear descriptions. The peculiar velocities of halos show a strong
-alignment signal for the tidal web at all halo masses, while in the
-velocity shear description the signal is weaker an only present for
-halos less massive than $10^{12}$\hMsun. We also find that the main
-directions of stronger tidal tension and velocity shear coincide for
-halos below $10^{12}$\hMpc but are perpendicular to each other for
-halos more massive than this threshold.
+numerical parameters in our experiments we find that the halo shape
+and the tidal field web presents the strongest alignment with a signal
+that gets stronger as the halo mass increases. For the angular momentum we
+find alignment signals only halos more massive than $10^{12}$\hMsun
+both in the tidal and velocity shear descriptions. The peculiar
+velocities of halos show a strong alignment signal for the tidal web
+at all halo masses, while in the velocity shear description the signal
+is weaker an only present for halos less massive than
+$10^{12}$\hMsun. We also find that the main directions of stronger
+tidal tension and velocity shear coincide for halos below
+$10^{12}$\hMpc but are perpendicular to each other for halos more
+massive than this threshold.
 
@@
 
-The formation of large scale structure in the Universe proceeds by
-gravitational instability. This is an intrinsic anisotropic
-process. [Pancake formation ...]
-
-Numerical simulations allow the exploration of a deep nonlinear
-regime, following the formation of virialized dark matter halos, which
-host observable galaxies. Some characteristics of these halos have to
-be linked to the environment in which they formed. One way to studty
-the connection halo-environment is to quantify the degree of
-correlation between different halo properties and their surrounding
-density and velocity fields.
-
-Among the properties that are of interest we find the shape, spin and
-peculiar velocity. [Relevanc of dark matter halo shapes ...]
-[Relevance of halo spin ...] [Relevance of peculiar velocities]
-
-There is large tradition of theoretical precedents for the
-measurements of shape and spin alignment. In this \documentname we
-review most of these studyes and offer our own study with
-complementary numerical techniques and simulations. [Brief summary of
-  the appendix ...]
-
-We also present the results for the alignment of peculiar velocities
-with large scale structure. Such a study has received less atention in
-the literature. However, we consider that it presents relevant
-insights for the study of cosmic flows.
+There is a long observational tradition stuying galactic properties
+as a function of its large scale environment. In these situations the environment
+definition is based on quantities easily accesible to observations
+such as the number density. With the advenment of large
+surveys the visibility of the cosmic web is clear. As a consequence,
+in order to capture this filamentarity, the environment definition
+started to be more complex, involving shear properties of the galaxy
+density field or the reconstructuted dark matter density field.
+
+The emergence of this web like structure is a great success of large
+scale structure growth models based on gravitational
+instability. Using numerical simulations allows the time description
+of such structure together with the formation of the virialized dark
+matter halos, which in turn should host observable galaxies. The
+finding of gas filaments that feed galaxies is another theoretical
+hint that strenghten the expected connection between galactic
+properties ant their place in the cosmic web.
+
+Using high resolution simulations it has been stablished that halos of
+a given mass for earlier in denser regions; concentration, spin and
+shape also depend on the local density. In the last decade new
+algorithms have implemented cosmic web classifications that go beyond
+the local density by defining a location to be a peak, sheet, filament
+or void depending on the simmetry properties of the local dark matter
+distribution.
+
+There analytical frameworks, such as tidal torque theory, that
+aim at describing how galaxies gain angular momentum and expect a
+correlation of this quantity with the cosmic web. The observational
+studies that try to measure such correlations actually try to use as a
+proxy the observed shape of galaxies. In this respect it is useful to
+have a theoretical baseline for the correlations of angular momentum
+and shape with the cosmic web.
+
+In the same spirit of describing the place of galaxies within the
+cosmic web, there has been an revival of surveys that measure the
+cosmic flow patters in the Local Universe. Assuming the correspondence
+between the divergenec of the cosmic flow velocity field and the local
+matter overdensity (valid in the linear regime) one could construct
+accurate maps of the matter density from peculiar velocities. From
+this perspective is interesting to look at the expected alignment of
+the peculiar velocities.
+
+There is large tradition of alignment measurements of shape and
+angular momentum. The main result of these previous studies is that shape
+alignment is a robust measurement regardless of the methods and
+simulations. On the other hand, the results for the angular momentum
+differ in the degree of the alignment. In this \documentname we review
+most of these studyes and offer our own study with complementary
+numerical techniques and simulations.  We also present for the first
+time in the literature new results for the alignment of peculiar velocities
+with large scale structure.
 
@@
 \begin{figure*}
-\includegraphics[width=0.8\textwidth]{Fig0.pdf}
+\includegraphics[width=0.8\textwidth]{Fig1.pdf}
 \caption{Fraction of halos in a mass bin that show a preferential
@@
 \begin{figure}
-\includegraphics[width=0.40\textwidth]{web.pdf}
+\includegraphics[width=0.40\textwidth]{Fig5.pdf}
 \caption{Median of the interweb alignment for the two grid
@@
 
-Possible conclusion. Prolateness follow concentration. In the Tweb
+{\bf Possible conclusion. Prolateness follow concentration. In the Tweb
 Angular momentum alignment is influenced by spin at higher masses. In
 the Vweb angular momentum alginment is influenced by all factors. In
-the peculiar velocity alginment only spin seemss to have an effect.
+the peculiar velocity alginment only spin seemss to have an effect. }
 
 \begin{figure*}
-\includegraphics[width=0.90\textwidth,angle=90]{all_cuts.pdf}
+\includegraphics[width=0.90\textwidth,angle=90]{Fig6.pdf}
 \caption{The alignment is always taken with respect to the third eigenvector.}

### 2014-02-17 paper/main.tex
fixing the appendix

@@
 \citep{Libeskind2013} %various alignments
-Studies shape and spin alignment with the cosmic web defined by the
-velocity shear tensor method described in this paper.
-
-The simulation has $2048^3$ particles in a box of $250$\hMpc,
-corresponding to a particles mass of $1.3\times 10^{8}$\hMsun.  Halos
-are found using a FOF halo finder with $b=0.17$. The catalog only
-include halos more massiven than $3\times 10^{9}$\hMsun.
-
-The shape is defined from the reduced inertia tensor. Results are
-reported for three mass bins $M_{\rm vir}<10^{11.5}$\hMsun,
-$11^{11.5}<M_{\rm vir}<12^{12.5}\hMsun$ and $M_{\rm
-  vir}>12^{12.5}\hMsun$.
-
-The identification of the cosmic web is done on a grid of $256^3$ with
-a gaussian smoothing of $\sim 1$\hMpc over the velocity field. We
-define this velocity field as the ratio of a momentum density to the
-matter density field. The details of this approach are described in
-the Appendix .
-
-The aligmnet signal of the spin is very weak while the shape alignment
+Studies shape and angular momentum alignments with the cosmic web
+defined by the velocity shear tensor method described in this
+paper.
+
+\cite{Libeskind2013} also used the Bolshoi simulation and the halo
+catalogs we use in this work. Results are reported for three mass bins $M_{\rm
+  vir}<10^{11.5}$\hMsun, $11^{11.5}<M_{\rm vir}<12^{12.5}\hMsun$ and
+$M_{\rm  vir}>12^{12.5}\hMsun$.   The identification of the cosmic web
+is done on a grid of $256^3$ with a gaussian smoothing of $\sim
+1$\hMpc over the velocity field. The way they compute this smoothed
+velocity field differs from our computation. We do it based on the
+momentum density field while \cite{Libesking2013} do not take into
+account the mass in each cell.
+
+The aligmnet signal for the angular momentum is very weak while the shape alignment
 signal is very strong. The shape alignment is such that the eigenvector
@@
 In other words the major axis of a halo is aligned with a filament,
-and lies on the plane that define a sheet. However the spin is
-antialgined with the filament for massive halos and weakly aligned for
-low mass halos.
+and lies on the plane that define a sheet. The angular momentum is
+anti-aligned with the filament for massive halos and weakly aligned
+for low mass halos.
 

### 2014-02-18 paper/main.tex
Appendix A updated

@@
 \item
-\citep{Libeskind2013} %various alignments
-Studies shape and angular momentum alignments with the cosmic web
-defined by the velocity shear tensor method described in this
-paper.
-
-\cite{Libeskind2013} also used the Bolshoi simulation and the halo
+\cite{Libeskind2013} %various alignments
+
+They study the shape and angular momentum alignments with the cosmic
+web defined by the velocity shear tensor method described in this
+paper.  \cite{Libeskind2013} used the Bolshoi simulation and the halo
 catalogs we use in this work. Results are reported for three mass bins $M_{\rm
@@
 
-The aligmnet signal for the angular momentum is very weak while the shape alignment
-signal is very strong. The shape alignment is such that the eigenvector
-corresponding to the smallest eigenvalue is aligned with the major
-axis. This effect is stronger for more massive halos. 
-In other words the major axis of a halo is aligned with a filament,
-and lies on the plane that define a sheet. The angular momentum is
+The aligmnet signal for the angular momentum is weak while the shape
+alignmentsignal is very strong. The shape alignment is such that the
+eigenvector corresponding to the smallest eigenvalue is aligned with
+the major axis. This effect is stronger for more massive halos.  In
+other words the major axis of a halo is aligned with a filament, and
+lies on the plane that define a sheet. The angular momentum is
 anti-aligned with the filament for massive halos and weakly aligned
@@
 \item
-\citep{Trowland2013}
-
-The simulation is the millennium run, which has $2160^3$
-particles in a volume of $500$\hMpc on a side. This corresponds to a
-particle mass of $8.6\times 10^{8}$\hMsun. The catalog uses both halos
-and subhalos which were identified with SUBFIND. Only halos with more
-than 500 particles were kept to get a robust computation for the
-spin. For each halo the spin is defined as the sum of the angular
-momentum of each particle with respect to the center of mass.
+\cite{Trowland2013}
+
+They used the Millennium Run, which has $2160^3$ particles in a volume
+of $500$\hMpc on a side. This corresponds to a particle mass of
+$8.6\times 10^{8}$\hMsun. The catalog uses both halos and subhalos
+identified with SUBFIND. Only halos with more than 500 particles were
+kept to get a robust computation for the spin. The angular momentum is
+defined as the sum of the angular momentum of each particle with 
+respect to the center of mass.
 
 The method to define the filamentary structure is based on the
-eigenvalues of the hessian of the density.However the analysis are
-reported ona box of $300$\hMpc on a side. Four different gaussian
+eigenvalues of the hessian of the density.  However, the analysis is
+performed on a box of $300$\hMpc on a side. Four different gaussian
 smoothing scales are used: $2.0$, $3.0$ and $5.0$\hMpc.
 
-The authors report a slight alignment signal of spin against the
-principal filament axis. By fitting the following functional form to
-the $\cos(\theta)$ distribution
+By fitting the following functional form tothe $\cos(\theta)$ distribution
 
@@
 \end{equation}
-
+%
 they are able to quantify the degree of alignment ($c<0$) or
@@
 with a transition scale $M_{\star}=5.9\times 10^{12}$\Msun, there is
-an anti-alignment above this mass and an alignment below it.
+a weak alignment signal of the angular momentum against the
+principal filament axis for halos above that mass, for halos below
+that scale there is a weak anti-alignment.
 
 \item 
-\citep{Codis2012}
-Studies the alignment of the spin of dark matter halos relative to
+\cite{Codis2012}
+
+They studies the alignment of the angular momentum dark relative to
 the surrounding large scale structure and to the tidal tensor
@@
 particle mass of $7.7\times 10^9$\Msun. Halos are identified
-using a FoF algorithm with a linking legth of 0.2 keeping all halos
+using a FoF algorithm with a linking length of 0.2 keeping all halos
 with more than 40 particles, which sets the minimum halo mass to be
@@
 Skeleton to be the set of critical lines joining the maxima of the
-densit field through saddle points following the gradient. They also
-compute the hessinan of the potential over the smoothed density field
+density field through saddle points following the gradient. They also
+compute the hessian of the potential over the smoothed density field
 to get their eigenvectors.
 
-The spin of the halo is defined as $m_{p}\sum_{i}(r_i-\bar{r})\times
+The angular momentum of the halo is defined as $m_{p}\sum_{i}(r_i-\bar{r})\times
 (v_i-\bar{v})$ where $\bar{r}$ is the center of mass of the halo and
@@
 
-They measure the sping alignment with each one of the
-eigenvectors. With repecto to the minor eigenvector $e_{1}$ there is
-antialignement for masses $M>5\times10^{12}$\Msun and alignment for masses
-$<5\times 10^{12}$\Msun. With respect to the intermediate eigenvector $e_2$
+They measure the alignment with each one of the eigenvectors. With
+repecto to the minor eigenvector $\vec{e}_{3}$  (the filament direction) there is anti-alignement for masses $M>5\times10^{12}$\Msun and alignment for masses
+$<5\times 10^{12}$\Msun; with respect to the intermediate eigenvector $\vec{e}_2$
 there is a strong alignment at high masses and no alignment for low
-masses, with respecto the major eigenvector $e_{3}$ there is an
-anti-alignment signal at all masses. The results from the Skeleton
-algorithm are in perfect agreement with the results from the Tidal
-web.  The transitional mass is weakly dependent on the smoothing scale,
-varing between $1-5\times 10^{12}$\hMsun for smoothing scales between
-  $1.0-5.0$\hMpc.
+masses; with respect to the major eigenvector $\vec{e}_{1}$
+(normal to the wall plane) there is an anti-alignment signal at all
+masses. The results from the Skeleton algorithm are in
+agreement with the results from the Tidal web.  The transitional mass
+is weakly dependent on the smoothing scale, varing between $1-5\times
+10^{12}$\hMsun for smoothing scales between $1.0-5.0$\hMpc.
 
@@
 \citep{Zhang2009}
-Study the spin and shape alignment against filaments.
-
-They use a dark matter simulation with $1024^3$ DM particles in a
+
+They studied the angular momentum and shape alignment against
+filaments.  They used a dark matter simulation with $1024^3$ DM particles in a
 periodic box of $100$ \hMpc on a side. The particle mass is
@@
 distance. Only halos with more than 500 particles are retained for
-further analysis.
-
-The angular momentum is measured with positions repect to the center
-of mass and the shape is determined using the non-normalized moment of
-inertia tensor.
+further analysis. The angular momentum is measured with positions
+repect to the center of mass and the shape is determined using the
+non-normalized moment of inertia tensor.
 
@@
 define the direction of a filament. The first method uses the
-eigenvalues of the hessian density, howevere they define the filament
-direction with the eigenvector corresponding the single positive
+eigenvalues of the hessian density; they take the filament
+direction to be the eigenvector corresponding the single positive
 eigenvalue of the hessian. The second method used a line that
@@
 
-The characterization of the alingment with the $\cos(\theta)$
-statistic. For the method that uses the eigenvectors, they find that
-the strenght of the spin alignment decreases with halo mass. For the
+For the method that uses the eigenvectors, they find that the strenght
+of the angular momentum alignment decreases with halo mass. For the
 shape they study the alingment of the major axis with the
-filament. The find an alignment signal in all mass bins, with an stronger
-effect for more massive halos.
-
-In a final experiment they measure the spin alignment in four
-different samples that separated by the strength of the shape
-alignment. They find that halos anticorrelated in shape, show a strong
-sping correlation going to the extreme where there is a strong spin
-anticorrelation for halos with a strong shape correlation. This means
-that the halos with strong spin alignment are not the same halos
-showing strong shape alignment.
+filament. The find an alignment signal in all mass bins, with an
+stronger effect for more massive halos.
+
+In a final experiment they measure the angular momentum alignment in four
+different samples split by the strength of the shape alignment. They
+find that halos anti-aligned in shape, show a strong angular momentum
+correlation; and a strong angular momentum anti-alignment for halos
+with a strong shape alignment.
 
@@
 \citep{AragonCalvo2007} %angular momentum alignment
-The method is the Multi-scale Morphology Filter which is based on the
-Hessian matrix of the density field, where the density field is
-computed from the particle distribution using a Delaunay tesselation
-field estimatior (DTFE), which is self-adaptive. This allows them to
+
+The used the Multi-Scale Morphology Filter to describe th filamentary
+structure. The method is based on the Hessian matrix of the density
+field, which is computed from the particle distribution using a
+Delaunay tesselation field estimatior (DTFE). This allows them to
 identify clusters, filaments and walls.
 
-The simulation has $512^3$ particles in a cubic box of $150$\hMpc. The
+They used a simulation with $512^3$ particles in a cubic box of $150$\hMpc. The
 mass per particle is $2\times 10^{9}$\hMsun.  Halo identitification is
 done with the HOP algorithm. They keep halos with more than $50$
-partices and less than $5000$, defining a mass range of$1-100\times
-10^{11}$\hMsun.
-
-The principal axes of each halo are computed from the non-normalized
-inertia tensor. The inertian tensor and the angular momentum are
-computed with respect to the center of mass of the halo.
+particles and less than $5000$, defining a mass range of$1-100\times
+10^{11}$\hMsun. The principal axes of each halo are computed from the
+non-normalized inertia tensor. The inertia tensor and the angular
+momentum are computed with respect to the center of mass of the halo.
 
@@
 distinction between halos of more massive and less massive than
-$10^{12}$\hMsun.
-
-The halo spins tend to lie on the plane of the wall. This is stronger
-for massive halos.The effect for filaments is weaker: low mass halos
-tend to lieparallel to their host filament, while high mass halos tend
-to be perpendicular.
-
-Theres is a very strong effect for the principal axes of halos in
-filaments to be strongly correlated with the direction of the
-filaments. The minor axis tend to be perpendicular to the
-filament. This effect is stronger for larger halos.
-
-The effect in walls is less strong ,but still the minor axis tend to
-lie perpendicular to the wall, while the other axis then to lie over
-the wall. The effect is stronger for massive halos.
-
-They find that spins and shapes of dark matter halos are significantly
-correlated with each other and with the orientation of their host
-structures.
+$10^{12}$\hMsun. The angular momentum tends to lie along the plane of
+the wall, with a stronger alignment for massive halos. The effect for
+filaments is weaker, low mass halos tend to alignt along the filament,
+while high mass halos tend to be anti-aligned.
+
+For the shape they find a very strong alignment along filaments. In
+walls the major axis lies along the wall. Both alignments are stronger
+for massive halos.
 
 \item
+
 \citep{Hahn2007}% various alignments with the Tweb
-The method is the Tweb. They use three simulations each of $512^3$
+
+The used the Tweb method applied on three simulations each of $512^3$
 particles, with sizes $L_1=45$\hMpc, $L_2=90$\hMpc and
 $L_3=180$\hMpc, this corresponds to particle masses of $4.7, 38.0,
-300\times 10^7$\hMsun. The normalization is $\sigma_8=0.9$. Halo
-identification was done with a FOF algorithm with 0.2 times the
-interparticle distance. They consider halos of at least 300
-particles.
+300\times 10^7$\hMsun. Halo identification was done with a FOF
+algorithm with 0.2 times the interparticle distance. They considered
+halos of at least 300  particles.
 
@@
 obtained with a CIC interpolation and smoothed using a Gaussian
-Kernel. In the rest of the paper all the results correspond to a
-smoothing scale of $R_{s}=2.1$\hMpc.
-
-They Report on the angle between the halo
-angular momentum vector and the eigenvector corresponding to
-perpendicular directions to the sheets and the direction of the
-filaments. This is divided in two halo populations: $5\times 10^{10} -
-1.0\times 10^{12}$ and $>10^{12}$. There is a weak antialignment in
-the case of the filaments and a stronger anti-alignment in the case of
-the sheets. For the sheets the effect is stronger for the massive
-bin. In the filaments the alignment is weak regardless of the
-mass. They do not report any other significan statistic, but recognize
-that they suffer from small-number statistics in voids).
-
-They do not see any strong dependance of the environment in the
-shape. They do not measure the shape alinment.
-
-\item
-\citep{Brunino2007}
-Uses a DM only N-body simulation (the Millennium Run) to study the
-shape and angular momentum alignment with respect to large
-cosmological voids.
-
-The voids are found with a spherical void finder. This algorithm first
-looks for potential void centers in the underdense regions of the
-simulation. These positions define the centers of spheres that are
-empty of halos above a given mass threshold. Only voids with radius
-larger than $10$\hMpc were considered for further analysis.
-
-Halos were identified by linking particles with density exceeding 900
-times the background density in order to keep the analysis of shape
-and angular momentum on the core of the halo. Only halos with masses
-in the range $8.6\times 10^{11}\hMsun < M_{\mathrm h}< 8.6\times
-10^{12}\hMsun$ were included analized to measure their angular
-momentum and the inertia tensor, both in a non-normalized way.
-
-For the purpose of measuring alignments a second cut is imposed
-whereby only halos within a shell of radius $R_{\mathrm void}<r<1.05R_{\mathrm
-void}$. The alignment is then measured between the vector connecting
-the center of the void to the halo in question and the vector of
-interest.
-
-The results show that there is a strong alignment of halo shape in
-such a way that the major axis is parallel to the shell surrounding
-the void. In the case of angular momentum there is not a significant
-signal for alignment.
-
-\item
-\citep{Basilakos2006}
-Use a cosmological SPH+N-body simulation to measure the alignment of
-cluster halos with their parent supercluster. For both the cluster
-halos and parent super-cluster they define the shape via the
-non-normalized inertia tensor.  The find that strenght of the
-alignments increases with the degree of filamentarity of the
-supercluster.
-
-The simulation has $2\times 512^3$ particles in a box of side
-$500$\hMpc. The dark matter particle mass is $6.6\times
-10^{10}$\hMsun while for SPH particles is $1.2\times
-10^{10}$\hMsun. The halo finding is done with a FOF algorithm with a
-linking length of 0.17 and keep objects with more than 100 partcles.
-
-\item
-\citep{Lee2002}%Obs. spin alignment
-Observational measurement for the alignment of galaxy spin axes with
-the local tidal shear field. For the measurement of shear, we have used
-the Point Source Catalog Redshift (PSCz) survey (a complete redshift survey
-from the IRAS Point Source Catalog) data. This was done down to a
-radial comoving distance of $\sim 150$\hMpc.
-\item
-\citep{Hatton2001} %angular momentum alignment
-DM matter only simulation. $256^3$ particles, $100$\hMpc, particle
-mass. Look for alignment of angular momentum vectors with neighbohring
-structures or other massive structures. They match halos using close
-pair statistics. They do not find any evidence for a statistically
-significant mutual alignment of halos on any escale. 
+Kernel. All the results correspond to a smoothing scale of
+$R_{s}=2.1$\hMpc.
+
+They report on the angle between the halo angular momentum vector and
+the eigenvector corresponding to perpendicular directions to the
+sheets and the direction of the filaments. This is divided into two halo
+populations according to mass; low mass $5\times 10^{10} - 1.0\times 10^{12}$ and
+high mass $>10^{12}$. They find a weake anti-alignment for filaments
+and a stronger anti-alignment in the case of the sheets. For the
+sheets the effect is stronger for the massive bin. The anti-alignment
+along filaments is weak regardless of the mass. They do not report any
+other significan statistic, but recognize that they suffer from
+small-number statistics in voids.
+
 \end{itemize}

### 2014-02-24 paper/main.tex
updated abstract, affiliations

@@
 \vspace*{6pt}\\
-$^{1}$Uni A
-$^{2}$Uni B
+$^{1}$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
+No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
+$^{2}$Instituto de Astrofísica, Pontificia Universidad Católica,
+Av. Vicuña Mackenna 4860, Santiago, Chile\\
 }
@@
 numerical parameters in our experiments we find that the halo shape
-and the tidal field web presents the strongest alignment with a signal
-that gets stronger as the halo mass increases. For the angular momentum we
-find alignment signals only halos more massive than $10^{12}$\hMsun
-both in the tidal and velocity shear descriptions. The peculiar
-velocities of halos show a strong alignment signal for the tidal web
-at all halo masses, while in the velocity shear description the signal
-is weaker an only present for halos less massive than
-$10^{12}$\hMsun. We also find that the main directions of stronger
-tidal tension and velocity shear coincide for halos below
-$10^{12}$\hMpc but are perpendicular to each other for halos more
-massive than this threshold.
+and the tidal field web presents the strongest alignment along
+filaments and walls with a signal that gets stronger as the halo mass
+increases; in the case of the velocity shear only massive halos
+$>10^{12}$\hMsun tend to have their shapes be perpendicular to
+filaments and walls. For the angular momentum we find alignment
+signals only for halos more massive than $10^{12}$\hMsun both in the
+tidal and velocity shear webs where the preferences are to be
+perpendicular to filaments or parallel to walls,
+respectively. Finally, the peculiar velocities show a strong alignment
+for all halo masses to move along filaments and walls in the tidal
+web, while in the velocity shear the same alignment is present but
+weaker and only for halos less massive than $10^{12}$\hMsun. Most of
+the different signals between the two web description are due to the
+fact that that the main directions of stronger tidal tension and
+velocity shear coincide for halos below $10^{12}$\hMpc but are
+perpendicular to each other for halos more massive than this
+threshold.
 
@@
 \section{Our Numerical Experiments}
+
 In this paper we use the data and the methods described above to
-perform three diferent kinds of measurements.
+perform two kinds of measurements: the preferential alignment and the
+average value of the angle along the eigenvectors of interest.
+
+We note that we measure alignments along the eigenvectors of the
+cosmic web without defining first whether each point corresponds to a
+filament or a wall. Our motivation is two-fold. First, partitioning the
+simulation into web elements implies an choice as to what value to use
+for the parameter $\lambda_{\rm th}$; although, this has been done
+before we consider that
 

### 2014-02-24 paper/main.tex
minor updates

@@
 
-\begin{table}
-\begin{tabular}{lllll}
-Author & Web Method & Halo Finder & Major Axis & Correlation\\
-\end{tabular}
-SHAPE
-\end{table}
+A novel aspect of our study is the use of a
+single computational volume of a high resolution simulation to study
+the alignments. Equally important, is our focus to quantify to what
+extent  these results depend on the method used to define the cosmic
+web and the numerical choices to implement the algorithms.
 

### 2014-03-06 paper/main.tex
setting Discussion to zero
Nelson

@@
 simulation that allows to study dark matter halos spanning almost five orders
-of magnitude in mass ($10^{9}$-$10^{14}$) \hMsun over spatial scales
+of magnitude in mass ($10^{9}$-$10^{14}$) \hMsun {\bf and use} spatial scales
 of $(0.5$-$1.0)$\hMpc to define the cosmic web. After varying the
@@
 increases; in the case of the velocity shear only massive halos
-$>10^{12}$\hMsun tend to have their shapes be perpendicular to
+$>10^{12}$\hMsun tend to have their shapes %be
+ perpendicular to
 filaments and walls. For the angular momentum we find alignment
@@
 the different signals between the two web description are due to the
-fact that that the main directions of stronger tidal tension and
+fact that %that 
+the main directions of stronger tidal tension and
 velocity shear coincide for halos below $10^{12}$\hMpc but are
 perpendicular to each other for halos more massive than this
-threshold.
+threshold.  {\bf This clearly separates halos into those that live
+in sheets and filaments (lower masses) and nodes of the cosmic web.}
 
@@
 There is a long observational tradition stuying galactic properties
-as a function of its large scale environment. In these situations the environment
-definition is based on quantities easily accesible to observations
-such as the number density. With the advenment of large
+as a function of {\bf their} large scale environment. In these situations the environment
+definition is {\bf usually} based on quantities easily accesible to observations
+such as the number density. With the {\bg advent}%advenment 
+of large
 surveys the visibility of the cosmic web is clear. As a consequence,
@@
 scale structure growth models based on gravitational
-instability. Using numerical simulations allows the time description
-of such structure together with the formation of the virialized dark
+instability. %Using 
+Numerical simulations allow the time description
+of such structures together with the formation of the virialized dark
 matter halos, which in turn should host observable galaxies. The
 finding of gas filaments that feed galaxies is another theoretical
-hint that strenghten the expected connection between galactic
+hint that strenghtened the expected connection between galactic
 properties ant their place in the cosmic web.
 
-Using high resolution simulations it has been stablished that halos of
-a given mass for earlier in denser regions; concentration, spin and
+{\bf With the aid of} high resolution simulations it has been established that halos of
+a given mass form earlier in denser regions; concentration, spin and
 shape also depend on the local density. In the last decade new
@@
 
-There analytical frameworks, such as tidal torque theory, that
+There {\bf are} analytical frameworks, such as tidal torque theory, that
 aim at describing how galaxies gain angular momentum and expect a
@@
 cosmic web, there has been an revival of surveys that measure the
-cosmic flow patters in the Local Universe. Assuming the correspondence
-between the divergenec of the cosmic flow velocity field and the local
+cosmic flow patterns in the Local Universe. Assuming the correspondence
+between the divergence of the cosmic flow velocity field and the local
 matter overdensity (valid in the linear regime) one could construct
 accurate maps of the matter density from peculiar velocities. From
-this perspective is interesting to look at the expected alignment of
+this perspective it is interesting to look at the expected alignment of
 the peculiar velocities.
@@
 The structure of this \documentname is the following. In \S
-\ref{sec:theory} we present the theoretical antecedendts for the
+\ref{sec:theory} we present the theoretical antecedents for the
 alignment studies we present in this paper. In \S
 \ref{sec:nbody} we present the N-body
-cosmological simulation and halo catalogs next to describe in
+cosmological simulation and halo catalogs.  Next, we describe in
 \S\ref{sec:algorithms} the two web-finding algorithms we use. In
@@
 There is abundant literature on the issue of shape and angular momentum
-aligmnent of dark matter haloe with respect to the cosmic web. In this
+alignment of dark matter halos with respect to the cosmic web. In this
 paper we focus our attention on results published during the last
@@
 ($\langle\vert\mu\vert\rangle<0.5$) we talk about an anti-alignment,
-meaning an perpendicular orientations with respecto to the $\hat{n}$
+meaning a perpendicular orientation with respect to the $\hat{n}$
 direction.
@@
 theoretical considerations by \cite{Lee2005} (Eq. \ref{eq:distro} in
-the Appendix A). Under this parameterization it was found a unique
-correspondece between the full shape of the $\vert\mu\vert$
-distribution and its average. In this paper we use that result to only
-present the results for the average $\langle\vert\mu\vert\rangle$.
+the Appendix A). Under this parameterization a unique
+correspondece was found between the full shape of the $\vert\mu\vert$
+distribution and its average. In this paper we follow the lines of their work but
+only present the results for the average $\langle\vert\mu\vert\rangle$.
 
@@
 description of the definitions, algorithms and simulations used in
-each one of these studies. In these tables the first column describe
+each one of these studies. In these tables the first column describes
 the reference, the second column summarizes the web finding method
-with a single name, the third scale associates an spatial scale to the
+with a single name, the third scale associates a spatial scale to the
 web finding methods, in most cases it corresponds to the grid size or
@@
 spectrum, the slope in the spectrum of the primordial matter
-fluctuation and the dimensionless Hubble constant. With this
+fluctuation and the dimensionless Hubble constant. With these
 conditions the mass of each dark matter particle in the simulation
@@
 matter density parameter. A detailed presentation of this algorithm
-can be found in \citep{Tweb}.
+can be found in \cite{Tweb}.
 
@@
 Hubble constant $-\nabla\cdot {\bf}v /H_{0}$. A detailed description
-of this algorithm can be found in \citep{Vweb}.
+of this algorithm can be found in \cite{Vweb}.
 
@@
 In this paper we compute the cosmic web on cubic grids of two different
-resolutions $256^3$ and $512^3$. For the T-Web we interpolate first
+resolutions $256^3$ and $512^3$ that roughly correspond
+to scales of $1$ and $0.5$h$^{-1}$Mpc, respectively. For the T-Web we interpolate first
 the matter density field using a Cloud-In-Cell (CIC) scheme. Then we
@@
 transformed into Fourier space to solve the Poisson equation and find
-the gravitational potential $\phi$. The Hessian is computed a finite
+the gravitational potential $\phi$. The Hessian is computed using a finite
 differences method. Finally, the eigenvalues and eigenvectors are
@@
 filament or a wall. Our motivation is two-fold. First, partitioning the
-simulation into web elements implies an choice as to what value to use
+simulation into web elements implies a choice as to what value to use
 for the parameter $\lambda_{\rm th}$; although, this has been done
-before we consider that
+before we consider that  COMPLETAR...
 
@@
 halo population in one of these sets, then we can talk about a
-preferential alignment along one of the axis. However, this statistic 
+preferential alignment along one of the axes. However, this statistics
 does not give a precise answer on the degree of the alignment
@@
 context we recall that the eigenvector $\hat{e}_1$ is vector
-perpendicular to the plane defining a sheet and also a filamente and
+perpendicular to the plane defining a sheet and also a filament and
 that $\hat{e}_3$ is the vector that marks the direction of a filament
@@
 $\vert\langle\hat{s}\cdot\hat{e}_1\rangle\vert$ and
-$\vert\langle\hat{s}\cdot\hat{e}_3\rangle\vert$.  We perform this
-tests in differet populations split into different mass bins
+$\vert\langle\hat{s}\cdot\hat{e}_3\rangle\vert$.  We perform these
+tests in different populations split into different mass bins
 logarithmically spaced between $1\times 10^{9}$\hMsun and
@@
 
+CAMBIE EL ORDEN DE PARRAFOS PARA QUE LA FIGURA SE LEA DE IZQ A DERECHA:
+
+The shape alignment and the Vweb (upper row, left column) gives a
+different perspective. Firstly, there seems to be little evidence
+for an alignment for masses below $10^{11}-10^{12}\hMsun$, depending
+on the grid resolution. Secondly, the alignment at higher masses goes
+along the first eigenvector $\vec{e}_{1}$ meaning that they mostly lie
+perpendicular to the filaments and sheets. In the discussion section
+we clarify this result that at first sight might seem puzzling.
+
 For shape alignment and the Tweb (upper row, right column) we find a strong
@@
 
-The shape alignment and the Vweb (upper row, left column) gives a
-different perspective. Firstly, there seems to be little evidence
-for an alignment for masses below $10^{11}-10^{12}\hMsun$, depending
-on the grid resolution. Secondly, the alignment at higher masses goes
-along the first eigenvector $\vec{e}_{1}$ meaning that they mostly lie
-perpendicular to the filaments and sheets. In the discussion section
-we clarify this result that at first might seem puzzling.
+The angular momentum in the Vweb (middle row, left column) presents a
+a signal of alignment along the second eigenvector $\hat{e}_{2}$;
+between $45\%$ to $60\%$ of the halos are aligned along that
+direction, while there is a minority of halos aligned with
+$\vec{e}_{1}$.  There is a clear change in trends around
+$10^{11}\hMsun-10^{12}\hMsun$ depending on the grid resolution;
+below that mass range there is no evidence for alignment while at
+higher masses all the trends we describe are aparent. This means that most
+of the halos tend to lie along walls but do not have a clear alignment
+with respect to filaments.
 
 For the angular momentum alignment and the Tweb (middle row, right
-column) we find that at low masses $<10^{12}\hMsun$ no evidence for
-any alignment. At higher masses $>10^{12}\hMsun$ there is weak signal
-of preferential alignment along the first and second eigenvectors,
+column) we find no evidence for any alighment at low masses $<10^{12}\hMsun$.
+At higher masses $>10^{12}\hMsun$ there is a weak signal
+of preferential alignment along the first and second eigenvectors;
 between $35\%$ to $45\%$ of the halos are aligned with respect to
 $\vec{e}_1$ and $\vec{e}_2$. Correspondingly, between $10\%$ to $20\%$
-of the halos are aligned along respect to $\vec{e}_{3}$. This means
+of the halos are aligned along $\vec{e}_{3}$. This means
 that most of the halos are perpendicular to the filaments and do not
@@
 
-The angular momentum in the Vweb (middle row, left column) presents a
-a signal of alignment along the second eigenvector $\hat{e}_{2}$,
-between $45\%$ to $60\%$ of the halos are aligned along that
-direction. While there is a minority of halos aligned with
-$\vec{e}_{1}$.  There a clear change in trends around
-$10^{11}\hMsun-10^{12}\hMsun$ depending on the grid resolution;
-below that mass range there is no evidence for alignment while at
-higher masses appear all the trends we describe. This means that most
-of the halos tend to lie along walls but do not have a clear alignment
-with respect to filaments.
-
-The peculiar velocities show a weak but consistent alignment along the
+The peculiar velocities (lower panels) show a weak but consistent alignment along the
 third eigenvector $\vec{e}_{3}$ of the Tweb for all masses below
 $10^{13.0}\hMsun-10^{13.5}\hMsun$ depending on the grid
-resolution. $45\%$ of the halos are aligned while only $25\%$ are
+resolution. $45\%$ of the halos are aligned this way, while only $25\%$ are
 aligned along the first eigenvector $\vec{e}_1$. This suggests that
@@
 at higher masses where the alignments get randomized.  In contrast,
-the peculiar velocities with respect to the Vweb show the same trend
-but weaker and only for low mass halos $<10^{12}$.
-
-In the next subsections we present a complementary account of this
+the peculiar velocities with respect to the Vweb show the same, although weaker, trend
+and only for low mass halos $<10^{12}$.
+
+In the next subsections we present a complementary account of these
 results by presenting quantitative results of the average angle
@@
   measured between the halo major axis and the first (third)
-  eigenvector.\label{fig:shape_alignment}} 
+  eigenvector.\label{fig:shape_alignment}.  SUGIERO PONER AMBAS LEYENDAS EN UN SOLO PANEL, SINO PARECE QUE
+IZQUIERDA Y DERECHA FUERAN PARA DOS RESOLUCIONES DISTINTAS.} 
 \end{figure*}
@@
 respect to the first eigenvector at high masses $>10^{12}\hMsun$, with
-values $\muavg\approx 0.8$ well above the expected value of $0.5$ for
+values $\muavg\approx 0.8$ well above the expected value of $0.5$ for a
 random distribution. With respect to the third eigenvector we measure
@@
 
-The Tweb (right column) show alignment trends starting at masses of
-$10^{10}$\hMsun, two orders of magnitude less than the V-web. In this
-case we measure an alignment along the third eigenvectors and an
-antialignment along the first eigenvector. In the later case at the
-highest mases $\muavg\approx 0.8$ while in the former $\muavg\approx
+The Tweb (right column) shows alignment trends starting at masses of
+$10^{10}$\hMsun, two orders of magnitude below than the V-web. In this
+case we measure an alignment along the third eigenvector and an
+antialignment along the first eigenvector. In the latter case at the
+highest mases $\muavg\approx 0.8$, while in the former $\muavg\approx
 0.2$. This strong alignment/antialignment signal mirrors the
@@
 \ref{fig:spin_alignment} shows the results as a function of halo mass
-following the same panel distributio as in Figure
+following the same panel layout as in Figure
 \ref{fig:shape_alignment}. In all cases we see that these alignment
-trends are weaker than shape alignments. For the Vweb low mass halos
+trends are weaker than the shape alignments. For the Vweb low mass halos
 $<10^{12}$\hMsun do not show any preferential alignment with the
@@
 momentum slightly perpendicular to the direction defined by the first
-eigenvector and uncorrelated to the third eigenvector. This translates
+eigenvector and are uncorrelated with the third eigenvector. This translates
 into a weak tendency for the angular momentum to lie parallel to walls.
@@
 is also absent. More massive halos present a weak alignment along
-first eigen vector and anti-alignment with the third eigenvector. This
+first eigenvector and anti-alignment with the third eigenvector. This
 provides a quantitative expression of the results derived from the
@@
 
-\subsection{Peculiar velocity Alignment}
+\subsection{Peculiar Velocity Alignment}
 
@@
 along the third eigenvector for low masses $<10^{12}$\Msun and a weak
-antialigment at higher masses. The strengt of the alignment also shows
-clear dependency on the grid size used to compute the web.
+antialignment at higher masses. The strength of the alignment also shows
+a clear dependency on the grid size used to compute the web.
 
@@
 eigenvector with $\muavg\approx 0.4$. In contrast to the Vweb results,
-these trends remain baiscally unchanged at all masses and grid
-resolutions, with only minor change for halos masses $>10^{13}$\hMsun.
-
-In the first place we wish to directly compare the results of the two
-algorithms. For the two algorithms we have the information for the
-eigenvectors and the eigenvalues on exactly the same positions defined
-by the grids. This allows us tocompute the pair-wise allignment
-between the eigenvectors in the two web finders.
-
-We are mainly interested in the alginment of the web with
-the halos. Therefore we restrict our analysis to the grid cells that are
-occupied by halos. If we had decided to perform this kind of analysis
-on all the grid cells, the statistics would be dominated by the void
-regions, because the dominate in number the fraction of cells in the
-simuation.
-
+these trends remain basically unchanged at all masses and grid
+resolutions, with only minor changes for halos masses $>10^{13}$\hMsun.
+
+MOVI EL TITULO DE LA SUBSECCION AQUI, ESTABA DOS PARRAFOS MAS ABAJO, PERO TAMBIEN MODIFIQUE EL TEXTO INICIAL
 \subsection{Interweb Alignment}
-
-Perhaps the most striking result so far is that the two webs give
-different results for the alignment of massive halos. This is not
-completely unexpected given that the two algorithms are based on
-different physical premises to obtain the directions defining the
-eigenvectors. However, we investigate the origin of the different
-alignment statistics by studying the inter-web alignment.
-
-Figure \ref{fig:interweb} shows the values for $\muavg$ between the
-two $\vec{e}_1$ eigenvectors in the Tweb and the Vweb.  The Figure
-shows that there is an alignment, $\muavg\approx 1.0$, for low mass
-halos and an antialignment, $\muavg\approx 0.2$ for massive.
-
-The transitional scale is located around $(10^{11.5}-10^{12.5})$\hMsun
-depending on the grid resolution. The coarse grid $(256^3)$ shows the
-transition at higher masses than the fine grid $(512^3)$.   We also
-note that the alignment is weaker in the finer grid, ($\muavg\approx
-0.7$) than in the coarser grid ($\muavg\approx1.0$).
-
-These two facts (alignment at low masses and low grid resolution)
-points towards an explanation in terms of the  linear / non-linear
-growth of structure. When the alignment is present on linear scales
-the divergence of the velocity field is proportional to the
-overdensity, i.e. the trace of the shear field is proportional to the
-trace of the tidal field.
-
-On the scale where the halos more massiven than $10^{13}$\hMsun are
-located, the relationshop between the velocity shear and the tidal
-field changes. There, the fastest momentum-weighted collapse direction
-(defined by the V-web) is perpendicular to the direction where the
-tidal compression is the highest.
 
@@
 
+Perhaps the most striking result so far is that the two webs give
+different results for the alignment of massive halos. This is not
+completely unexpected given that the two algorithms are based on
+different physical premises to obtain the directions defining the
+eigenvectors. However, we investigate the origin of the different
+alignment statistics by studying the inter-web alignment.
+
+%We also wish to directly compare the results of the two
+%web tensor algorithms. 
+For the two algorithms, Tweb and Vweb, we have the information for their
+eigenvectors and eigenvalues on exactly the same positions defined
+by the grids. This allows us tocompute the pair-wise alignment
+between the eigenvectors in the two web finders.
+
+We are mainly interested in the alignment of the web near
+halos. Therefore we restrict our analysis to the grid cells that are
+occupied by halos. Otherwise, if we decided to perform this kind of analysis
+on all the grid cells, the statistics would be dominated by the void
+regions, because they dominate in number the fraction of cells in the
+simuation.
+
+Figure \ref{fig:interweb} shows the values for $\muavg$ between the
+two $\vec{e}_1$ eigenvectors in the Tweb and the Vweb.  The Figure
+shows that there is an alignment, $\muavg\approx 1.0$, for low mass
+halos and an antialignment, $\muavg\approx 0.2$ for massive ones.
+
+The transitional scale is located around $(10^{11.5}-10^{12.5})$\hMsun
+depending on the grid resolution. The coarse grid $(256^3)$ shows the
+transition at higher masses than the fine grid $(512^3)$.   We also
+note that the alignment is weaker in the finer grid, ($\muavg\approx
+0.7$) than in the coarser grid ($\muavg\approx1.0$).
+
+These two facts (alignment at low masses and low grid resolution)
+points towards an explanation in terms of the  linear / non-linear
+growth of structure. When the alignment is present on linear scales
+the divergence of the velocity field is proportional to the
+overdensity, i.e. the trace of the shear field is proportional to the
+trace of the tidal field.
+
+On the scale where the halos more massive than $10^{13}$\hMsun are
+located, the relationship between the velocity shear and the tidal
+field changes. There, the fastest momentum-weighted collapse direction
+(defined by the V-web) is perpendicular to the direction where the
+tidal compression is the highest.
+
 \subsection{What drives the alignment}
@@
 For each mass interval we perform cuts in the following properties:
-spin, concentration, triaxiallity, circularity  and density. We
+halo spin, concentration, halo triaxiallity defined as $(A^2-B^2)/(A^2-C^2)$ with
+high (low) triaxiality corresponding to prolate (oblate) shapes, circularity ($C/A$)  and halo
+inner density (virial mass divided by volume out to the virial radius). We
 measure the web alignments in two sets, each one including the $30\%$
@@
 
-{\bf Possible conclusion. Prolateness follow concentration. In the Tweb
-Angular momentum alignment is influenced by spin at higher masses. In
-the Vweb angular momentum alginment is influenced by all factors. In
-the peculiar velocity alginment only spin seemss to have an effect. }
+Figure \ref{fig:drive} shows the results for the major axes of
+the Vweb and Tweb (left and right panels) and the major axis,
+the angular momentum vector, and the halo peculiar velocity (top, middle
+and bottom panels, respectively).  As here we show the average
+of the halo population above the lower mass limit imposed, the halo masses that dominate the
+statistics are close to this lower limit $~10^{11}\hMsun$.
+We show the result for the Twev and Vweb calculated using the two available
+resolutions, but as can be seen in general we find no significant differences in our results.
+
+As can be seen, halos with higher circularity and inner density show
+a higher alignment with the Vweb major axes.  The oposite is the case
+of haloes with higher concentration, spin and triaxiality.  This trend
+is also visible in the angular momentum vs. Vweb major axis alignment only
+for the concentration and spin, with little differences evidenced by the
+other halo properties.  And the alignment strengthening is somewhat
+reversed when comparing the Vweb with the halo peculiar velocity,
+with some evidence for a strengthening with lower circularity and
+inner density, and a weakening with spin and triaxiality.
+
+On the right panels the trends can also be readily seen.  The Tweb
+vs. major axis alignments are stronger for higher circularity,
+concentration and inner density, and weaker for higher spins and
+triaxialities.  With respect to the angular momentum, the alignment
+is weaker for higher circularities, concentrations, inner densities and
+spins, and is only strengthened when the triaxiality is higher.
+Not much difference is seen in the Tweb vs. halo peculiar velocity
+alignments, being this the only regime where there is a clear difference
+in influence of halo properties on the alignments with the Tweb and Vweb;
+the latter do show important changes on the lower-left panel.
+
+As can be seen, higher concentrations, circularities and densities,
+as well as lower spins and triaxialities, produce a similar effect on the
+Tweb vs. major axis alignmets similar to that of diminishing the mass
+of the halos.  This has also been detected in other halo properties such
+as their clustering amplitude in what has been termed assembly bias
+(e.g. Gao, Springel \& White 2005, Li et al., 2008, Lacerna et al., 2011)
+where halos of different ages and equal mass show different clustering
+amplitudes, which could also be interpreted as a change in the effective
+halo mass according to halo properties.
+
+An older halo age has been shown to come along with more spherical halo
+shapes, higher concentrations and halo inner density.  However, in the
+assembly bias scenario of Gao et al., these halos tend to show a clustering
+amplitude consistent with that of the median halo population of higher masses.
+In terms of the alignments with the Tweb, our results show the oposite
+trend.  This shows that the physics behind the clustering amplitude and
+alignments do not necessarily coincide.  The full understanding of
+the dependence of halo properties and/or on their environment is 
+a complex problem, but these results provide extra information that complements
+that obtained from clustering measurements.
+
+%Prolateness follow concentration. In the Tweb
+%Angular momentum alignment is influenced by spin at higher masses. In
+%the Vweb angular momentum alginment is influenced by all factors. In
+%the peculiar velocity alginment only spin seemss to have an effect.
 
@@
 \caption{The alignment is always taken with respect to the third eigenvector.}
+\label{fig:drive}
 \end{figure*}
@@
 \label{sec:discussion}
-
-We do not find a strong signal for the alignment of spin and the
-cosmic web. A significant correlation signal has been recently
-measured between the spin and the cosmic vorticity
-\citep{Libeskind2013b,Laigle2013}. This two facts are consistent with
-spin being produced by the non-symmetric part of the shear and tidal
-tensors.
 
@@
 other than mass, in driving the alignments. We find that in the case of
-shape, halos located in high density regions or with a low value of
+shape, high concentration halos or halos with a low value of
 the reduced spin parameter tend to show a stronger signal. This trend is

### 2014-03-06 paper/main.tex
sergio

@@
 \end{document}
+
+Circularidad: C/A (en la figura 1 del paper de  Faltenbacher
+lo ponen como spherical o aspherical)
+
+Concentracion: sigma (v_dispersion)/ M^(1/3) H^(1/3) (ignore esta constante porque 
+solo estamos viendo el 30% superior he inferior
+
+Triaxialidad: (A^2 - B^2)/(A^2-C^2)
+
+Densidad: (este es propio)  masa virial dividido
+el volumen como una esfera de radio R_vir
+
+Spin: (no tengo la ecuacion aqui, pero es la del libro de
+Mo, Van de Bosh, White que va como proporcional a |J|/ M^{5/3}

### 2014-03-13 paper/main.tex
accepted all changes from Nelson + new references

--- 2014-03-06 paper/main.tex
@@
 simulation that allows to study dark matter halos spanning almost five orders
-of magnitude in mass ($10^{9}$-$10^{14}$) \hMsun {\bf and use} spatial scales
+of magnitude in mass ($10^{9}$-$10^{14}$) \hMsun and use spatial scales
 of $(0.5$-$1.0)$\hMpc to define the cosmic web. After varying the
@@
 increases; in the case of the velocity shear only massive halos
-$>10^{12}$\hMsun tend to have their shapes %be
- perpendicular to
+$>10^{12}$\hMsun tend to have their shapes perpendicular to
 filaments and walls. For the angular momentum we find alignment
@@
 the different signals between the two web description are due to the
-fact that %that 
-the main directions of stronger tidal tension and
+fact that the main directions of stronger tidal tension and
 velocity shear coincide for halos below $10^{12}$\hMpc but are
 perpendicular to each other for halos more massive than this
-threshold.  {\bf This clearly separates halos into those that live
-in sheets and filaments (lower masses) and nodes of the cosmic web.}
+threshold.  This clearly separates halos into those that live
+in sheets and filaments (lower masses) and nodes of the cosmic web.
 
@@
 There is a long observational tradition stuying galactic properties
-as a function of {\bf their} large scale environment. In these situations the environment
-definition is {\bf usually} based on quantities easily accesible to observations
-such as the number density. With the {\bg advent}%advenment 
+as a function of their large scale environment. In these situations the environment
+definition is usually based on quantities easily accesible to observations
+such as the number density. With the advent
 of large
@@
 scale structure growth models based on gravitational
-instability. %Using 
+instability. 
 Numerical simulations allow the time description
@@
 
-{\bf With the aid of} high resolution simulations it has been established that halos of
+With the aid of high resolution simulations it has been established that halos of
 a given mass form earlier in denser regions; concentration, spin and
@@
 
-There {\bf are} analytical frameworks, such as tidal torque theory, that
+There are analytical frameworks, such as tidal torque theory, that
 aim at describing how galaxies gain angular momentum and expect a
@@
 For each mass interval we perform cuts in the following properties:
-halo spin, concentration, halo triaxiallity defined as $(A^2-B^2)/(A^2-C^2)$ with
-high (low) triaxiality corresponding to prolate (oblate) shapes, circularity ($C/A$)  and halo
-inner density (virial mass divided by volume out to the virial radius). We
-measure the web alignments in two sets, each one including the $30\%$
-of halos in the lower/higher end of the corresponding property.
+halo spin, concentration, halo triaxiallity defined as $(a^2-b^2)/(a^2-c^2)$ with
+high (low) triaxiality corresponding to prolate (oblate) shapes,
+circularity ($c/a$)  and halo inner density (virial mass divided by
+volume out to the virial radius). We measure the web alignments in two
+sets, each one including the $30\%$ of halos in the lower/higher end
+of the corresponding property.
 
@@
 and bottom panels, respectively).  As here we show the average
-of the halo population above the lower mass limit imposed, the halo masses that dominate the
-statistics are close to this lower limit $~10^{11}\hMsun$.
-We show the result for the Twev and Vweb calculated using the two available
-resolutions, but as can be seen in general we find no significant differences in our results.
+of the halo population above the lower mass limit imposed, the halo
+masses that dominate the statistics are close to this lower limit $~10^{11}\hMsun$.
+We show the result for the Twev and Vweb calculated using the two
+available resolutions, but as can be seen in general we find no
+significant differences in our results.
 
@@
 as their clustering amplitude in what has been termed assembly bias
-(e.g. Gao, Springel \& White 2005, Li et al., 2008, Lacerna et al., 2011)
-where halos of different ages and equal mass show different clustering
-amplitudes, which could also be interpreted as a change in the effective
-halo mass according to halo properties.
+\citep[e.g.][]{Gao2005,Li2008,Lacerna2011} where halos of different
+ages and equal mass show different clustering amplitudes, which could
+also be interpreted as a change in the effective halo mass according
+to halo properties.
 
@@
 shapes, higher concentrations and halo inner density.  However, in the
-assembly bias scenario of Gao et al., these halos tend to show a clustering
+assembly bias scenario of \cite{Gao2005}, these halos tend to show a clustering
 amplitude consistent with that of the median halo population of higher masses.
@@
 
-%Prolateness follow concentration. In the Tweb
-%Angular momentum alignment is influenced by spin at higher masses. In
-%the Vweb angular momentum alginment is influenced by all factors. In
-%the peculiar velocity alginment only spin seemss to have an effect.
-
 \begin{figure*}
 \includegraphics[width=0.90\textwidth,angle=90]{Fig6.pdf}
-\caption{The alignment is always taken with respect to the third eigenvector.}
+\caption{Median of the $|\cos\theta|$ for the shape alignment of the
+  major axis with the third eigenvector. Each panel shows 
+  different subsamples according to selections on five different
+  properties: circularity, concentration, halo inner density, spin and
+  triaxiality. Each subsets includes $30\%$ of halos in the lower/higher end of each
+  property. The grey band indicates the region around
+  $|\cos\theta|=0.5$ that indicates the absence of alignment.}
 \label{fig:drive}
 \end{figure*}
-\section{Discussion}
-\label{sec:discussion}
 

### 2014-03-13 paper/main.tex
many new references

@@
 threshold.  This clearly separates halos into those that live
-in sheets and filaments (lower masses) and nodes of the cosmic web.
-
+in sheets and filaments (lower masses) and nodes of the cosmic web. As
+a general conclusion, our results clearly show that the two different
+algorithms we used to define the cosmic web describe different physical
+aspects of non-linear collapse and should be used in a complementary
+way according to the problem at hand.
 \end{abstract}
@@
 There is a long observational tradition stuying galactic properties
-as a function of their large scale environment. In these situations the environment
-definition is usually based on quantities easily accesible to observations
-such as the number density. With the advent
-of large
-surveys the visibility of the cosmic web is clear. As a consequence,
-in order to capture this filamentarity, the environment definition
-started to be more complex, involving shear properties of the galaxy
-density field or the reconstructuted dark matter density field.
-
-The emergence of this web like structure is a great success of large
-scale structure growth models based on gravitational
-instability. 
-Numerical simulations allow the time description
-of such structures together with the formation of the virialized dark
-matter halos, which in turn should host observable galaxies. The
-finding of gas filaments that feed galaxies is another theoretical
-hint that strenghtened the expected connection between galactic
-properties ant their place in the cosmic web.
+as a function of their large scale environment
+\citep[e.g.][]{Oemler1974,Dressler1980,Pimbblet2002,Gomez2003,Kauffmann2004,Abbas2006,Baldry2006,Park2007,OMill2008,Wilman2010}. In
+these situations the environment definition is usually based on
+quantities easily accesible to observations such as local number
+density or nearest neighbour measurements \citep{Muldrew2012}. With
+the advent of large surveys the visibility of the cosmic web is
+clear. As a consequence, in order to capture this filamentarity, the
+environment definition started to be more complex, involving shear
+properties of the galaxy density field or the reconstructuted dark
+matter density field \citep[e.g.]{Lee2005,Sousbie2008,MunozCuartas2011,Tempel2014}.
+
+In parallel, numerical simulations can reproduce the web-like
+structure of the galaxy distribution in models based on gravitational
+instability in a Dark Matter (DM) dominated universe
+\citep[e.g.][]{Bond1996,Colberg2005}. Simulations now allow to follow the time
+evolution into the non-linear regime of virialized structures which in
+turm should host observable galaxies. The discovery in simulations of
+gas filaments that feed galaxies is another theoretical hint that
+strenghtened the expected connection between galactic properties ant
+their place in the cosmic web \citep{Ocvirk2008,Dekel2009}.
 
@@
 or void depending on the simmetry properties of the local dark matter
-distribution.
+distribution
+\citep[e.g][]{Hahn2007,Sousbie2008b,Tweb,Gonzalez2010,Noh2011}.
 
@@
 studies that try to measure such correlations actually try to use as a
-proxy the observed shape of galaxies. In this respect it is useful to
+proxy the observed shape of galaxies
+\citep{Lee2002,Lee2007,Jones2010}. In this respect it is useful to
 have a theoretical baseline for the correlations of angular momentum
-and shape with the cosmic web.
+and shape with the cosmic web.  There is large tradition of alignment
+measurements of shape and angular momentum
+\citep[e.g.][]{Hahn2007,AragonCalvo2007,Zhang2009,Codis2012,Trowland2013,Libeskind2013}. The
+main result of these previous studies is that shape alignment is a
+robust measurement regardless of the methods and simulations. On the
+other hand, the results for the angular momentum differ in the degree of the alignment.
 
@@
 cosmic web, there has been an revival of surveys that measure the
-cosmic flow patterns in the Local Universe. Assuming the correspondence
-between the divergence of the cosmic flow velocity field and the local
-matter overdensity (valid in the linear regime) one could construct
-accurate maps of the matter density from peculiar velocities. From
-this perspective it is interesting to look at the expected alignment of
-the peculiar velocities.
-
-There is large tradition of alignment measurements of shape and
-angular momentum. The main result of these previous studies is that shape
-alignment is a robust measurement regardless of the methods and
-simulations. On the other hand, the results for the angular momentum
-differ in the degree of the alignment. In this \documentname we review
-most of these studyes and offer our own study with complementary
+cosmic flow patterns in the Local Universe
+\citep{Nusser2011,Tully2013}. Assuming the correspondence between the
+divergence of the cosmic flow velocity field and the local matter
+overdensity (valid in the linear regime) one could construct accurate
+maps of the matter density from peculiar velocities
+\citep{Courtois2012}. From this perspective it is interesting to look
+at the expected alignment of the peculiar velocities.
+
+In this \documentname we review most of these studies about shape and
+angular momentum alignment and offer our own study with complementary
 numerical techniques and simulations.  We also present for the first
@@
 of shape, spin and peculiar velocities with respect to the cosmic
-web. We continue with a discussion of these results in
-\S\ref{sec:discussion} paying special attention to resolution effects
-and the conditions that might drive the strong alignment signals
-observed in the precedent section. In \S\ref{sec:conclusions} we
-present our conclusions.
+web. In \S\ref{sec:conclusions} we present our conclusions.
 
@@
 
+In both algorithms we note the three eigenvalues as
+$\lambda_1>\lambda_2>\lambda_3$ and their correspoding eivenvectors as
+$\hat{e}_1$, $\hat{e}_2$ and $\hat{e}_3$.
+
 \subsection{Numerical considerations}
@@
 resolutions $256^3$ and $512^3$ that roughly correspond
-to scales of $1$ and $0.5$h$^{-1}$Mpc, respectively. For the T-Web we interpolate first
-the matter density field using a Cloud-In-Cell (CIC) scheme. Then we
-smooth using a Gaussian kernel with a spatial variance equal to the
-size of one grid cell. This smoothed matter density field is
+to scales of $1$ and $0.5$h$^{-1}$Mpc, respectively. For the T-Web we
+interpolate first the matter density field using a Cloud-In-Cell (CIC)
+scheme. Then we smooth using a Gaussian kernel with a spatial variance
+equal to the size of one grid cell. This smoothed matter density field is
 transformed into Fourier space to solve the Poisson equation and find
@@
 
+We caution the reader that the results reported by
+\citep{Vweb, Libeskind2013} use a velocity field that is calculated by a
+gaussian smoothing of the CIC velocity field without taking into
+account any weight by mass. We present a simple example to clarify the difference
+between the two ways of finding the smoothed velocity field. Let's consider two
+neighboring CIC cells, one with total mass $m_1 = 10^{11}$\hMsun and
+velocity along $x$ $v_{1x}=0$ km/s and a second cell with mass $m_2 = 10^{10}$
+and $v_{2x}=-10$ km/s. In the case of defining an average value for the
+velocity over these two cells our method finds a result $\bar{v}_x=
+(m_1v_{1x} + m_2v_{2x})/(m_1+m_2)= -0.09$km/s while the method used in
+\cite{Vweb,Libeskind2013} would find
+$\bar{v}_x=(v_{1x}+v_{2x})/2=-5$km/s.
+
 \section{Our Numerical Experiments}
@@
 for the parameter $\lambda_{\rm th}$; although, this has been done
-before we consider that  COMPLETAR...
+before we consider that deriving robust results independent of a the
+free paramenter $\lambda_{\rm th}$ can be more illuminating to
+understand the connection of halos with the cosmic web.
+
+However, for simplicity and readibility we report our results in terms
+of alignment with respect to filaments and sheets. Given that the
+direction along a filament should be defined by the eigenvector
+$\hat{e}_3$ corresponding to the smallest eigenvalue $\lambda_3$, a
+strong aligmnet along that vector will be reported as an aligment
+along filaments. Correspondingly,
 
@@
   the three properties studied in this paper: shape (major axis),
-  angular momentum and  peculiar velocity. Left column presents the
-  results against the Vweb   and the right the Tweb. Strong colors
-  refer to $256^3$ grid resolutions and lighter colors to a $512^3$
-  grid. The thick black horizontal line at $0.33$ corresponds to the
-  expected fraction for a random vector field.
+  angular momentum and  peculiar velocity. Left (right) column presents the
+  results against the Vweb (Tweb). Strong colors refer to $256^3$ grid
+  resolutions and lighter colors to a $512^3$ grid. The thick black
+  horizontal line at $0.33$ corresponds to the expected fraction for a
+  random vector field. 
 \label{fig:preferential}}
@@
   measured between the halo major axis and the first (third)
-  eigenvector.\label{fig:shape_alignment}.  SUGIERO PONER AMBAS LEYENDAS EN UN SOLO PANEL, SINO PARECE QUE
-IZQUIERDA Y DERECHA FUERAN PARA DOS RESOLUCIONES DISTINTAS.} 
+  eigenvector.\label{fig:shape_alignment}. }
 \end{figure*}
@@
 resolutions, with only minor changes for halos masses $>10^{13}$\hMsun.
-
-MOVI EL TITULO DE LA SUBSECCION AQUI, ESTABA DOS PARRAFOS MAS ABAJO, PERO TAMBIEN MODIFIQUE EL TEXTO INICIAL
-\subsection{Interweb Alignment}
-
-\begin{figure}
-\includegraphics[width=0.40\textwidth]{Fig5.pdf}
-\caption{Median of the interweb alignment for the two grid
-  resolutions as a function of the dark matter mass corresponding to
-  the halos where the measurement was made. The error bars indicate
-  the lower and upper quartiles (Figure in color in the web version).
-\label{fig:interweb}} 
-\end{figure}
-
-Perhaps the most striking result so far is that the two webs give
-different results for the alignment of massive halos. This is not
-completely unexpected given that the two algorithms are based on
-different physical premises to obtain the directions defining the
-eigenvectors. However, we investigate the origin of the different
-alignment statistics by studying the inter-web alignment.
-
-%We also wish to directly compare the results of the two
-%web tensor algorithms. 
-For the two algorithms, Tweb and Vweb, we have the information for their
-eigenvectors and eigenvalues on exactly the same positions defined
-by the grids. This allows us tocompute the pair-wise alignment
-between the eigenvectors in the two web finders.
-
-We are mainly interested in the alignment of the web near
-halos. Therefore we restrict our analysis to the grid cells that are
-occupied by halos. Otherwise, if we decided to perform this kind of analysis
-on all the grid cells, the statistics would be dominated by the void
-regions, because they dominate in number the fraction of cells in the
-simuation.
-
-Figure \ref{fig:interweb} shows the values for $\muavg$ between the
-two $\vec{e}_1$ eigenvectors in the Tweb and the Vweb.  The Figure
-shows that there is an alignment, $\muavg\approx 1.0$, for low mass
-halos and an antialignment, $\muavg\approx 0.2$ for massive ones.
-
-The transitional scale is located around $(10^{11.5}-10^{12.5})$\hMsun
-depending on the grid resolution. The coarse grid $(256^3)$ shows the
-transition at higher masses than the fine grid $(512^3)$.   We also
-note that the alignment is weaker in the finer grid, ($\muavg\approx
-0.7$) than in the coarser grid ($\muavg\approx1.0$).
-
-These two facts (alignment at low masses and low grid resolution)
-points towards an explanation in terms of the  linear / non-linear
-growth of structure. When the alignment is present on linear scales
-the divergence of the velocity field is proportional to the
-overdensity, i.e. the trace of the shear field is proportional to the
-trace of the tidal field.
-
-On the scale where the halos more massive than $10^{13}$\hMsun are
-located, the relationship between the velocity shear and the tidal
-field changes. There, the fastest momentum-weighted collapse direction
-(defined by the V-web) is perpendicular to the direction where the
-tidal compression is the highest.
 
@@
 
+\subsection{Interweb Alignment}
+
+\begin{figure}
+\includegraphics[width=0.40\textwidth]{Fig5.pdf}
+\caption{Median of the interweb alignment for the two grid
+  resolutions as a function of the dark matter mass corresponding to
+  the halos where the measurement was made. The error bars indicate
+  the lower and upper quartiles (Figure in color in the web version).
+\label{fig:interweb}} 
+\end{figure}
+
+Perhaps the most striking result so far is that the two webs give
+different results for the alignment of massive halos. This is not
+completely unexpected given that the two algorithms are based on
+different physical premises to obtain the directions defining the
+eigenvectors. However, we investigate the origin of the different
+alignment statistics by studying the inter-web alignment.
+
+For the two algorithms, Tweb and Vweb, we have the information for their
+eigenvectors and eigenvalues on exactly the same positions defined
+by the grids. This allows us tocompute the pair-wise alignment
+between the eigenvectors in the two web finders.
+
+We restrict our analysis to the grid cells that are occupied by
+halos. Otherwise, if we decided to perform this kind of analysis on
+all the grid cells, the statistics would be dominated by the void
+regions as they dominate in number the fraction of cells in the
+simuation.
+
+Figure \ref{fig:interweb} shows the values for $\muavg$ between the
+two $\vec{e}_1$ eigenvectors in the Tweb and the Vweb.  The Figure
+shows that there is an alignment, $\muavg\approx 1.0$, for low mass
+halos and an antialignment, $\muavg\approx 0.2$ for massive ones.
+
+The transitional scale is located around $(10^{11.5}-10^{12.5})$\hMsun
+depending on the grid resolution. The coarse grid $(256^3)$ shows the
+transition at higher masses than the fine grid $(512^3)$.   We also
+note that the alignment is weaker in the finer grid, ($\muavg\approx
+0.7$) than in the coarser grid ($\muavg\approx1.0$).
+
+These two facts (alignment at low masses and low grid resolution)
+points towards an explanation in terms of the  linear / non-linear
+growth of structure. When the alignment is present on linear scales
+the divergence of the velocity field is proportional to the
+overdensity, i.e. the trace of the shear field is proportional to the
+trace of the tidal field.
+
+On the scale where the halos more massive than $10^{13}$\hMsun are
+located, the relationship between the velocity shear and the tidal
+field changes. There, the fastest momentum-weighted collapse direction
+(defined by the V-web) is perpendicular to the direction where the
+tidal compression is the highest.
+
 \section{Conclusions}
@@
 are alignment with sheets. These results broadly agree with the
-published literature. Nevertheless, in the same publications there is an
-alignment/anti-alignment signal reported at lower halo masses
-$<10^{12}$\hMsun that we do not detect in our measurements.
+published literature. Nevertheless, in some publications
+\citep{AragonCalvo2007,Hahn2007} there is an alignment signal
+reported at lower halo masses $<10^{12}$\hMsun that we do not detect
+in our measurements.
 
@@
 the direction defined by the third eigenvector and perpendicular to
-the first. This signal is very strong in the Tweb for all masses below
+the first. This signal is clear in the Tweb for all masses below
 $<10^{13}$\hMsun. This can be interpreted as a flow parallel to walls
@@
 
+Our study has shown that the alignment properties of dark matter
+halos depend on the physical definition of the cosmic web. This shows
+that the main aspect of non-linear gravitational collapse might be
+revealead easily depending on the choice of the physical context
+(i.e. tidal field vs. velocity shear). There is not a better method,
+simply differente perspectives. We will explore the potential of these
+two different techniques in undertanding the environmental dependence
+of galaxy evolution in future work.
+
 \section*{Acknowledgments}
@@
 
-The tidal connection between voids in simulations \citep{Platen2008},
-the alignment of observed galaxies with the inferred tidal
-field\citep{Lee2007,Jones2010}. There are other kind of alignment
-statistics based on modifications of the correlation
+In this Appendix we review the results that use a similar exploration
+techniques for halo alignments with the cosmic web. Other kind of
+alignment statistics based based on modifications of the correlation
 \citep{Paz2008,Faltenbacher2009} that go beyond a local computation
-and therefore are not reviewed in detail in this paper.
+and therefore are not reviewed here.
 
@@
 \item
-\cite{Libeskind2013} %various alignments
+\cite{Libeskind2013}
 
@@
 \item 
-\citep{AragonCalvo2007} %angular momentum alignment
+\citep{AragonCalvo2007}
 
@@
 
-\citep{Hahn2007}% various alignments with the Tweb
+\citep{Hahn2007}
 

### 2014-03-13 paper/main.tex
minor changes

@@
 {\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1$ & 
-filament &none & $<10^{12}$\hMsun\\
-
-&   & & 
 filament & - & $>10^{12}$\hMsun\\
@@
 &   & & 
-wall & none & $<10^{12}$\hMsun\\
-
-&   & & 
-wall & none & $>10^{12}$\hMsun\\\hline
+filament & none & $<10^{12}$\hMsun\\
+
+&   & & 
+wall & none & $>10^{12}$\hMsun\\
+
+&   & & 
+wall & none & $<10^{12}$\hMsun\\\hline
 
 {\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1$ & 
-filament &none & $<10^{12}$\hMsun\\
-
-&   & & 
-filament & none & $>10^{12}$\hMsun\\
-
-&   & & 
-wall & none & $<10^{12}$\hMsun\\
-
-&   & & 
-wall & + & $>10^{12}$\hMsun\\\hline
+filament &none & $>10^{12}$\hMsun\\
+
+&   & & 
+filament & none & $<10^{12}$\hMsun\\
+
+&   & & 
+wall & + & $>10^{12}$\hMsun\\
+
+&   & & 
+wall & nonte & $<10^{12}$\hMsun\\\hline
 
@@
 & & &
-wall& $+$ & $<10^{12}$\hMsun\\
-& &    &
-wall & $++$ & $>10^{12}$\hMsun\\\hline \hline
+wall & $++$ & $>10^{12}$\hMsun\\
+& &    &
+wall& $+$ & $<10^{12}$\hMsun\\\hline \hline
 
 \end{tabular}
-\caption{Spin alignment with the cosmic web. Summary of theoretical
+\caption{Angular momentum alignment with the cosmic web. Summary of theoretical
   results provided by methods similar to ours.}
@@
 
-The spin is calculated as
+The angular momentum is calculated as
 \begin{equation}
@@
 
-The halo data used in this paper is publicly available through the
+The halo and environment used in this paper is publicly available through the
 MultiDark
-database\footnote{\texttt{http://www.multidark.org/MultiDark/}} and is
-thoroughly described in \cite{2013AN....334..691R}.
+database\footnote{\texttt{http://www.multidark.org/MultiDark/}}. The
+halo data is thoroughly described in \cite{2013AN....334..691R}.
 
@@
 
-CAMBIE EL ORDEN DE PARRAFOS PARA QUE LA FIGURA SE LEA DE IZQ A DERECHA:
-
 The shape alignment and the Vweb (upper row, left column) gives a

### 2014-03-13 paper/main.tex
almost there

@@
 
-We study the alignment of dark matter halos with the cosmic web as described by
-the tidal and velocity shear fields. We focus on the alignment of their
-shape, angular momentum and peculiar velocities. We use a cosmological N-body
-simulation that allows to study dark matter halos spanning almost five orders
-of magnitude in mass ($10^{9}$-$10^{14}$) \hMsun and use spatial scales
-of $(0.5$-$1.0)$\hMpc to define the cosmic web. After varying the
+We study the alignment of dark matter halos with the cosmic web
+charachterized by the tidal and velocity shear fields. We focus on the
+alignment of their shape, angular momentum and peculiar velocities. We
+use a cosmological N-body simulation that allows to study dark matter
+halos spanning almost five orders of magnitude in mass
+($10^{9}$-$10^{14}$) \hMsun and use spatial scales of
+$(0.5$-$1.0)$\hMpc to define the cosmic web. After varying the
 numerical parameters in our experiments we find that the halo shape
-and the tidal field web presents the strongest alignment along
-filaments and walls with a signal that gets stronger as the halo mass
-increases; in the case of the velocity shear only massive halos
-$>10^{12}$\hMsun tend to have their shapes perpendicular to
-filaments and walls. For the angular momentum we find alignment
-signals only for halos more massive than $10^{12}$\hMsun both in the
-tidal and velocity shear webs where the preferences are to be
-perpendicular to filaments or parallel to walls,
-respectively. Finally, the peculiar velocities show a strong alignment
-for all halo masses to move along filaments and walls in the tidal
-web, while in the velocity shear the same alignment is present but
-weaker and only for halos less massive than $10^{12}$\hMsun. Most of
-the different signals between the two web description are due to the
-fact that the main directions of stronger tidal tension and
-velocity shear coincide for halos below $10^{12}$\hMpc but are
+presents the strongesalignment along filaments and walls defined by
+the tidal field with a signal that gets stronger as the halo mass
+increases; in the case of the velocity shear field only massive halos
+$>10^{12}$\hMsun tend to have their shapes perpendicular to filaments
+and walls. For the angular momentum we find alignment signals only for
+halos more massive than $10^{12}$\hMsun both in the tidal and velocity
+shear webs where the preferences are to be perpendicular to filaments
+or parallel to walls, respectively. Finally, the peculiar velocities
+show a strong alignment for all halo masses to move along filaments
+and walls in the tidal web, while in the velocity shear the same
+alignment is present but weaker and only for halos less massive than
+$10^{12}$\hMsun. Most of the different signals between the two web
+description are due to the fact that the main directions of stronger
+tidal tension and velocity shear coincide for halos below $10^{12}$\hMpc but are
 perpendicular to each other for halos more massive than this
-threshold.  This clearly separates halos into those that live
-in sheets and filaments (lower masses) and nodes of the cosmic web. As
-a general conclusion, our results clearly show that the two different
+threshold.  ur results clearly show that the two different
 algorithms we used to define the cosmic web describe different physical
 aspects of non-linear collapse and should be used in a complementary
-way according to the problem at hand.
+way to understand the effect of the cosmic web on galaxy evolution.
 \end{abstract}
@@
 
-There is a long observational tradition stuying galactic properties
+There is a long observational tradition studying galactic properties
 as a function of their large scale environment
@@
 density or nearest neighbour measurements \citep{Muldrew2012}. With
-the advent of large surveys the visibility of the cosmic web is
-clear. As a consequence, in order to capture this filamentarity, the
-environment definition started to be more complex, involving shear
+the advent of large surveys the visibility of the cosmic web became
+clear. As a consequence, in order to capture its filamentarity, the
+environment def nition started to be more complex, involving shear
 properties of the galaxy density field or the reconstructuted dark
-matter density field \citep[e.g.]{Lee2005,Sousbie2008,MunozCuartas2011,Tempel2014}.
-
-In parallel, numerical simulations can reproduce the web-like
-structure of the galaxy distribution in models based on gravitational
-instability in a Dark Matter (DM) dominated universe
-\citep[e.g.][]{Bond1996,Colberg2005}. Simulations now allow to follow the time
-evolution into the non-linear regime of virialized structures which in
-turm should host observable galaxies. The discovery in simulations of
-gas filaments that feed galaxies is another theoretical hint that
-strenghtened the expected connection between galactic properties ant
-their place in the cosmic web \citep{Ocvirk2008,Dekel2009}.
-
-With the aid of high resolution simulations it has been established that halos of
-a given mass form earlier in denser regions; concentration, spin and
-shape also depend on the local density. In the last decade new
-algorithms have implemented cosmic web classifications that go beyond
-the local density by defining a location to be a peak, sheet, filament
-or void depending on the simmetry properties of the local dark matter
-distribution
-\citep[e.g][]{Hahn2007,Sousbie2008b,Tweb,Gonzalez2010,Noh2011}.
-
-There are analytical frameworks, such as tidal torque theory, that
-aim at describing how galaxies gain angular momentum and expect a
-correlation of this quantity with the cosmic web. The observational
-studies that try to measure such correlations actually try to use as a
-proxy the observed shape of galaxies
-\citep{Lee2002,Lee2007,Jones2010}. In this respect it is useful to
-have a theoretical baseline for the correlations of angular momentum
-and shape with the cosmic web.  There is large tradition of alignment
-measurements of shape and angular momentum
+matter density field
+\citep[e.g.]{Lee2005,Sousbie2008,MunozCuartas2011,Tempel2014}.
+
+In parallel to the observational advances, numerical simulations
+successfully reproduced the web-like structure of the galaxy
+distribution in models based on gravitational instability in a Dark
+Matter (DM) dominated universe
+\citep[e.g.][]{Bond1996,Colberg2005}. Simulations now allow to follow
+the time evolution into the deep non-linear regime of virialized
+structures (DM halos) which in turn should host observable
+galaxies to study their evolution in the cosmic web. The discovery in
+simulations of gas filaments that feed galaxies is another theoretical
+hint that strenghtened the expected connection between galactic
+properties ant their place in the web \citep{Ocvirk2008,Dekel2009}.
+
+In the last decade new algorithms have implemented cosmic web
+classifications that go beyond the local density by defining a
+location to be a peak, sheet, filament or void depending on the
+simmetry properties of the local dark matter distribution. With the
+aid of simulations it has been established that halos of a given mass
+form earlier in denser regions; concentration, angular momentum and shape also
+depend can be aligned with these web elements. \citep[e.g][]{Hahn2007,Sousbie2008b,Tweb,Gonzalez2010,Noh2011}.
+
+The observational studies that try to measure angular momentum correlations
+use the galaxy shape as a proxy  \citep{Lee2002,Lee2007,Jones2010}. In
+this respect it is useful to have a theoretical baseline for the
+correlations of angular momentum and shape with the cosmic web.  There
+is large tradition of alignment measurements of shape and angular momentum
 \citep[e.g.][]{Hahn2007,AragonCalvo2007,Zhang2009,Codis2012,Trowland2013,Libeskind2013}. The
@@
 robust measurement regardless of the methods and simulations. On the
-other hand, the results for the angular momentum differ in the degree of the alignment.
+other hand, the results for the angular momentum differ in the degree
+of the alignment.
 
@@
 cosmic flow patterns in the Local Universe
-\citep{Nusser2011,Tully2013}. Assuming the correspondence between the
+\citep{Nusser2011,Tully2013}. Assuming the linearity between the
 divergence of the cosmic flow velocity field and the local matter
@@
 numerical techniques and simulations.  We also present for the first
-time in the literature new results for the alignment of peculiar velocities
-with large scale structure.
+time in the literature new results for the alignment of peculiar
+velocities with large scale structure.
 
@@
 cosmological simulation and halo catalogs.  Next, we describe in
-\S\ref{sec:algorithms} the two web-finding algorithms we use. In
+\S\ref{sec:algorithms} the two web-finding algorithms we use and in
+\S\ref{sec:experiments} the setup for out numerical experiments. In
 \S\ref{sec:results} we present our main results about the alignment
-of shape, spin and peculiar velocities with respect to the cosmic
+of shape, angular momentum and peculiar velocities with respect to the cosmic
 web. In \S\ref{sec:conclusions} we present our conclusions.
@@
 
-There is abundant literature on the issue of shape and angular momentum
-alignment of dark matter halos with respect to the cosmic web. In this
-paper we focus our attention on results published during the last
+Out of the three alignments that we study in this paper -shape,
+angular momentum and peculiar velocity- only the the first two have
+received wide attention in the literature, being angular momentum the
+most popular with twice the number of studies for shape alignment.
+
+In this paper we focus our attention on results published during the last
 decade that have made use of large N-body dark matter only
@@
 
-Out of the three alignments that we study in this paper -shape,
-angular momentum and peculiar velocity- only the the first two have
-received wide attention in the literature, being angular momentum the
-most popular with twice the number of studies for shape alignment.
-
-These alignments are often measured from the distribution of the
+Alignments are often measured from the distribution of the
 $\mu=\vert\cos\theta\vert$ where $\theta$ is the angle between the two axes of
-interest. This is often directly measuered as the absolute value of
+interest. This is often directly measured as the absolute value of
 the dot product between the two unit vectors along the directions
-being tested, for instance in the case of angular momentum one would compute
-$\mu=\vert\hat{j}\cdot\hat{n}\vert$ In the case of shape alignments the major
+being tested. For instance, in the case of angular momentum one would compute
+$\mu=\vert\hat{j}\cdot\hat{n}\vert$. In the case of shape alignments the major
 axis is the chosen direction to compare against the cosmic web.
@@
 
-A novel aspect of our study is the use of a
-single computational volume of a high resolution simulation to study
-the alignments. Equally important, is our focus to quantify to what
-extent  these results depend on the method used to define the cosmic
-web and the numerical choices to implement the algorithms.
+A novel aspect of our study is the use of a single computational
+volume of a high resolution simulation to study the
+alignments. Equally important, is our focus to quantify to what extent
+these results depend on the method used to define the cosmic web and
+the numerical choices to implement the algorithms.
 
@@
 The halo and environment used in this paper is publicly available through the
-MultiDark
-database\footnote{\texttt{http://www.multidark.org/MultiDark/}}. The
+MultiDark database\footnote{\texttt{http://www.multidark.org/MultiDark/}}. The
 halo data is thoroughly described in \cite{2013AN....334..691R}.
@@
 
-In both algorithms we note the three eigenvalues as
-$\lambda_1>\lambda_2>\lambda_3$ and their correspoding eivenvectors as
-$\hat{e}_1$, $\hat{e}_2$ and $\hat{e}_3$.
-
 \subsection{Numerical considerations}
@@
 \section{Our Numerical Experiments}
+\label{sec:experiments}
 
@@
 strong aligmnet along that vector will be reported as an aligment
-along filaments. Correspondingly,
+along filaments. Correspondingly, the first eigenvector $\hat{e}_{1}$
+defines the direction perpendicular to walls, a strong alignemnt along
+this vector will be reported as an anti-alignment along walls.
 
@@
 \caption{Fraction of halos in a mass bin that show a preferential
-  alignment with respect to an eigenvector. Each row presents on of
-  the three properties studied in this paper: shape (major axis),
+  alignment with respect to an eigenvector in the cosmic
+  web; $\hat{e}_1$ (black) defines the direction perpendicular to a wall and
+  $\hat{e}_3$ (yellow) indicates the direction along a filament. Each row
+  presents one of the three properties studied in this paper: shape (major axis),
   angular momentum and  peculiar velocity. Left (right) column presents the
@@
   horizontal line at $0.33$ corresponds to the expected fraction for a
-  random vector field. 
+  random vector field. The uncertainty is computed assumed poissonian
+  statistics in each mass bin.
 \label{fig:preferential}}
@@
 \includegraphics[width=0.75\textwidth]{Fig2.pdf}
-\caption{Median of $\cos\theta$ quantifying the shape alignment for
+\caption{Median of $|\cos\theta|$ quantifying the shape alignment for
   the Vweb (left) and the Tweb (right) at two different grid
-  resolutions. In the upper (lower) panels the angle $\theta$ is
-  measured between the halo major axis and the first (third)
+  resolutions as a function of halo mass. In the upper (lower) panels
+  the angle $\theta$ is measured between the halo major axis and the first (third)
   eigenvector.\label{fig:shape_alignment}. }
@@
   alingment for the Vweb (left) and the Tweb (right) for two different
-  grid resolutions. In the upper (lower) panels the angle $\theta$ is
-  measured between the first (third) eivenvector and the angular
-  momentum vector.\label{fig:spin_alignment}} 
+  grid resolutions as a function of halo mass. In the upper (lower)
+  panels the angle $\theta$ is measured between the first (third)
+  eivenvector and the angular momentum
+  vector.\label{fig:spin_alignment}}  
 \end{figure*}
@@
   alignment with the Vweb (left) and the Tweb (right) for two different
-  grid resolutions. In the upper (lower) panels the angle $\theta$ is
-  measured between the first (third) eivenvector and a halo's peculiar
-  velocity.
+  grid resolutions as a function of halo mass. In the upper (lower)
+  panels the angle $\theta$ is measured between the first (third)
+  eivenvector and a halo's peculiar velocity.
 \label{fig:velocity_alignment}} 
@@
   the halos where the measurement was made. The error bars indicate
-  the lower and upper quartiles (Figure in color in the web version).
+  the lower and upper quartiles.
 \label{fig:interweb}} 
@@
 cosmological N-body simulation to study halo populations spanning five
-orders of magnitude in mass. The first algorithm uses the tidal field
-and the second the velocity shear, both present local results on
-scales of $0.5$\hMpc to $1.0$\hMpc.
+orders of magnitude in mass. The first algorithm uses the tidal field (Tweb)
+and the second the velocity shear (Vweb), both include results on spatial scales of
+$0.5$\hMpc and $1.0$\hMpc.
 
@@
 aligned with either one of the eigenvectors $\vec{e}_1$, $\vec{e}_2$
-or $\vec{e}_3$. The second method measures the average value of the
-angle between an eigenvector and the quantity of interest. These two
-measurements give us a complete picture for the different degrees of
-alignment in the cosmic web.
+or $\vec{e}_3$ en the local definition of the cosmic web. The second
+method measures the average value of the angle between an eigenvector
+and the quantity of interest. These two measurements give us a
+complete picture for the different degrees of alignment in the web.
 
@@
 respect to the Tweb. In this case the halos tend to align with the
-third eigenvector, $\vec{e}_3$, meaning that they lie along filaments
-and walls. This trend is gets stronger as the halo mass
+third eigenvector, $\hat{e}_3$, meaning that they lie along filaments
+and walls. This trend gets stronger as the halo mass
 increases and agrees with all the results published so far. Instead,
@@
 with respect to the filaments, while for the Vweb the massive halos
-are alignment with sheets. These results broadly agree with the
+are aligned with sheets. These results broadly agree with the
 published literature. Nevertheless, in some publications
@@
 velocities. Here we find a relatively strong signal of alignment along
-the direction defined by the third eigenvector and perpendicular to
-the first. This signal is clear in the Tweb for all masses below
+the direction defined by the third eigenvector, $\hat{e}_3$, and perpendicular to
+the first, $\hat{e}_1$. This signal is clear in the Tweb for all masses below
 $<10^{13}$\hMsun. This can be interpreted as a flow parallel to walls
@@
 The different behaviour for the alignments of massive halos in the
-Tweb and the Vweb was tracked to a corresponding anti-alignment
-between the eigenvectors in the two web grids for massive halos
+Tweb and the Vweb is explained by an anti-alignment between the
+eigenvectors in the two web grids for massive halos
 $>10^{12}$\hMsun. For low mass halos the directions defined by the two
@@
 (i.e. tidal field vs. velocity shear). There is not a better method,
-simply differente perspectives. We will explore the potential of these
-two different techniques in undertanding the environmental dependence
-of galaxy evolution in future work.
+but differente perspectives. In future work we will explore the
+potential of these two complementary techniques in understanding the
+environmental dependence of galaxy evolution.
 
 \section*{Acknowledgments}
+
+J.E.F-R acknowledges the financial support by Vicerrector\'ia de
+Investigaciones at Universidad de los Andes through a FAPA grant.
 
@@
 alignment statistics based based on modifications of the correlation
-\citep{Paz2008,Faltenbacher2009} that go beyond a local computation
-and therefore are not reviewed here.
+\citep[e.g.][]{Paz2008,Faltenbacher2009} that go beyond a local computation
+and are not reviewed here.
 

### 2014-03-24 paper/main.tex
submitted version :)

@@
   Jaime E. Forero-Romero$^{1}$,
-  Sergio Contreras$^{2}$,
-  Nelson Padilla$^{2}$ 
+  Sergio Contreras$^{2,3}$,
+  Nelson Padilla$^{2,3,4}$
 }
@@
 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
-$^{2}$Instituto de Astrofísica, Pontificia Universidad Católica,
-Av. Vicuña Mackenna 4860, Santiago, Chile\\
+$^{2}$Instituto de Astrofísica, Pontificia Universidad Cat\'olica,
+Av. Vicu\~na Mackenna 4860, Santiago, Chile\\
+$^{3}$Centro de Astro-Ingenier\'\i a, Pontificia Universidad Cat\'olica,
+Av. Vicu\~na Mackenna 4860, Santiago, Chile\\
+$^{4}$Max Planck Institut f\"ur Astrophysik, Postfach 1317, D-85741, Garching, Germany\\
 }
@@
 We study the alignment of dark matter halos with the cosmic web
-charachterized by the tidal and velocity shear fields. We focus on the
+characterized by the tidal and velocity shear fields. We focus on the
 alignment of their shape, angular momentum and peculiar velocities. We
@@
 numerical parameters in our experiments we find that the halo shape
-presents the strongesalignment along filaments and walls defined by
+presents the strongest alignment along filaments and walls defined by
 the tidal field with a signal that gets stronger as the halo mass
@@
 halos more massive than $10^{12}$\hMsun both in the tidal and velocity
-shear webs where the preferences are to be perpendicular to filaments
+shear webs where the preferences are for it to be perpendicular to filaments
 or parallel to walls, respectively. Finally, the peculiar velocities
@@
 $10^{12}$\hMsun. Most of the different signals between the two web
-description are due to the fact that the main directions of stronger
+descriptions are due to the fact that the main directions of stronger
 tidal tension and velocity shear coincide for halos below $10^{12}$\hMpc but are
 perpendicular to each other for halos more massive than this
-threshold.  ur results clearly show that the two different
+threshold.  Our results clearly show that the two different
 algorithms we used to define the cosmic web describe different physical
@@
 as a function of their large scale environment
-\citep[e.g.][]{Oemler1974,Dressler1980,Pimbblet2002,Gomez2003,Kauffmann2004,Abbas2006,Baldry2006,Park2007,OMill2008,Wilman2010}. In
+\citep[e.g.][]{Oemler1974,Dressler1980,Pimbblet2002,Gomez2003,Kauffmann2004,Abbas2006,Baldry2006,Park2007,OMill2008,Gonzales2009,Padilla2010,Wilman2010}. In
 these situations the environment definition is usually based on
-quantities easily accesible to observations such as local number
+quantities easily accessible to observations such as local number
 density or nearest neighbour measurements \citep{Muldrew2012}. With
@@
 environment def nition started to be more complex, involving shear
-properties of the galaxy density field or the reconstructuted dark
+properties of the galaxy density field or the reconstructed dark
 matter density field
@@
 simulations of gas filaments that feed galaxies is another theoretical
-hint that strenghtened the expected connection between galactic
-properties ant their place in the web \citep{Ocvirk2008,Dekel2009}.
+hint that strengthened the expected connection between galactic
+properties and their place in the web \citep{Ocvirk2008,Dekel2009}.
 
@@
 location to be a peak, sheet, filament or void depending on the
-simmetry properties of the local dark matter distribution. With the
+symmetry properties of the local dark matter distribution. With the
 aid of simulations it has been established that halos of a given mass
-form earlier in denser regions; concentration, angular momentum and shape also
-depend can be aligned with these web elements. \citep[e.g][]{Hahn2007,Sousbie2008b,Tweb,Gonzalez2010,Noh2011}.
+form earlier in denser regions; concentration, angular momentum and shape can also
+be aligned with these web elements. \citep[e.g][]{Hahn2007,Sousbie2008b,Tweb,Gonzalez2010,Noh2011}.
 
 The observational studies that try to measure angular momentum correlations
-use the galaxy shape as a proxy  \citep{Lee2002,Lee2007,Jones2010}. In
+use the galaxy shape as a proxy  \citep{Lee2002,Lee2007,Jones2010,Paz2008}. In
 this respect it is useful to have a theoretical baseline for the
@@
 is large tradition of alignment measurements of shape and angular momentum
-\citep[e.g.][]{Hahn2007,AragonCalvo2007,Zhang2009,Codis2012,Trowland2013,Libeskind2013}. The
+\citep[e.g.][]{Hahn2007,AragonCalvo2007,Zhang2009,Paz2010,Codis2012,Trowland2013,Libeskind2013}. The
 main result of these previous studies is that shape alignment is a
@@
 In the same spirit of describing the place of galaxies within the
-cosmic web, there has been an revival of surveys that measure the
+cosmic web, there has been a revival of surveys that measure the
 cosmic flow patterns in the Local Universe
@@
 
-In this \documentname we review most of these studies about shape and
+In this \documentname we review most of the studies about shape and
 angular momentum alignment and offer our own study with complementary
@@
 time in the literature new results for the alignment of peculiar
-velocities with large scale structure.
+velocities with the large scale structure.
 
@@
 
-\section{Theoretical Considerations: Notation and Precendents}
+\section{Theoretical Considerations: Notation and Precedents}
 \label{sec:theory}
@@
 Sloan Digital Sky Survey (SDSS), however we choose to narrow our
-discussion to simulation based studies which are prone to comparison.
+discussion to simulation based studies which are %prone to comparison.
+directly comparable to the one we present here.
 
@@
 
-For an isotropic ditribution of the vector around the direction defined by
+For an isotropic distribution of the vector around the direction defined by
 $\hat{n}$ the $\mu$ distribution, ranging between $0$ and $1$, should
-be flat and its mean value shoud be
+be flat and its mean value should be
 $\langle|mu|\rangle=0.5$. If a distribution is biased towards $1$
@@
 \cite{Trowland2013} presented a parameterization for the $\mu$
-distribution in the case of angular momentm alignment based on
+distribution in the case of angular momentum alignment based on
 theoretical considerations by \cite{Lee2005} (Eq. \ref{eq:distro} in
 the Appendix A). Under this parameterization a unique
-correspondece was found between the full shape of the $\vert\mu\vert$
+correspondence was found between the full shape of the $\vert\mu\vert$
 distribution and its average. In this paper we follow the lines of their work but
@@
 the reference, the second column summarizes the web finding method
-with a single name, the third scale associates a spatial scale to the
+with a single name, the third associates a spatial scale to the
 web finding methods, in most cases it corresponds to the grid size or
@@
 velocity field; The fourth column indicates along which web element
-(filament or wall) was measured the alignment; the fifth colume
-indicates the strenght of the alignment/anti-alignment, $++$/$--$
-indicate a strong alignement/anti-alignment while $+$/$-$ indicate a
-weaker signal; the last columns indicates whether the described signal
+(filament or wall) the alignment was measured; the fifth column
+indicates the strength of the alignment/anti-alignment, $++$/$--$
+indicate a strong alignment/anti-alignment while $+$/$-$ indicate a
+weaker signal; the last column indicates whether the described signal
 is present within a defined range of halo mass.
@@
 
-\section{N-body simulation and halo finding}
+\section{N-body simulation and halo catalogue}
 \label{sec:nbody}
@@
 
-In this paper we use groups found with a Friends-Of-Friends (FOF) halo
+In this paper we use groups identified with a Friends-Of-Friends (FOF) halo
 finder using a linking length of $b=0.17$ times the mean interparticle
@@
 following four web types: void, sheet, filament and peak depending
-on the number of eigenvalues larger than a given threshold
+on whether the number of eigenvalues larger than a given threshold
 $\lambda_{th}$ is $3$, $2$, $1$ or $0$, respectively.
@@
 where $\phi$ is the gravitational potential rescaled by a factor $4\pi
-G\bar{\rho}=3/2\Omega_m H_{0}^2$ in such a way that the Poission
+G\bar{\rho}=3/2\Omega_m H_{0}^2$ in such a way that the Poisson
 equation can be written as $\nabla^{2}\phi  = \delta$, where $\delta$
 is the matter overdensity, $\bar{\rho}$ is the average matter density,
-$H_{0}$ is the Hubble constant at present time and $\Omega_m$ is the
+$H_{0}$ is the Hubble constant at the present time and $\Omega_m$ is the
 matter density parameter. A detailed presentation of this algorithm
@@
 %
-where $v_{\alpha}$ correspond to the components of the peculiar
+where the $v_{\alpha}$ correspond to the components of the peculiar
 comoving velocities. With this definition the trace of the shear
@@
 neighboring CIC cells, one with total mass $m_1 = 10^{11}$\hMsun and
-velocity along $x$ $v_{1x}=0$ km/s and a second cell with mass $m_2 = 10^{10}$
-and $v_{2x}=-10$ km/s. In the case of defining an average value for the
+velocity along $x$ $v_{1x}=0$ km/s and a second cell with mass $m_2 = 10^{10}$\hMsun and $v_{2x}=-10$ km/s. In the case of defining an average value for the
 velocity over these two cells our method finds a result $\bar{v}_x=
@@
 filament or a wall. Our motivation is two-fold. First, partitioning the
-simulation into web elements implies a choice as to what value to use
-for the parameter $\lambda_{\rm th}$; although, this has been done
-before we consider that deriving robust results independent of a the
-free paramenter $\lambda_{\rm th}$ can be more illuminating to
+simulation into web elements implies a choice regarding the value
+for the parameter $\lambda_{\rm th}$; although this has been done
+before we consider that deriving robust results independent of the
+free parameter $\lambda_{\rm th}$ can be more illuminating to
 understand the connection of halos with the cosmic web.
 
-However, for simplicity and readibility we report our results in terms
+However, for simplicity and readability we report our results in terms
 of alignment with respect to filaments and sheets. Given that the
@@
 $\hat{e}_3$ corresponding to the smallest eigenvalue $\lambda_3$, a
-strong aligmnet along that vector will be reported as an aligment
+strong alignment along that vector will be reported as an alignment
 along filaments. Correspondingly, the first eigenvector $\hat{e}_{1}$
-defines the direction perpendicular to walls, a strong alignemnt along
+defines the direction perpendicular to walls, a strong alignment along
 this vector will be reported as an anti-alignment along walls.
@@
 The first measurement is a rough approximation to find out along which
-axes are halos aligned. We call this Preferential Alignment (PA).
+axes halos are aligned. We refer to this as Preferential Alignment (PA).
 
 We use the fact that for a given vector under study $\hat{a}$ and the
-tree eigenvectors the following identity holds
+three eigenvectors the following identity holds
 
@@
 independent of any threshold on the eigenvalues that could be used to make a web
-clasification into web types. Instead, we focus on the alignments with
+classification into web types. Instead, we focus on the alignments with
 respect to the eigenvectors regardless of the web type. In this
-context we recall that the eigenvector $\hat{e}_1$ is vector
+context we recall that the eigenvector $\hat{e}_1$ is 
 perpendicular to the plane defining a sheet and also a filament and
@@
 
-This experiment complements the results obtained by the PA satistic by
+This experiment complements the results obtained by the PA statistic by
 computing the average and standard deviation of
@@
 triaxiality. In this case we take the upper and lower $30\%$ of the
-halos according to each property and measure the strenght of the
+halos according to each property and measure the strength of the
 alignment by the average value of
@@
   presents one of the three properties studied in this paper: shape (major axis),
-  angular momentum and  peculiar velocity. Left (right) column presents the
+  angular momentum and  peculiar velocity. The left (right) column presents the
   results against the Vweb (Tweb). Strong colors refer to $256^3$ grid
@@
   horizontal line at $0.33$ corresponds to the expected fraction for a
-  random vector field. The uncertainty is computed assumed poissonian
+  random vector field. The uncertainty is computed assuming poissonian
   statistics in each mass bin.
@@
 preferential alignment along the third eigenvector $\vec{e}_{3}$. This
-signal incresases steadily with mass and is almost independent of the
+signal increases steadily with mass and is almost independent of the
 grid resolution. At high masses between $70\%$ and $100\%$ of the
@@
 
-The angular momentum in the Vweb (middle row, left column) presents a
+The angular momentum in the Vweb (middle row, left column) presents 
 a signal of alignment along the second eigenvector $\hat{e}_{2}$;
@@
 below that mass range there is no evidence for alignment while at
-higher masses all the trends we describe are aparent. This means that most
+higher masses all the trends we describe are apparent. This means that most
 of the halos tend to lie along walls but do not have a clear alignment
@@
 For the angular momentum alignment and the Tweb (middle row, right
-column) we find no evidence for any alighment at low masses $<10^{12}\hMsun$.
+column) we find no evidence for any alignment at low masses $<10^{12}\hMsun$.
 At higher masses $>10^{12}\hMsun$ there is a weak signal
@@
 In the next subsections we present a complementary account of these
-results by presenting quantitative results of the average angle
+results by showing quantitative results of the average angle
 between vector pairs describing the alignments discussed so far.
@@
   the Vweb (left) and the Tweb (right) at two different grid
-  resolutions as a function of halo mass. In the upper (lower) panels
+  resolutions as a function of halo mass.  The errorbars show the $20$ and $80$ percentiles 
+  of the distribution; the
+  errors on the median are too small to be noticed in this figure. In the upper (lower) panels
   the angle $\theta$ is measured between the halo major axis and the first (third)
-  eigenvector.\label{fig:shape_alignment}. }
+  eigenvector.\label{fig:shape_alignment} }
 \end{figure*}
@@
 angles between the first and third eigenvectors and the major shape
-axis as a function of halo mass.
+axis as a function of halo mass.  Notice that the errorbars shown correspond
+to the $20$ and $80$ percentiles; the actual error of the medians are
+always small, $\sim 1-5$ percent, and therefore are not shown.
 
@@
 an anti-alignment with $\muavg\approx0.3$. For low masses
-$<10^{12}\hMsun$ we do not detect any aligmnent signal. This is 
+$<10^{12}\hMsun$ we do not detect any alignment signal. This is
 consistent with the PA results of massive halos
@@
 case we measure an alignment along the third eigenvector and an
-antialignment along the first eigenvector. In the latter case at the
-highest mases $\muavg\approx 0.8$, while in the former $\muavg\approx
-0.2$. This strong alignment/antialignment signal mirrors the
+anti-alignment along the first eigenvector. In the latter case at the
+highest masses $\muavg\approx 0.8$, while in the former at $\muavg\approx
+0.2$. This strong alignment/anti-alignment signal mirrors the
 interpretation from the PA results that describe halos lying parallel
@@
 \caption{Median of $|\cos\theta|$ quantifying the angular momentum
-  alingment for the Vweb (left) and the Tweb (right) for two different
+  alignment for the Vweb (left) and the Tweb (right) for two different
   grid resolutions as a function of halo mass. In the upper (lower)
   panels the angle $\theta$ is measured between the first (third)
-  eivenvector and the angular momentum
+  eigenvector and the angular momentum
   vector.\label{fig:spin_alignment}} 
@@
   panels the angle $\theta$ is measured between the first (third)
-  eivenvector and a halo's peculiar velocity.
+  eigenvector and a halo's peculiar velocity.
 \label{fig:velocity_alignment}}
@@
 velocities alignments. In the case of the Vweb, the peculiar
-velocities show a weak signal of aligmnent ($\muavg\approx0.55$)
+velocities show a weak signal of alignment ($\muavg\approx0.55$)
 along the third eigenvector for low masses $<10^{12}$\Msun and a weak
-antialignment at higher masses. The strength of the alignment also shows
+anti-alignment at higher masses. The strength of the alignment also shows
 a clear dependency on the grid size used to compute the web.
 
-The Tweb shows a stronger alignment with the third eignenvecor at all
-masses with $\muavg\approx0.6$ and an antialignment with the first
+The Tweb shows a stronger alignment with the third eigenvector at all
+masses with $\muavg\approx0.6$ and an anti-alignment with the first
 eigenvector with $\muavg\approx 0.4$. In contrast to the Vweb results,
@@
 For each mass interval we perform cuts in the following properties:
-halo spin, concentration, halo triaxiallity defined as $(a^2-b^2)/(a^2-c^2)$ with
+halo spin, concentration, halo triaxiality defined as $(a^2-b^2)/(a^2-c^2)$ with
 high (low) triaxiality corresponding to prolate (oblate) shapes,
@@
 Figure \ref{fig:drive} shows the results for the major axes of
-the Vweb and Tweb (left and right panels) and the major axis,
+the Vweb and Tweb (left and right panels) and the shape major axis,
 the angular momentum vector, and the halo peculiar velocity (top, middle
@@
 masses that dominate the statistics are close to this lower limit $~10^{11}\hMsun$.
-We show the result for the Twev and Vweb calculated using the two
+We show the result for the Tweb and Vweb calculated using the two
 available resolutions, but as can be seen in general we find no
@@
 
-As can be seen, halos with higher circularity and inner density show
-a higher alignment with the Vweb major axes.  The oposite is the case
+Halos with higher circularity and inner density show
+a higher alignment with the Vweb major axes.  The opposite is the case
 of haloes with higher concentration, spin and triaxiality.  This trend
@@
 for the concentration and spin, with little differences evidenced by the
-other halo properties.  And the alignment strengthening is somewhat
+other halo properties.  The alignment strengthening is somewhat
 reversed when comparing the Vweb with the halo peculiar velocity,
@@
 as well as lower spins and triaxialities, produce a similar effect on the
-Tweb vs. major axis alignmets similar to that of diminishing the mass
+Tweb vs. major axis alignments to that of diminishing the mass
 of the halos.  This has also been detected in other halo properties such
@@
 amplitude consistent with that of the median halo population of higher masses.
-In terms of the alignments with the Tweb, our results show the oposite
+In terms of the alignments with the Tweb, our results show the opposite
 trend.  This shows that the physics behind the clustering amplitude and
@@
 eigenvectors and eigenvalues on exactly the same positions defined
-by the grids. This allows us tocompute the pair-wise alignment
+by the grids. This allows us to compute the pair-wise alignment
 between the eigenvectors in the two web finders.
@@
 halos. Otherwise, if we decided to perform this kind of analysis on
-all the grid cells, the statistics would be dominated by the void
+all the grid cells, the statistics would be more representative of the void
 regions as they dominate in number the fraction of cells in the
-simuation.
+simulation.
 
@@
 shows that there is an alignment, $\muavg\approx 1.0$, for low mass
-halos and an antialignment, $\muavg\approx 0.2$ for massive ones.
+halos and an anti-alignment, $\muavg\approx 0.2$ for massive ones.
 
@@
 orders of magnitude in mass. The first algorithm uses the tidal field (Tweb)
-and the second the velocity shear (Vweb), both include results on spatial scales of
+and the second the velocity shear (Vweb); both include results on spatial scales of
 $0.5$\hMpc and $1.0$\hMpc.
@@
 We quantify the alignments in two complementary ways. The first one
-measures the fraction of halos in a poulation that is preferentially
+measures the fraction of halos in a population that is preferentially
 aligned with either one of the eigenvectors $\vec{e}_1$, $\vec{e}_2$
-or $\vec{e}_3$ en the local definition of the cosmic web. The second
+or $\vec{e}_3$ in the local definition of the cosmic web. The second
 method measures the average value of the angle between an eigenvector
@@
 increases and agrees with all the results published so far. Instead,
-for the Vweb, there is only an antialignment for halos more massive
-than $10^{12}$\hMsun, a result that is presented here for the first
+for the Vweb, there is only an anti-alignment for halos more massive
+than $10^{12}\hMsun$, a result that is presented here for the first
 time.
@@
 A much weaker alignment signal is present for the angular momentum. In
-the Tweb only the most massive halos $>10^{12}$\hMsun are antialigned
+the Tweb only the most massive halos $>10^{12}$\hMsun are anti-aligned
 with respect to the filaments, while for the Vweb the massive halos
@@
 and filaments. In the case of the Vweb similar signal, albeit weaker,
-is present only for the low mass halos $<10^{12}$\hMsun.
+is present only for the low mass halos $<10^{12}\hMsun$.
+A similar result was obtained by \citep{Padilla2005} who found that
+peculiar velocities are larger in the direction parallel to void walls.
 
@@
 eigenvectors in the two web grids for massive halos
-$>10^{12}$\hMsun. For low mass halos the directions defined by the two
+$>10^{12}\hMsun$. For low mass halos the directions defined by the two
 webs point in the same direction. This trends can be interpreted as
@@
 more pronounced in the Tweb than in the Vweb. Concerning angular
-momentum we find that the antialignment signal is stronger for halos
+momentum we find that the anti-alignment signal is stronger for halos
 with high spin values. In the peculiar velocities we do not find any
-effect in the Tweb alignments, and the results for the Vweb show a
+effect in the Tweb alignments, and the results for the Vweb show 
 wide variations with grid resolution that impedes driving any strong
@@
 that the main aspect of non-linear gravitational collapse might be
-revealead easily depending on the choice of the physical context
+revealed easily depending on the choice of the physical context
 (i.e. tidal field vs. velocity shear). There is not a better method,
-but differente perspectives. In future work we will explore the
+but different perspectives. In future work we will explore the
 potential of these two complementary techniques in understanding the
@@
 Investigaciones at Universidad de los Andes through a FAPA grant.
+NP acknowledges support by Fondecyt Regular No. 1110328 and BASAL PFB-06 "Centro de Astronomia y Tecnologias Afines".
+NP and SC acknowledge support by the European Commissions Framework Programme 7, through the Marie Curie International
+Research Staff Exchange Scheme LACEGAL (PIRSES-GA-2010-269264).
+NP thanks the hospitality of the Max Planck
+Institute for Astrophysics at Garching during his sabbatical year 2013-2014.
+The Geryon cluster at the Centro de Astro-Ingenieria UC was extensively used for the calculations performed in this paper.
+The Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding for several improvements to the Geryon cluster.
 
@@
 
-The aligmnet signal for the angular momentum is weak while the shape
-alignmentsignal is very strong. The shape alignment is such that the
+The alignment signal for the angular momentum is weak while the shape
+alignment signal is very strong. The shape alignment is such that the
 eigenvector corresponding to the smallest eigenvalue is aligned with
@@
 they are able to quantify the degree of alignment ($c<0$) or
-antialignment ($c>0$).  This parameterization is based on theoretical
-expectactions of Tidal Torque Theory (TTT) \citep{Lee2005}. At $z=0$,
+anti-alignment ($c>0$).  This parameterization is based on theoretical
+expectations of Tidal Torque Theory (TTT) \citep{Lee2005}. At $z=0$,
 the reported value is $c = −0.035 \pm 0.004$, where the uncertainty
-was calculated using bootstraping and resampling.
+was calculated using bootstrapping and resampling.
 
@@
 agreement with the results from the Tidal web.  The transitional mass
-is weakly dependent on the smoothing scale, varing between $1-5\times
+is weakly dependent on the smoothing scale, varying between $1-5\times
 10^{12}$\hMsun for smoothing scales between $1.0-5.0$\hMpc.
@@
 
-For the method that uses the eigenvectors, they find that the strenght
+For the method that uses the eigenvectors, they find that the strength
 of the angular momentum alignment decreases with halo mass. For the
-shape they study the alingment of the major axis with the
+shape they study the alignment of the major axis with the
 filament. The find an alignment signal in all mass bins, with an
@@
 the wall, with a stronger alignment for massive halos. The effect for
-filaments is weaker, low mass halos tend to alignt along the filament,
+filaments is weaker, low mass halos tend to align along the filament,
 while high mass halos tend to be anti-aligned.
@@
 populations according to mass; low mass $5\times 10^{10} - 1.0\times 10^{12}$ and
-high mass $>10^{12}$. They find a weake anti-alignment for filaments
+high mass $>10^{12}$. They find a weak anti-alignment for filaments
 and a stronger anti-alignment in the case of the sheets. For the
@@
 along filaments is weak regardless of the mass. They do not report any
-other significan statistic, but recognize that they suffer from
+other significant statistic, but recognize that they suffer from
 small-number statistics in voids.

### 2014-03-24 paper/main.tex
typo

@@
 descriptions are due to the fact that the main directions of stronger
-tidal tension and velocity shear coincide for halos below $10^{12}$\hMpc but are
+tidal tension and velocity shear coincide for halos below $10^{12}$\hMsun but are
 perpendicular to each other for halos more massive than this

### 2014-05-02 paper/main.tex
submitted version
updates de sergio

@@
 \begin{keywords}
-methods: N-body simulations, galaxies: haloes, cosmology: theory, dark
+methods: numerical, galaxies: haloes, cosmology: theory, dark
 matter, large-scale structure of Universe
@@
 as a function of their large scale environment
-\citep[e.g.][]{Oemler1974,Dressler1980,Pimbblet2002,Gomez2003,Kauffmann2004,Abbas2006,Baldry2006,Park2007,OMill2008,Gonzales2009,Padilla2010,Wilman2010}. In
+\citep[e.g.][]{Oemler1974,Dressler1980,Pimbblet2002,Gomez2003,Kauffmann2004,Abbas2006,Baldry2006,Park2007,OMill2008,Gonzalez2009,Padilla2010,Wilman2010}. In
 these situations the environment definition is usually based on
@@
 clear. As a consequence, in order to capture its filamentarity, the
-environment def nition started to be more complex, involving shear
+environment definition started to be more complex, involving shear
 properties of the galaxy density field or the reconstructed dark
@@
 form earlier in denser regions; concentration, angular momentum and shape can also
-be aligned with these web elements. \citep[e.g][]{Hahn2007,Sousbie2008b,Tweb,Gonzalez2010,Noh2011}.
+be aligned with these web elements. \citep[e.g][]{AragonCalvo2007,Hahn2007,Tweb,Zhang2009,Gonzalez2010,Noh2011,Codis2012,Libeskind2013,Trowland2013}.
 
@@
 is large tradition of alignment measurements of shape and angular momentum
-\citep[e.g.][]{Hahn2007,AragonCalvo2007,Zhang2009,Paz2010,Codis2012,Trowland2013,Libeskind2013}. The
+\citep[e.g.][]{Hahn2007,AragonCalvo2007,Zhang2009,Paz2010,Codis2012,Trowland2013,Libeskind2013,AragonCalvo2014}. The
 main result of these previous studies is that shape alignment is a
@@
 We caution the reader that the results reported by
-\citep{Vweb, Libeskind2013} use a velocity field that is calculated by a
+\citep{Vweb, Libeskind2013,Wang2013} use a velocity field that is calculated by a
 gaussian smoothing of the CIC velocity field without taking into
-account any weight by mass. We present a simple example to clarify the difference
-between the two ways of finding the smoothed velocity field. Let's consider two
-neighboring CIC cells, one with total mass $m_1 = 10^{11}$\hMsun and
-velocity along $x$ $v_{1x}=0$ km/s and a second cell with mass $m_2 = 10^{10}$\hMsun and $v_{2x}=-10$ km/s. In the case of defining an average value for the
-velocity over these two cells our method finds a result $\bar{v}_x=
-(m_1v_{1x} + m_2v_{2x})/(m_1+m_2)= -0.09$km/s while the method used in
-\cite{Vweb,Libeskind2013} would find
-$\bar{v}_x=(v_{1x}+v_{2x})/2=-5$km/s.
+account any weight by mass. 
+% We present a simple example to clarify the difference
+% between the two ways of finding the smoothed velocity field. Let's consider two
+% neighboring CIC cells, one with total mass $m_1 = 10^{11}$\hMsun and
+% velocity along $x$ $v_{1x}=0$ km/s and a second cell with mass $m_2 = 10^{10}$\hMsun and $v_{2x}=-10$ km/s. In the case of defining an average value for the
+% velocity over these two cells our method finds a result $\bar{v}_x=
+% (m_1v_{1x} + m_2v_{2x})/(m_1+m_2)= -0.09$km/s while the method used in
+% \cite{Vweb,Libeskind2013} would find
+% $\bar{v}_x=(v_{1x}+v_{2x})/2=-5$km/s.
 
@@
 populations. On the contrary, if there is more than one third of the
-halo population in one of these sets, then we can talk about a
+halo population in one of these sets, then this will indicate a
 preferential alignment along one of the axes. However, this statistics
@@
 
-We now take a look at the angular momentum alignment. Figure
+We now focus our attention on the angular momentum alignment. Figure
 \ref{fig:spin_alignment} shows the results as a function of halo mass
@@
 
-Perhaps the most striking result so far is that the two webs give
+Perhaps the most striking result so far is that the two webs algorithms gives
 different results for the alignment of massive halos. This is not
@@
 published literature. Nevertheless, in some publications
-\citep{AragonCalvo2007,Hahn2007} there is an alignment signal
+\citep{AragonCalvo2007,Hahn2007,AragonCalvo2014} there is an alignment signal
 reported at lower halo masses $<10^{12}$\hMsun that we do not detect
@@
 
-The used the Multi-Scale Morphology Filter to describe th filamentary
+They used the Multi-Scale Morphology Filter to describe th filamentary
 structure. The method is based on the Hessian matrix of the density
@@
 
-The used the Tweb method applied on three simulations each of $512^3$
+They used the Tweb method\footnote{In \citep{Hahn2007} the authors do not use the term "Tweb", but their definition of the
+tidal field tensor they use is equivalent with the T-Web} applied on three simulations each of $512^3$
 particles, with sizes $L_1=45$\hMpc, $L_2=90$\hMpc and

### 2014-05-02 paper/main.tex
new changes

@@
 as a function of their large scale environment
-\citep[e.g.][]{Oemler1974,Dressler1980,Pimbblet2002,Gomez2003,Kauffmann2004,Abbas2006,Baldry2006,Park2007,OMill2008,Gonzalez2009,Padilla2010,Wilman2010}. In
+\citep[e.g.][]{Oemler1974,Dressler1980,Pimbblet2002,Gomez2003,Kauffmann2004,Abbas2006,Baldry2006,Park2007,OMill2008,Gonzalez2009,Padilla2010,Wilman2010,Muldrew2012}. In
 these situations the environment definition is usually based on
 quantities easily accessible to observations such as local number
-density or nearest neighbour measurements \citep{Muldrew2012}. With
+density or nearest neighbour measurements. With
 the advent of large surveys the visibility of the cosmic web became
 clear. As a consequence, in order to capture its filamentarity, the
-environment definition started to be more complex, involving shear
+environment definition started to be more complex, involving shear and gradient 
 properties of the galaxy density field or the reconstructed dark
-matter density field
-\citep[e.g.]{Lee2005,Sousbie2008,MunozCuartas2011,Tempel2014}.
+matter density/velocity field
+\citep[e.g.]{Lee2005,AragonCalvo2007,Hahn2007,Sousbie2008,Zhang2009,MunozCuartas2011,Vweb,Trowland2013,Tempel2014}.
 
@@
 {\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1 \hMpc$ &
-filament &$++$ & $>10^{12}$\hMsun\\
-&   & &
-filament & $+$ & $<10^{12}$\hMsun\\
-
-&   & &
-wall & $++$ & $>10^{12}$\hMsun\\
-
-&   & &
-wall & $+$ & $<10^{12}$\hMsun\\\hline
+$\hat{e}_3$ (filament) &$++$ & $>10^{12}$\hMsun\\
+&   & &
+$\hat{e}_3$ (filament) & $+$ & $<10^{12}$\hMsun\\
+
+&   & &
+$\hat{e}_1$ (wall) & $++$ & $>10^{12}$\hMsun\\
+
+&   & &
+$\hat{e}_1$ (wall) & $+$ & $<10^{12}$\hMsun\\\hline
 
 {\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ &
-filament &$--$ & $>10^{12}$\hMsun\\
-&   & &
-filament & none & $<10^{12}$\hMsun\\
-&   & &
-wall & $--$ & $>10^{12}$\hMsun\\
-
-&   & &
-wall & none & $<10^{12}$\hMsun\\\hline
+$\hat{e}_3$ (filament) &$--$ & $>10^{12}$\hMsun\\
+&   & &
+$\hat{e}_3$ (filament) & none & $<10^{12}$\hMsun\\
+&   & &
+$\hat{e}_1$ (wall) & $--$ & $>10^{12}$\hMsun\\
+
+&   & &
+$\hat{e}_1$ (wall) & none & $<10^{12}$\hMsun\\\hline
 
@@
 {\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1$ &
-filament & - & $>10^{12}$\hMsun\\
-
-&   & &
-filament & none & $<10^{12}$\hMsun\\
-
-&   & &
-wall & none & $>10^{12}$\hMsun\\
-
-&   & &
-wall & none & $<10^{12}$\hMsun\\\hline
+$\hat{e}_3$  (filament) & - & $>10^{12}$\hMsun\\
+
+&   & &
+$\hat{e}_3$  (filament) & none & $<10^{12}$\hMsun\\
+
+&   & &
+$\hat{e}_1$ (wall) & none & $>10^{12}$\hMsun\\
+
+&   & &
+$\hat{e}_1$ (wall) & none & $<10^{12}$\hMsun\\\hline
 
 {\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1$ &
-filament &none & $>10^{12}$\hMsun\\
-
-&   & &
-filament & none & $<10^{12}$\hMsun\\
-
-&   & &
-wall & + & $>10^{12}$\hMsun\\
-
-&   & &
-wall & nonte & $<10^{12}$\hMsun\\\hline
+$\hat{e}_3$  (filament) & none & $>10^{12}$\hMsun\\
+
+&   & &
+$\hat{e}_3$ (filament) & none & $<10^{12}$\hMsun\\
+
+&   & &
+$\hat{e}_1$ (wall) & + & $>10^{12}$\hMsun\\
+
+&   & &
+$\hat{e}_1$ (wall) & none & $<10^{12}$\hMsun\\\hline
 
@@
 cosmic web without defining first whether each point corresponds to a
-filament or a wall. Our motivation is two-fold. First, partitioning the
-simulation into web elements implies a choice regarding the value
-for the parameter $\lambda_{\rm th}$; although this has been done
-before we consider that deriving robust results independent of the
-free parameter $\lambda_{\rm th}$ can be more illuminating to
-understand the connection of halos with the cosmic web.
-
-However, for simplicity and readability we report our results in terms
-of alignment with respect to filaments and sheets. Given that the
-direction along a filament should be defined by the eigenvector
-$\hat{e}_3$ corresponding to the smallest eigenvalue $\lambda_3$, a
+filament or a wall. However, for simplicity and readability we describe
+our results in terms of alignment with respect to filaments and
+sheets. Given that the direction along a filament should be defined by the
+eigenvector $\hat{e}_3$ corresponding to the smallest eigenvalue $\lambda_3$, a
 strong alignment along that vector will be reported as an alignment
@@
 this vector will be reported as an anti-alignment along walls.
+
+We avoid the classification into filaments and walls for the following
+reason. Partitioning the simulation into web elements implies
+a choice regarding the value for the parameter $\lambda_{\rm th}$;
+although this has been done before, we consider that deriving robust
+results independent of the free parameter $\lambda_{\rm th}$ can be
+more illuminating to understand the connection of halos with the
+cosmic web.
+
+However, a possible disadvantage is that we are mixing the alignment signal
+of different environments. For instance, if half of halo population of
+fixed mass is aligned along filaments (and the vector $\hat{e}_3$), and the
+other half along planes (perpendicular to $\hat{e}_1$ but without a clear signal along
+$\hat{e}_3$, $\hat{e}_2$), the total signal of the alignment along
+$e_3$ might appear diluted in comparison to a signal taken separately
+for filaments and walls.
 
@@
 below that mass range there is no evidence for alignment while at
-higher masses all the trends we describe are apparent. This means that most
-of the halos tend to lie along walls but do not have a clear alignment
-with respect to filaments.
+higher masses all the trends we describe are noticeable. This means
+that the angular momentum of halos above $10^{12}\hMsun$ tends to lie
+along walls, parallel to the vector $\vec{e}_2$; without any clear
+trend for alignment/anti-alignment with respec to filaments.
 
@@
 
+It is possible to consider that numerical effects can also
+affect the estimation of the eigenvectors. For instance,
+different levels of shot noise in the interpolation scheme to
+construct the density and momentum grids could contribute to the
+anti-alignment of the two algorithms. However, a detailed study of the
+inter-web alignments is beyond the scope of this paper.
+
 \section{Conclusions}
@@
 NP acknowledges support by Fondecyt Regular No. 1110328 and BASAL PFB-06 "Centro de Astronomia y Tecnologias Afines".
-NP and SC acknowledge support by the European Commissions Framework Programme 7, through the Marie Curie International
-Research Staff Exchange Scheme LACEGAL (PIRSES-GA-2010-269264).
-NP thanks the hospitality of the Max Planck
-Institute for Astrophysics at Garching during his sabbatical year 2013-2014.
-The Geryon cluster at the Centro de Astro-Ingenieria UC was extensively used for the calculations performed in this paper.
-The Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding for several improvements to the Geryon cluster.
+NP and SC acknowledge support by the European Commissions Framework
+Programme 7, through the Marie Curie International Research Staff
+Exchange Scheme LACEGAL (PIRSES-GA-2010-269264). NP thanks the
+hospitality of the Max Planck Institute for Astrophysics at Garching
+during his sabbatical year 2013-2014. The Geryon cluster at the Centro de Astro-Ingenieria UC was extensively used for the calculations performed in this paper.
+The Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided
+funding for several i provements to the Geryon cluster.
+
+We thank the referee, Miguel Aragon-Calvo, for a constructive report
+that help us to improve the paper.
 
@@
 
-They used the Tweb method\footnote{In \citep{Hahn2007} the authors do not use the term "Tweb", but their definition of the
-tidal field tensor they use is equivalent with the T-Web} applied on three simulations each of $512^3$
+They used the hessian of the gravitational potential \footnote{In \citep{Hahn2007} the authors use a definition of the tidal field tensor equivalent with the T-Web method} applied on three simulations each of $512^3$
 particles, with sizes $L_1=45$\hMpc, $L_2=90$\hMpc and

### 2014-05-06 paper/main.tex
new text

@@
 numerical parameters in our experiments we find that the halo shape
-presents the strongest alignment along filaments and walls defined by
-the tidal field with a signal that gets stronger as the halo mass
-increases; in the case of the velocity shear field only massive halos
-$>10^{12}$\hMsun tend to have their shapes perpendicular to filaments
-and walls. For the angular momentum we find alignment signals only for
+presents the strongest alignment along the smallest tidal eigenvector
+,i.e. along filaments and walls, with a signal that gets stronger as
+the halo mass increases. In the case of the velocity shear field only
+massive halos $>10^{12}$\hMsun tend to have their shapes aligned along
+the largest tidal eigenvector; that is perpendicular to filaments and
+walls. For the angular momentum we find alignment signals only for
 halos more massive than $10^{12}$\hMsun both in the tidal and velocity
-shear webs where the preferences are for it to be perpendicular to filaments
-or parallel to walls, respectively. Finally, the peculiar velocities
-show a strong alignment for all halo masses to move along filaments
-and walls in the tidal web, while in the velocity shear the same
-alignment is present but weaker and only for halos less massive than
-$10^{12}$\hMsun. Most of the different signals between the two web
-descriptions are due to the fact that the main directions of stronger
-tidal tension and velocity shear coincide for halos below $10^{12}$\hMsun but are
-perpendicular to each other for halos more massive than this
-threshold.  Our results clearly show that the two different
-algorithms we used to define the cosmic web describe different physical
-aspects of non-linear collapse and should be used in a complementary
-way to understand the effect of the cosmic web on galaxy evolution.
+shear webs where the preferences are for it to be parallel to the
+middle eigenvector; perpendicular to filaments and parallel to
+walls. Finally, the peculiar velocities show a strong alignment along
+the smallest tidal eigenvector for all halo masses; moving along filaments
+and walls. In the velocity shear the same alignment is present but
+weaker and only for halos less massive than $10^{12}$\hMsun. Most of
+the different signals between the two web descriptions are due to the
+fact that the main directions of stronger tidal tension and velocity
+shear coincide for halos below $10^{12}$\hMsun but are perpendicular
+to each other for halos more massive than this threshold.  Our results
+clearly show that the two different algorithms we used to define the
+cosmic web describe different physical aspects of non-linear collapse
+and should be used in a complementary way to understand the effect of
+the cosmic web on galaxy evolution. 
 \end{abstract}
@@
 We caution the reader that the results reported by
-\citep{Vweb, Libeskind2013,Wang2013} use a velocity field that is calculated by a
-gaussian smoothing of the CIC velocity field without taking into
-account any weight by mass. 
+\citep{Vweb, Libeskind2013,Wang2013} use a velocity field that is
+calculated by a gaussian smoothing of the CIC velocity field without
+taking into account any weight by mass.
+
 % We present a simple example to clarify the difference
@@
 defines the direction perpendicular to walls, a strong alignment along
-this vector will be reported as an anti-alignment along walls.
+this vector will be reported as an anti-alignment along
+walls. Finally, a strong alignment along the second eigenvector
+$\hat{e}_2$ in company with an anti-alignment with $\hat{e}_1$ is
+reported as an alignment with walls and anti-alignment with respec to
+filaments.
 
@@
 reason. Partitioning the simulation into web elements implies
-a choice regarding the value for the parameter $\lambda_{\rm th}$;
-although this has been done before, we consider that deriving robust
-results independent of the free parameter $\lambda_{\rm th}$ can be
-more illuminating to understand the connection of halos with the
-cosmic web.
+a choice regarding the value for the parameter $\lambda_{\rm th}$ in
+two different web finders. This has been done before for each web
+finder independently. However, we consider that deriving results
+independent of the choice of parameters $\lambda_{\rm th,TWEB}$,
+$\lambda_{\rm th, VWEB}$ provides clear data to understand the
+connection of DM halos with the cosmic web.
 
 However, a possible disadvantage is that we are mixing the alignment signal
-of different environments. For instance, if half of halo population of
-fixed mass is aligned along filaments (and the vector $\hat{e}_3$), and the
-other half along planes (perpendicular to $\hat{e}_1$ but without a clear signal along
-$\hat{e}_3$, $\hat{e}_2$), the total signal of the alignment along
-$e_3$ might appear diluted in comparison to a signal taken separately
-for filaments and walls.
+of different environments. For instance, if half of the halo population of
+fixed mass is aligned along filaments (the vector $\hat{e}_3$), and the
+other half along planes (perpendicular to $\hat{e}_1$ but without a
+clear signal along $\hat{e}_3$, $\hat{e}_2$), the total signal of the
+alignment along $e_3$ might appear diluted in comparison to a signal
+taken separately for filaments and walls. However, as it has been
+shown in \cite{Libeskind2013} the alignment signals are robust across
+different environments.
 
@@
 
-We use the fact that for a given vector under study $\hat{a}$ and the
+We use the fact that for a given vector under study $\hat{s}$ and the
 three eigenvectors the following identity holds
@@
 
-We emphasize that all the quantities that we compute in this paper are
-independent of any threshold on the eigenvalues that could be used to make a web
-classification into web types. Instead, we focus on the alignments with
-respect to the eigenvectors regardless of the web type. In this
-context we recall that the eigenvector $\hat{e}_1$ is 
-perpendicular to the plane defining a sheet and also a filament and
-that $\hat{e}_3$ is the vector that marks the direction of a filament
-and lies on the plane of a sheet. Therefore we focus on quantifying
-the degree of alignment along these two eigenvectors.
+We emphasize that we focus on the alignments with respect to the
+eigenvectors regardless of the web type. We recall that the
+eigenvector $\hat{e}_1$ is perpendicular to the plane defining a sheet
+and the line describing a filament; and $\hat{e}_3$ is the vector that
+marks the direction of a filament and lies on the plane of a
+sheet. Therefore we focus on quantifying the degree of alignment along
+these two eigenvectors.
 
@@
 
-The peculiar velocities (lower panels) show a weak but consistent alignment along the
-third eigenvector $\vec{e}_{3}$ of the Tweb for all masses below
-$10^{13.0}\hMsun-10^{13.5}\hMsun$ depending on the grid
+The peculiar velocities (lower panels) show a weak but consistent
+alignment along the third eigenvector $\vec{e}_{3}$ of the Tweb for
+all masses below $10^{13.0}\hMsun-10^{13.5}\hMsun$ depending on the grid
 resolution. $45\%$ of the halos are aligned this way, while only $25\%$ are
@@
 at higher masses where the alignments get randomized.  In contrast,
-the peculiar velocities with respect to the Vweb show the same, although weaker, trend
-and only for low mass halos $<10^{12}$.
+the peculiar velocities with respect to the Vweb show the same,
+although weaker, trend and only for low mass halos $<10^{12}$.
 
@@
 orders of magnitude in mass. The first algorithm uses the tidal field (Tweb)
-and the second the velocity shear (Vweb); both include results on spatial scales of
-$0.5$\hMpc and $1.0$\hMpc.
+and the second the velocity shear (Vweb); both include results on
+spatial scales of $0.5$\hMpc and $1.0$\hMpc.
 
@@
 increases and agrees with all the results published so far. Instead,
-for the Vweb, there is only an anti-alignment for halos more massive
-than $10^{12}\hMsun$, a result that is presented here for the first
+for the momentum based Vweb, there is only an anti-alignment for halos
+more massive than $10^{12}\hMsun$, a result that is presented here for the first
 time.
@@
 A much weaker alignment signal is present for the angular momentum. In
-the Tweb only the most massive halos $>10^{12}$\hMsun are anti-aligned
-with respect to the filaments, while for the Vweb the massive halos
-are aligned with sheets. These results broadly agree with the
+the Tweb only the most massive halos $>10^{12}$\hMsun are
+perpendicular with respect to $\hat{e}_3$ (anti-aligned to filaments),
+while for the Vweb the massive halos are aligned with $\hat{e}_2$,
+lying along sheets. These results broadly agree with the
 published literature. Nevertheless, in some publications
@@
 reported at lower halo masses $<10^{12}$\hMsun that we do not detect
-in our measurements.
+in our measurements.  One possible explanation for this discrepancy
+can be appreciated by carefully looking at the results for different
+resolutions.  The $512^3$ grid does show a small anti-alignment for low
+mass haloes indicating that this signal could be related to scales
+smaller than $1$h$^{-1}$Mpc.  This would be consistent with
+\citep{Paz2008}, where using a different technique, they find an
+alignment for low mass haloes with the structure on small scales, and
+an anti-alighment at large scales (the 2-halo term). The diversity of
+results for the could be then interpreted as a high sensitivity of the
+alignment signal to the small scale cosmic web description, including
+numerical choices as to how interpolate the relevant fields.
 
@@
 velocities. Here we find a relatively strong signal of alignment along
-the direction defined by the third eigenvector, $\hat{e}_3$, and perpendicular to
-the first, $\hat{e}_1$. This signal is clear in the Tweb for all masses below
-$<10^{13}$\hMsun. This can be interpreted as a flow parallel to walls
-and filaments. In the case of the Vweb similar signal, albeit weaker,
-is present only for the low mass halos $<10^{12}\hMsun$.
-A similar result was obtained by \citep{Padilla2005} who found that
-peculiar velocities are larger in the direction parallel to void walls.
+the direction defined by the third eigenvector, $\hat{e}_3$, and
+perpendicular to the first, $\hat{e}_1$. This signal is clear in the
+Tweb for all masses below $<10^{13}$\hMsun. This can be interpreted as
+a flow parallel to walls and filaments. In the case of the Vweb
+similar signal, albeit weaker, is present only for the low mass halos
+$<10^{12}\hMsun$. A similar result was obtained by \citep{Padilla2005}
+who found that peculiar velocities are larger in the direction
+parallel to void walls.
 
@@
 non-linear effects that appear in the two different physical
-descriptions for the cosmic web.
+descriptions for the cosmic web, but the impact of the numerical
+choices to build the interpolation must be studied as well.
 

### 2014-05-07 paper/main.tex
new version + diff
including nelson's version

@@
 $\hat{e}_2$ in company with an anti-alignment with $\hat{e}_1$ is
-reported as an alignment with walls and anti-alignment with respec to
+reported as an alignment with walls and anti-alignment with respect to
 filaments.
@@
 
-However, a possible disadvantage is that we are mixing the alignment signal
+A possible disadvantage is that we are mixing the alignment signal
 of different environments. For instance, if half of the halo population of
@@
 smaller than $1$h$^{-1}$Mpc.  This would be consistent with
-\citep{Paz2008}, where using a different technique, they find an
+\citep{Paz2008} where, using a different technique, they find an
 alignment for low mass haloes with the structure on small scales, and
 an anti-alighment at large scales (the 2-halo term). The diversity of
-results for the could be then interpreted as a high sensitivity of the
+results could be then interpreted as a high sensitivity of the
 alignment signal to the small scale cosmic web description, including
-numerical choices as to how interpolate the relevant fields.
+numerical choices as to how the relevant fields are interpolated.
 
@@
 We thank the referee, Miguel Aragon-Calvo, for a constructive report
-that help us to improve the paper.
+that helped us to improve the paper.
 

### 2014-05-08 paper/main.tex
new comments from sergio

@@
 presents the strongest alignment along the smallest tidal eigenvector
-,i.e. along filaments and walls, with a signal that gets stronger as
+,e.g. along filaments and walls, with a signal that gets stronger as
 the halo mass increases. In the case of the velocity shear field only
@@
 clear. As a consequence, in order to capture its filamentarity, the
-environment definition started to be more complex, involving shear and gradient 
-properties of the galaxy density field or the reconstructed dark
+environment definition started to be more complex, involving shear and gradient properties of the galaxy density field or the reconstructed dark
 matter density/velocity field
-\citep[e.g.]{Lee2005,AragonCalvo2007,Hahn2007,Sousbie2008,Zhang2009,MunozCuartas2011,Vweb,Trowland2013,Tempel2014}.
+\citep[e.g.][]{Lee2005,AragonCalvo2007,Hahn2007,Sousbie2008,Zhang2009,Tweb,MunozCuartas2011,Vweb,Trowland2013,Tempel2014}.
 
@@
 aid of simulations it has been established that halos of a given mass
-form earlier in denser regions; concentration, angular momentum and shape can also
-be aligned with these web elements. \citep[e.g][]{AragonCalvo2007,Hahn2007,Tweb,Zhang2009,Gonzalez2010,Noh2011,Codis2012,Libeskind2013,Trowland2013}.
+form earlier in denser regions; concentration, angular momentum and
+shape can also be aligned with these web
+elements. \citep[e.g][]{AragonCalvo2007,Hahn2007,,Zhang2009,Gonzalez2010,Noh2011,Codis2012,Libeskind2013,Trowland2013}.
 
@@
 Sloan Digital Sky Survey (SDSS), however we choose to narrow our
-discussion to simulation based studies which are %prone to comparison.
+discussion to simulation based studies which are
 directly comparable to the one we present here.
@@
 \end{tabular}\\
-\caption{Shape alignment with the cosmic web. Summary of theoretical
+\caption{Shape alignment with the cosmic web, 
+$\hat{e}_1$ ($\hat{e}_3$)
+is the major (minor) eigenvector of
+the corresponding shear. 
+Summary of theoretical
   results provided by methods similar to ours.}
@@
 \end{tabular}
-\caption{Angular momentum alignment with the cosmic web. Summary of theoretical
+\caption{Angular momentum alignment with the cosmic web, 
+$\hat{e}_1$ ($\hat{e}_3$)
+is the major (minor) eigenvector of
+the corresponding shear. 
+Summary of theoretical
   results provided by methods similar to ours.}
@@
 \item Halos with $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_2)^2$
-  and $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_3)$, which can
+  and $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_3^2)$, which can
   be considered to aligned mostly along $\hat{e}_1$.
@@
 on the grid resolution. Secondly, the alignment at higher masses goes
-along the first eigenvector $\vec{e}_{1}$ meaning that they mostly lie
+along the first eigenvector $\hat{e}_{1}$ meaning that they mostly lie
 perpendicular to the filaments and sheets. In the discussion section
@@
 For shape alignment and the Tweb (upper row, right column) we find a strong
-preferential alignment along the third eigenvector $\vec{e}_{3}$. This
+preferential alignment along the third eigenvector $\hat{e}_{3}$. This
 signal increases steadily with mass and is almost independent of the
 grid resolution. At high masses between $70\%$ and $100\%$ of the
-halos have their major axis aligned along $\vec{e}_{3}$ which means
+halos have their major axis aligned along $\hat{e}_{3}$ which means
 that they mostly lie along filaments and sheets.
@@
 direction, while there is a minority of halos aligned with
-$\vec{e}_{1}$.  There is a clear change in trends around
+$\hat{e}_{1}$.  There is a clear change in trends around
 $10^{11}\hMsun-10^{12}\hMsun$ depending on the grid resolution;
@@
 that the angular momentum of halos above $10^{12}\hMsun$ tends to lie
-along walls, parallel to the vector $\vec{e}_2$; without any clear
+along walls, parallel to the vector $\hat{e}_2$; without any clear
 trend for alignment/anti-alignment with respec to filaments.
@@
 between $35\%$ to $45\%$ of the halos are aligned with respect to
-$\vec{e}_1$ and $\vec{e}_2$. Correspondingly, between $10\%$ to $20\%$
-of the halos are aligned along $\vec{e}_{3}$. This means
+$\hat{e}_1$ and $\hat{e}_2$. Correspondingly, between $10\%$ to $20\%$
+of the halos are aligned along $\hat{e}_{3}$. This means
 that most of the halos are perpendicular to the filaments and do not
@@
 The peculiar velocities (lower panels) show a weak but consistent
-alignment along the third eigenvector $\vec{e}_{3}$ of the Tweb for
+alignment along the third eigenvector $\hat{e}_{3}$ of the Tweb for
 all masses below $10^{13.0}\hMsun-10^{13.5}\hMsun$ depending on the grid
 resolution. $45\%$ of the halos are aligned this way, while only $25\%$ are
-aligned along the first eigenvector $\vec{e}_1$. This suggests that
+aligned along the first eigenvector $\hat{e}_1$. This suggests that
 halos tend to move along filaments and parallel to the walls, except
@@
 as their clustering amplitude in what has been termed assembly bias
-\citep[e.g.][]{Gao2005,Li2008,Lacerna2011} where halos of different
+\citep[][e.g.]{Gao2005,Li2008,Lacerna2011} where halos of different
 ages and equal mass show different clustering amplitudes, which could
@@
 Figure \ref{fig:interweb} shows the values for $\muavg$ between the
-two $\vec{e}_1$ eigenvectors in the Tweb and the Vweb.  The Figure
+two $\hat{e}_1$ eigenvectors in the Tweb and the Vweb.  The Figure
 shows that there is an alignment, $\muavg\approx 1.0$, for low mass
@@
 measures the fraction of halos in a population that is preferentially
-aligned with either one of the eigenvectors $\vec{e}_1$, $\vec{e}_2$
-or $\vec{e}_3$ in the local definition of the cosmic web. The second
+aligned with either one of the eigenvectors $\hat{e}_1$, $\hat{e}_2$
+or $\hat{e}_3$ in the local definition of the cosmic web. The second
 method measures the average value of the angle between an eigenvector
@@
 revealed easily depending on the choice of the physical context
-(i.e. tidal field vs. velocity shear). There is not a better method,
+(e.g. tidal field vs. velocity shear). There is not a better method,
 but different perspectives. In future work we will explore the
@@
 
-We thank the referee, Miguel Aragon-Calvo, for a constructive report
+We thank the referee, Miguel Arag\'on-Calvo, for a constructive report
 that helped us to improve the paper.
@@
 They measure the alignment with each one of the eigenvectors. With
-repecto to the minor eigenvector $\vec{e}_{3}$  (the filament direction) there is anti-alignement for masses $M>5\times10^{12}$\Msun and alignment for masses
-$<5\times 10^{12}$\Msun; with respect to the intermediate eigenvector $\vec{e}_2$
+repecto to the minor eigenvector $\hat{e}_{3}$  (the filament direction) there is anti-alignement for masses $M>5\times10^{12}$\Msun and alignment for masses
+$<5\times 10^{12}$\Msun; with respect to the intermediate eigenvector $\hat{e}_2$
 there is a strong alignment at high masses and no alignment for low
-masses; with respect to the major eigenvector $\vec{e}_{1}$
+masses; with respect to the major eigenvector $\hat{e}_{1}$
 (normal to the wall plane) there is an anti-alignment signal at all

### 2014-05-08 paper/main.tex
new references

@@
 matter density/velocity field
-\citep[e.g.][]{Lee2005,AragonCalvo2007,Hahn2007,Sousbie2008,Zhang2009,Tweb,MunozCuartas2011,Vweb,Trowland2013,Tempel2014}.
+\citep[e.g.][]{Lee2005,AragonCalvo2007,Hahn2007,Sousbie2008,Zhang2009,Tweb,MunozCuartas2011,Vweb,Trowland2013,Tempel2014},
+including recent developments that take into account the rotational
+part of the velocity field \citep[e.g.][]{Wang2013,LibeskindVorticity}.
 
@@
 We caution the reader that the results reported by
-\citep{Vweb, Libeskind2013,Wang2013} use a velocity field that is
+\citep{Vweb, Libeskind2013} use a velocity field that is
 calculated by a gaussian smoothing of the CIC velocity field without
@@
 for the momentum based Vweb, there is only an anti-alignment for halos
-more massive than $10^{12}\hMsun$, a result that is presented here for the first
-time.
+more massive than $10^{12}\hMsun$, a result that is presented here for
+the first time.
 
@@
 reported at lower halo masses $<10^{12}$\hMsun that we do not detect
-in our measurements.  One possible explanation for this discrepancy
+in our measurements. Actually \cite{AragonCalvo2014} confirms the mass
+$10^{12}$\hMsun as a transitional scale between alignment
+/anti-alignment in filaments, showing that it reflects the degree of
+evolution of the host filament.
+
+One possible explanation for this discrepancy
 can be appreciated by carefully looking at the results for different

### 2014-05-08 paper/main.tex
new changes

@@
 reported at lower halo masses $<10^{12}$\hMsun that we do not detect
-in our measurements. Actually \cite{AragonCalvo2014} confirms the mass
-$10^{12}$\hMsun as a transitional scale between alignment
-/anti-alignment in filaments, showing that it reflects the degree of
-evolution of the host filament.
-
-One possible explanation for this discrepancy
-can be appreciated by carefully looking at the results for different
-resolutions.  The $512^3$ grid does show a small anti-alignment for low
-mass haloes indicating that this signal could be related to scales
-smaller than $1$h$^{-1}$Mpc.  This would be consistent with
+in our measurements. Actually \cite{AragonCalvo2014}, using a
+multiscale web-finding method, confirmed the mass $10^{12}$\hMsun as a
+transitional scale between alignment /anti-alignment in filaments,
+showing that it reflects the degree of evolution of the host
+filament.
+
+There are two possible explanations for the discrepancy. The first is
+that in this low mass range the signal for the different
+environments (mostly filaments and sheets) is mixed, diluting the
+strength of the alignment. Another possible explanation can be
+appreciated by carefully looking at the results for different
+resolutions.  The $512^3$ grid does show a small anti-alignment for
+low  mass haloes indicating that this signal could be related to scales
+smaller than $1\hMpc$.  This would be consistent with
 \citep{Paz2008} where, using a different technique, they find an
@@
 The Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided
-funding for several i provements to the Geryon cluster.
+funding for several improvements to the Geryon cluster.
 

### 2014-05-08 paper/main.tex
minor typos fixed

@@
 shape can also be aligned with these web
-elements. \citep[e.g][]{AragonCalvo2007,Hahn2007,,Zhang2009,Gonzalez2010,Noh2011,Codis2012,Libeskind2013,Trowland2013}.
+elements. \citep[e.g][]{AragonCalvo2007,Hahn2007,Zhang2009,Gonzalez2010,Noh2011,Codis2012,Libeskind2013,Trowland2013}.
 
@@
 is the major (minor) eigenvector of
-the corresponding shear. 
+the corresponding tensor. 
 Summary of theoretical
@@
 \item Halos with $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_2)^2$
-  and $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_3^2)$, which can
+  and $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_3)^2$, which can
   be considered to aligned mostly along $\hat{e}_1$.

### 2014-05-09 paper/main.tex
latest version

@@
 numerical parameters in our experiments we find that the halo shape
-presents the strongest alignment along the smallest tidal eigenvector
-,e.g. along filaments and walls, with a signal that gets stronger as
+presents the strongest alignment along the smallest tidal eigenvector,
+e.g. along filaments and walls, with a signal that gets stronger as
 the halo mass increases. In the case of the velocity shear field only 
@@
 walls. Finally, the peculiar velocities show a strong alignment along
-the smallest tidal eigenvector for all halo masses; moving along filaments
+the smallest tidal eigenvector for all halo masses; halos move along filaments
 and walls. In the velocity shear the same alignment is present but
-weaker and only for halos less massive than $10^{12}$\hMsun. Most of
+weaker and only for halos less massive than $10^{12}\hMsun$. Most of
 the different signals between the two web descriptions are due to the
@@
   and sheets, more so for massive haloes.
-\item Halo spin tends to be oriented perpendicular to filaments and
-parallel to sheets, but it is a weaker than shape alignment.
+\item Halo angular momentum tends to be oriented perpendicular to filaments and
+parallel to sheets, but it is weaker than shape alignment.
 \end{itemize}
@@
 three real eigenvalues $\lambda_1>\lambda_2>\lambda_3$ and their
-corresponding eigenvectors ${\bf e}_{1}$, ${\bf e}_2$ and ${\bf
- e}_3$. This allows for a local classification into one of the
+corresponding eigenvectors $\hat{e}_{1}$, $\hat{e}_2$ and
+$\hat{e}_3$. This allows for a local classification into one of the 
 following four web types: void, sheet, filament and peak depending
@@
 resolutions $256^3$ and $512^3$ that roughly correspond
-to scales of $1$ and $0.5$h$^{-1}$Mpc, respectively. For the T-Web we
+to scales of $1$ and $0.5\hMpc$, respectively. For the T-Web we
 interpolate first the matter density field using a Cloud-In-Cell (CIC)
@@
 taking into account any weight by mass.
-
-% We present a simple example to clarify the difference
-% between the two ways of finding the smoothed velocity field. Let's consider two
-% neighboring CIC cells, one with total mass $m_1 = 10^{11}$\hMsun and
-% velocity along $x$ $v_{1x}=0$ km/s and a second cell with mass $m_2 = 10^{10}$\hMsun and $v_{2x}=-10$ km/s. In the case of defining an average value for the
-% velocity over these two cells our method finds a result $\bar{v}_x=
-% (m_1v_{1x} + m_2v_{2x})/(m_1+m_2)= -0.09$km/s while the method used in
-% \cite{Vweb,Libeskind2013} would find
-% $\bar{v}_x=(v_{1x}+v_{2x})/2=-5$km/s.
 
@@
   angular momentum and  peculiar velocity. The left (right) column presents the
-  results against the Vweb (Tweb). Strong colors refer to $256^3$ grid
+  results against the V-web (T-web). Strong colors refer to $256^3$ grid
   resolutions and lighter colors to a $512^3$ grid. The thick black
@@
 
-The shape alignment and the Vweb (upper row, left column) gives a
+The shape alignment and the V-web (upper row, left column) give a
 different perspective. Firstly, there seems to be little evidence
@@
 
-For shape alignment and the Tweb (upper row, right column) we find a strong
+For shape alignment and the T-web (upper row, right column) we find a strong
 preferential alignment along the third eigenvector $\hat{e}_{3}$. This
@@
 
-The angular momentum in the Vweb (middle row, left column) presents 
+The angular momentum in the V-web (middle row, left column) presents 
 a signal of alignment along the second eigenvector $\hat{e}_{2}$;
@@
 
-For the angular momentum alignment and the Tweb (middle row, right
+For the angular momentum alignment and the T-web (middle row, right
 column) we find no evidence for any alignment at low masses $<10^{12}\hMsun$.
@@
 The peculiar velocities (lower panels) show a weak but consistent
-alignment along the third eigenvector $\hat{e}_{3}$ of the Tweb for
+alignment along the third eigenvector $\hat{e}_{3}$ of the T-web for
 all masses below $10^{13.0}\hMsun-10^{13.5}\hMsun$ depending on the grid
@@
 at higher masses where the alignments get randomized.  In contrast,
-the peculiar velocities with respect to the Vweb show the same,
+the peculiar velocities with respect to the V-web show the same,
 although weaker, trend and only for low mass halos $<10^{12}$.
@@
 \caption{Median of $|\cos\theta|$ quantifying the shape alignment for
-  the Vweb (left) and the Tweb (right) at two different grid
+  the V-web (left) and the T-web (right) at two different grid
   resolutions as a function of halo mass.  The errorbars show the $20$ and $80$ percentiles 
@@
 
-In the case of the Vweb (left column) we have a clear alignment with
+In the case of the V-web (left column) we have a clear alignment with
 respect to the first eigenvector at high masses $>10^{12}\hMsun$, with
@@
 
-The Tweb (right column) shows alignment trends starting at masses of
+The T-web (right column) shows alignment trends starting at masses of
 $10^{10}$\hMsun, two orders of magnitude below than the V-web. In this
@@
 \caption{Median of $|\cos\theta|$ quantifying the angular momentum
-  alignment for the Vweb (left) and the Tweb (right) for two different
+  alignment for the V-web (left) and the T-web (right) for two different
   grid resolutions as a function of halo mass. In the upper (lower)
@@
 \ref{fig:shape_alignment}. In all cases we see that these alignment
-trends are weaker than the shape alignments. For the Vweb low mass halos
+trends are weaker than the shape alignments. For the V-web low mass halos
 $<10^{12}$\hMsun do not show any preferential alignment with the
@@
 
-In the case of the Tweb, the alignment for low mass halos $<10^{12}$\hMsun
+In the case of the T-web, the alignment for low mass halos $<10^{12}$\hMsun
 is also absent. More massive halos present a weak alignment along
@@
 \caption{Median of $\vert\cos\theta\vert$ quantifying the peculiar velocity
-  alignment with the Vweb (left) and the Tweb (right) for two different
+  alignment with the V-web (left) and the T-web (right) for two different
   grid resolutions as a function of halo mass. In the upper (lower)
@@
 Figure \ref{fig:velocity_alignment} shows the results for peculiar
-velocities alignments. In the case of the Vweb, the peculiar
+velocities alignments. In the case of the V-web, the peculiar
 velocities show a weak signal of alignment ($\muavg\approx0.55$)
@@
 
-The Tweb shows a stronger alignment with the third eigenvector at all
+The T-web shows a stronger alignment with the third eigenvector at all
 masses with $\muavg\approx0.6$ and an anti-alignment with the first
-eigenvector with $\muavg\approx 0.4$. In contrast to the Vweb results,
+eigenvector with $\muavg\approx 0.4$. In contrast to the V-web results,
 these trends remain basically unchanged at all masses and grid
@@
 Figure \ref{fig:drive} shows the results for the major axes of
-the Vweb and Tweb (left and right panels) and the shape major axis,
+the V-web and T-web (left and right panels) and the shape major axis,
 the angular momentum vector, and the halo peculiar velocity (top, middle
@@
 masses that dominate the statistics are close to this lower limit $~10^{11}\hMsun$.
-We show the result for the Tweb and Vweb calculated using the two
+We show the result for the T-web and V-web calculated using the two
 available resolutions, but as can be seen in general we find no
@@
 Halos with higher circularity and inner density show
-a higher alignment with the Vweb major axes.  The opposite is the case
+a higher alignment with the V-web major axes.  The opposite is the case
 of haloes with higher concentration, spin and triaxiality.  This trend
-is also visible in the angular momentum vs. Vweb major axis alignment only
+is also visible in the angular momentum vs. V-web major axis alignment only
 for the concentration and spin, with little differences evidenced by the
 other halo properties.  The alignment strengthening is somewhat
-reversed when comparing the Vweb with the halo peculiar velocity,
+reversed when comparing the V-web with the halo peculiar velocity,
 with some evidence for a strengthening with lower circularity and
@@
 
-On the right panels the trends can also be readily seen.  The Tweb
+On the right panels the trends can also be readily seen.  The T-web
 vs. major axis alignments are stronger for higher circularity,
@@
 spins, and is only strengthened when the triaxiality is higher.
-Not much difference is seen in the Tweb vs. halo peculiar velocity
+Not much difference is seen in the T-web vs. halo peculiar velocity
 alignments, being this the only regime where there is a clear difference
-in influence of halo properties on the alignments with the Tweb and Vweb;
+in influence of halo properties on the alignments with the T-web and V-web;
 the latter do show important changes on the lower-left panel.
@@
 as well as lower spins and triaxialities, produce a similar effect on the
-Tweb vs. major axis alignments to that of diminishing the mass
+T-web vs. major axis alignments to that of diminishing the mass
 of the halos.  This has also been detected in other halo properties such
@@
 amplitude consistent with that of the median halo population of higher masses.
-In terms of the alignments with the Tweb, our results show the opposite
+In terms of the alignments with the T-web, our results show the opposite
 trend.  This shows that the physics behind the clustering amplitude and
@@
 
-For the two algorithms, Tweb and Vweb, we have the information for their
+For the two algorithms, T-web and V-web, we have the information for their
 eigenvectors and eigenvalues on exactly the same positions defined
@@
 Figure \ref{fig:interweb} shows the values for $\muavg$ between the
-two $\hat{e}_1$ eigenvectors in the Tweb and the Vweb.  The Figure
+two $\hat{e}_1$ eigenvectors in the T-web and the V-web.  The Figure
 shows that there is an alignment, $\muavg\approx 1.0$, for low mass
@@
 cosmological N-body simulation to study halo populations spanning five
-orders of magnitude in mass. The first algorithm uses the tidal field (Tweb)
-and the second the velocity shear (Vweb); both include results on
+orders of magnitude in mass. The first algorithm uses the tidal field (T-web)
+and the second the velocity shear (V-web); both include results on
 spatial scales of $0.5$\hMpc and $1.0$\hMpc.
@@
 method measures the average value of the angle between an eigenvector
-and the quantity of interest. These two measurements give us a
+and the vector of interest. These two measurements give us a
 complete picture for the different degrees of alignment in the web.
@@
 We find that the strongest alignment occurs for the halo shape with
-respect to the Tweb. In this case the halos tend to align with the
+respect to the T-web. In this case the halos tend to align with the
 third eigenvector, $\hat{e}_3$, meaning that they lie along filaments
@@
 increases and agrees with all the results published so far. Instead,
-for the momentum based Vweb, there is only an anti-alignment for halos
+for the momentum based V-web, there is only an anti-alignment for halos
 more massive than $10^{12}\hMsun$, a result that is presented here for
@@
 A much weaker alignment signal is present for the angular momentum. In
-the Tweb only the most massive halos $>10^{12}$\hMsun are
+the T-web only the most massive halos $>10^{12}$\hMsun are
 perpendicular with respect to $\hat{e}_3$ (anti-aligned to filaments),
-while for the Vweb the massive halos are aligned with $\hat{e}_2$,
+while for the V-web the massive halos are aligned with $\hat{e}_2$,
 lying along sheets. These results broadly agree with the
@@
 perpendicular to the first, $\hat{e}_1$. This signal is clear in the
-Tweb for all masses below $<10^{13}$\hMsun. This can be interpreted as
-a flow parallel to walls and filaments. In the case of the Vweb
+T-web for all masses below $<10^{13}$\hMsun. This can be interpreted as
+a flow parallel to walls and filaments. In the case of the V-web
 similar signal, albeit weaker, is present only for the low mass halos
@@
 The different behaviour for the alignments of massive halos in the
-Tweb and the Vweb is explained by an anti-alignment between the
+T-web and the V-web is explained by an anti-alignment between the
 eigenvectors in the two web grids for massive halos
@@
 the reduced spin parameter tend to show a stronger signal. This trend is
-more pronounced in the Tweb than in the Vweb. Concerning angular
+more pronounced in the T-web than in the V-web. Concerning angular
 momentum we find that the anti-alignment signal is stronger for halos
 with high spin values. In the peculiar velocities we do not find any
-effect in the Tweb alignments, and the results for the Vweb show 
+effect in the T-web alignments, and the results for the V-web show 
 wide variations with grid resolution that impedes driving any strong

### 2014-05-11 paper/main.tex
agradecimientos updated

@@
 NP acknowledges support by Fondecyt Regular No. 1110328 and BASAL PFB-06 "Centro de Astronomia y Tecnologias Afines".
-NP and SC acknowledge support by the European Commissions Framework
+S.C. acknowledges support from a PhD Fellowship from CONICYT
+N.P. and S.C. acknowledge support by the European Commissions Framework
 Programme 7, through the Marie Curie International Research Staff
-Exchange Scheme LACEGAL (PIRSES-GA-2010-269264). NP thanks the
+Exchange Scheme LACEGAL (PIRSES-GA-2010-269264). N.P. thanks the
 hospitality of the Max Planck Institute for Astrophysics at Garching

### 2014-05-13 paper/main.tex
updates from Nelson

@@
 
-Perhaps the most striking result so far is that the two webs algorithms gives
+Perhaps the most striking result so far is that the two web algorithms give
 different results for the alignment of massive halos. This is not
@@
 smaller than $1\hMpc$.  This would be consistent with
-\citep{Paz2008} where, using a different technique, they find an
+\cite{Paz2008} where, using a different technique, they find an
 alignment for low mass haloes with the structure on small scales, and

### 2014-05-13 paper/main.tex
reduced abstract length

@@
 \begin{abstract}
-
 We study the alignment of dark matter halos with the cosmic web
@@
 halos spanning almost five orders of magnitude in mass
-($10^{9}$-$10^{14}$) \hMsun and use spatial scales of
-$(0.5$-$1.0)$\hMpc to define the cosmic web. After varying the
-numerical parameters in our experiments we find that the halo shape
+($10^{9}$-$10^{14}$) \hMsun and spatial scales of
+$(0.5$-$1.0)$\hMpc to define the cosmic web. We find that the halo shape
 presents the strongest alignment along the smallest tidal eigenvector,
@@
 massive halos $>10^{12}$\hMsun tend to have their shapes aligned along
-the largest tidal eigenvector; that is perpendicular to filaments and
+the largest tidal eigenvector; that is, perpendicular to filaments and
 walls. For the angular momentum we find alignment signals only for
@@
 and walls. In the velocity shear the same alignment is present but
-weaker and only for halos less massive than $10^{12}\hMsun$. Most of
-the different signals between the two web descriptions are due to the
-fact that the main directions of stronger tidal tension and velocity
-shear coincide for halos below $10^{12}$\hMsun but are perpendicular
-to each other for halos more massive than this threshold.  Our results
-clearly show that the two different algorithms we used to define the
-cosmic web describe different physical aspects of non-linear collapse
-and should be used in a complementary way to understand the effect of
-the cosmic web on galaxy evolution. 
+weaker and only for halos less massive than $10^{12}\hMsun$. Our
+results clearly show that the two different algorithms we used to
+define the cosmic web describe different physical aspects of
+non-linear collapse and should be used in a complementary way to
+understand the effect of the cosmic web on galaxy evolution.    
 \end{abstract}

### 2014-06-02 paper/main.tex
minor changes

@@
 
+We thank Kristin Riebe for her work to make the cosmic-web data available in the Multidark database.
+
 We thank the referee, Miguel Arag\'on-Calvo, for a constructive report
@@
 
-They studies the alignment of the angular momentum dark relative to
+They study the alignment of the angular momentum dark relative to
 the surrounding large scale structure and to the tidal tensor

### 2014-06-02 paper/main.tex
astro-ph version

@@
 density or nearest neighbour measurements. With
-the advent of large surveys the visibility of the cosmic web became
+the advent of large galaxy surveys and cosmological N-body simulations
+the visibility of the cosmic web and its physical origin became
 clear. As a consequence, in order to capture its filamentarity, the
-environment definition started to be more complex, involving shear and gradient properties of the galaxy density field or the reconstructed dark
+environment definition started to be more complex, involving shear and gradient properties of the galaxy density field or the reconstructed/simulated dark
 matter density/velocity field
@@
 Author & Web Method & Spatial Scale & Along &
-Alignment & Mass dependence\\\hline
-
-{\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1 \hMpc$ &
+Alignment & Mass dependence\\
+ & & ($\hMpc$)& & & \\\hline
+
+{\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1$ &
 $\hat{e}_3$ (filament) &$++$ & $>10^{12}$\hMsun\\
@@
 
-{\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ &
+{\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1$ &
 $\hat{e}_3$ (filament) &$--$ & $>10^{12}$\hMsun\\
@@
 
-\cite{Libeskind2013} & V-Web & $1 \hMpc$ &
+\cite{Libeskind2013} & V-Web & $1$ &
 filament &$++$ & $>10^{12}$\hMsun\\
@@
 
-\cite{Zhang2009}  & Hessian density field &  $2.1$\hMpc &
+\cite{Zhang2009}  & Hessian density field &  $2.1$ &
 filament & $++$ & $>10^{12}\hMsun$\\
@@
 {\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1$ &
-$\hat{e}_3$  (filament) & - & $>10^{12}$\hMsun\\
+$\hat{e}_3$  (filament) & $-$ & $>10^{12}$\hMsun\\
 
@@
 
-We thank Kristin Riebe for her work to make the cosmic-web data available in the Multidark database.
+We thank Kristin Riebe for her work to make the cosmic web data available in the Multidark database.
 

### 2014-06-04 paper/main.tex
new reference to basilakos

@@
 as a function of their large scale environment
-\citep[e.g.][]{Oemler1974,Dressler1980,Pimbblet2002,Gomez2003,Kauffmann2004,Abbas2006,Baldry2006,Park2007,OMill2008,Gonzalez2009,Padilla2010,Wilman2010,Muldrew2012}. In
-these situations the environment definition is usually based on
+\citep[e.g.][]{Oemler1974,Dressler1980,Pimbblet2002,Gomez2003,Kauffmann2004,Abbas2006,Baldry2006,Park2007,OMill2008,Gonzalez2009,Padilla2010,Wilman2010,Muldrew2012}.
+In these situations the environment definition is usually based on
 quantities easily accessible to observations such as local number
@@
 matter density/velocity field
-\citep[e.g.][]{Lee2005,AragonCalvo2007,Hahn2007,Sousbie2008,Zhang2009,Tweb,MunozCuartas2011,Vweb,Trowland2013,Tempel2014},
+\citep[e.g.][]{Lee2005,Basilakos2006,AragonCalvo2007,Hahn2007,Sousbie2008,Zhang2009,Tweb,MunozCuartas2011,Vweb,Trowland2013,Tempel2014},
 including recent developments that take into account the rotational
@@
 techniques for halo alignments with the cosmic web. Other kind of
-alignment statistics based based on modifications of the correlation
-\citep[e.g.][]{Paz2008,Faltenbacher2009} that go beyond a local computation
-and are not reviewed here.
+alignment statistics based based on shape measurements
+\citep{Basilakos2006} or modifications of the correlation
+\citep[e.g.][]{Paz2008,Faltenbacher2009} that go beyond a local
+computation and are not reviewed here.
 
@@
 Skeleton to be the set of critical lines joining the maxima of the
-density field through saddle points following the gradient. They also
+density field through saddle points following the gradient \citep{Sousbie2008b}. They also
 compute the hessian of the potential over the smoothed density field
@@
 
-They used the Multi-Scale Morphology Filter to describe th filamentary
+They used the Multi-Scale Morphology Filter \citep{AragonCalvo2007} to describe th filamentary
 structure. The method is based on the Hessian matrix of the density

### 2014-06-09 paper/main.tex
latest versio for the journal

@@
 ($10^{9}$-$10^{14}$) \hMsun and spatial scales of
-$(0.5$-$1.0)$\hMpc to define the cosmic web. We find that the halo shape
-presents the strongest alignment along the smallest tidal eigenvector,
+$(0.5$-$1.0)$\hMpc to define the cosmic web. The strongest alignment
+is measured for halo shape along the smallest tidal eigenvector,
 e.g. along filaments and walls, with a signal that gets stronger as
@@
 halos more massive than $10^{12}$\hMsun both in the tidal and velocity
-shear webs where the preferences are for it to be parallel to the
+shear fields where the preferences are for it to be parallel to the
 middle eigenvector; perpendicular to filaments and parallel to
@@
 the smallest tidal eigenvector for all halo masses; halos move along filaments
-and walls. In the velocity shear the same alignment is present but
-weaker and only for halos less massive than $10^{12}\hMsun$. Our
-results clearly show that the two different algorithms we used to
+and walls. The same alignment is present with the velocity shear,
+albeit weaker and only for halos less massive than $10^{12}\hMsun$. Our
+results show that the two different algorithms we used to
 define the cosmic web describe different physical aspects of
 non-linear collapse and should be used in a complementary way to
-understand the effect of the cosmic web on galaxy evolution.    
+understand the cosmic web influence on galaxy evolution.    
 \end{abstract}
@@
 $\hat{e}_3$ (filament) &$++$ & $>10^{12}$\hMsun\\
-&   & &
+{\bf (This Work)}&   & &
 $\hat{e}_3$ (filament) & $+$ & $<10^{12}$\hMsun\\
@@
 $\hat{e}_3$ (filament) &$--$ & $>10^{12}$\hMsun\\
-&   & &
+{\bf (This Work)}&   & &
 $\hat{e}_3$ (filament) & none & $<10^{12}$\hMsun\\
@@
 
-&   & &
+{\bf (This Work)}&   & &
 $\hat{e}_3$  (filament) & none & $<10^{12}$\hMsun\\
@@
 
-&   & &
+{\bf (This Work)}&   & &
 $\hat{e}_3$ (filament) & none & $<10^{12}$\hMsun\\

### 2014-06-09 paper/main.tex
less than 250 words in the abstract

@@
 halos more massive than $10^{12}$\hMsun both in the tidal and velocity
-shear fields where the preferences are for it to be parallel to the
+shear fields where the preferences is to be parallel to the
 middle eigenvector; perpendicular to filaments and parallel to

### 2014-06-09 paper/main.tex
one word less

@@
 albeit weaker and only for halos less massive than $10^{12}\hMsun$. Our
-results show that the two different algorithms we used to
+results show that the two different algorithms used to
 define the cosmic web describe different physical aspects of

### 2014-07-02 paper/main.tex
final version after proof-reading

@@
   the shape, angular momentum and peculiar velocities of dark matter
-  halos}  
+  haloes}  
 \author[J.E. Forero-Romero et al.]{
@@
 \begin{abstract}
-We study the alignment of dark matter halos with the cosmic web
+We study the alignment of dark matter haloes with the cosmic web
 characterized by the tidal and velocity shear fields. We focus on the
@@
 use a cosmological N-body simulation that allows to study dark matter
-halos spanning almost five orders of magnitude in mass
+haloes spanning almost five orders of magnitude in mass
 ($10^{9}$-$10^{14}$) \hMsun and spatial scales of
@@
 the halo mass increases. In the case of the velocity shear field only
-massive halos $>10^{12}$\hMsun tend to have their shapes aligned along
+massive haloes $>10^{12}$\hMsun tend to have their shapes aligned along
 the largest tidal eigenvector; that is, perpendicular to filaments and
 walls. For the angular momentum we find alignment signals only for
-halos more massive than $10^{12}$\hMsun both in the tidal and velocity
+haloes more massive than $10^{12}$\hMsun both in the tidal and velocity
 shear fields where the preferences is to be parallel to the
@@
 walls. Finally, the peculiar velocities show a strong alignment along
-the smallest tidal eigenvector for all halo masses; halos move along filaments
+the smallest tidal eigenvector for all halo masses; haloes move along filaments
 and walls. The same alignment is present with the velocity shear,
-albeit weaker and only for halos less massive than $10^{12}\hMsun$. Our
+albeit weaker and only for haloes less massive than $10^{12}\hMsun$. Our
 results show that the two different algorithms used to
@@
 the time evolution into the deep non-linear regime of virialized
-structures (DM halos) which in turn should host observable
+structures (DM haloes) which in turn should host observable
 galaxies to study their evolution in the cosmic web. The discovery in
@@
 symmetry properties of the local dark matter distribution. With the
-aid of simulations it has been established that halos of a given mass
+aid of simulations it has been established that haloes of a given mass
 form earlier in denser regions; concentration, angular momentum and
@@
 
-\cite{Trowland2013} presented a parameterization for the $\mu$
+\cite{Trowland2013} presented a parametrization for the $\mu$
 distribution in the case of angular momentum alignment based on
-theoretical considerations by \cite{Lee2005} (Eq. \ref{eq:distro} in
-the Appendix A). Under this parameterization a unique
+theoretical considerations by \cite{Lee2005} (equation \ref{eq:distro} in
+Appendix A). Under this parametrization a unique
 correspondence was found between the full shape of the $\vert\mu\vert$
@@
 
-Table 1 and Table 2 summarize recent results found in the literature for
-shape and angular momentum alignment. The Appendix A includes a detailed
+Tables 1 and 2 summarize recent results found in the literature for
+shape and angular momentum alignment. Appendix A includes a detailed
 description of the definitions, algorithms and simulations used in
@@
 \begin{tabular}{cccccc}\hline\hline
-Author & Web Method & Spatial Scale & Along &
+Author & Web method & Spatial scale & Along &
 Alignment & Mass dependence\\
@@
 finder using a linking length of $b=0.17$ times the mean interparticle
-separation. This choice translates into halos with a density of $570$
+separation. This choice translates into haloes with a density of $570$
 times the mean density at $z=0$. The measurements for the shape,
@@
 x_{i,3}^2$, where the positions are measured with respect to the
-center of mass.
+centre of mass.
 
@@
 \end{equation}
-where the velocities are also measured with respect to the center of
+where the velocities are also measured with respect to the centre of
 mass velocity. Finally the peculiar velocity of a halo is computed as
-the center of mass velocity.
-
-The halo and environment used in this paper is publicly available through the
-MultiDark database\footnote{\texttt{http://www.multidark.org/MultiDark/}}. The
+the centre of mass velocity.
+
+The halo and environment used in this paper are publicly available through the
+MultiDark data base\footnote{\texttt{http://www.multidark.org/MultiDark/}}. The
 halo data is thoroughly described in \cite{2013AN....334..691R}.
@@
 For the V-Web we interpolate first the momentum density field over a
-grid using the CIC scheme and then apply a gaussian smoothing with a
+grid using the CIC scheme and then apply a Gaussian smoothing with a
 spatial variance of one grid cell. We use the matter density field,
-which is also CIC interpolated and gaussian smoothed, to normalize the
+which is also CIC interpolated and Gaussian smoothed, to normalize the
 momentum field. This ratio between the momentum and matter density
@@
 We caution the reader that the results reported by
-\citep{Vweb, Libeskind2013} use a velocity field that is
-calculated by a gaussian smoothing of the CIC velocity field without
+\cite{Vweb} and \cite{Libeskind2013} use a velocity field that is
+calculated by a Gaussian smoothing of the CIC velocity field without
 taking into account any weight by mass.
@@
 In this paper we use the data and the methods described above to
-perform two kinds of measurements: the preferential alignment and the
+perform two kinds of measurements: the preferential alignment (PA) and the
 average value of the angle along the eigenvectors of interest.
@@
 $\lambda_{\rm th, VWEB}$ provides clear data to understand the
-connection of DM halos with the cosmic web.
+connection of DM haloes with the cosmic web.
 
@@
 The first measurement is a rough approximation to find out along which
-axes halos are aligned. We refer to this as Preferential Alignment (PA).
+axes haloes are aligned. We refer to this as PA.
 
@@
 %
-Using this we know that all halos can be splitted into three groups:
+Using this we know that all haloes can be split into three groups:
 
 \begin{enumerate}
-\item Halos with $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_2)^2$
+\item Haloes with $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_2)^2$
   and $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_3)^2$, which can
   be considered to aligned mostly along $\hat{e}_1$.
-\item Halos with $(\hat{s}\cdot\hat{e}_2)^2> (\hat{s}\cdot\hat{e}_1)^2$
+\item Haloes with $(\hat{s}\cdot\hat{e}_2)^2> (\hat{s}\cdot\hat{e}_1)^2$
   and $(\hat{s}\cdot\hat{e}_2)^2> (\hat{s}\cdot\hat{e}_3)^2$, which can
   be considered to aligned mostly along $\hat{e}_2$.
-\item Halos with $(\hat{s}\cdot\hat{e}_3)^2> (\hat{s}\cdot\hat{e}_1)^2$
+\item Haloes with $(\hat{s}\cdot\hat{e}_3)^2> (\hat{s}\cdot\hat{e}_1)^2$
   and $(\hat{s}\cdot\hat{e}_3)^2> (\hat{s}\cdot\hat{e}_2)^2$, which can
@@
 
-If the halo population does not show any preferential alignment, then
-all the halos must be evenly distributed along these three
+If the halo population does not show any PA, then
+all the haloes must be evenly distributed along these three
 populations. On the contrary, if there is more than one third of the
 halo population in one of these sets, then this will indicate a
-preferential alignment along one of the axes. However, this statistics
+PA along one of the axes. However, this statistics
 does not give a precise answer on the degree of the alignment
@@
 tests in different populations split into different mass bins
-logarithmically spaced between $1\times 10^{9}$\hMsun and
+logarithmically spaced between $1\times 10^{9}$ and
 $1\times10^{14}$\hMsun.
@@
 triaxiality. In this case we take the upper and lower $30\%$ of the
-halos according to each property and measure the strength of the
+haloes according to each property and measure the strength of the
 alignment by the average value of
@@
 \includegraphics[width=0.8\textwidth]{Fig1.pdf}
-\caption{Fraction of halos in a mass bin that show a preferential
-  alignment with respect to an eigenvector in the cosmic
+\caption{Fraction of haloes in a mass bin that show a PA with respect to an eigenvector in the cosmic
   web; $\hat{e}_1$ (black) defines the direction perpendicular to a wall and
@@
   presents one of the three properties studied in this paper: shape (major axis),
-  angular momentum and  peculiar velocity. The left (right) column presents the
-  results against the V-web (T-web). Strong colors refer to $256^3$ grid
-  resolutions and lighter colors to a $512^3$ grid. The thick black
+  angular momentum and  peculiar velocity. The left-hand (right-hand) column presents the
+  results against the V-web (T-web). Strong colours refer to $256^3$ grid
+  resolutions and lighter colours to a $512^3$ grid. The thick black
   horizontal line at $0.33$ corresponds to the expected fraction for a
-  random vector field. The uncertainty is computed assuming poissonian
+  random vector field. The uncertainty is computed assuming Poissonian
   statistics in each mass bin.
@@
 
-Figure \ref{fig:preferential} presents all the results for the
-preferential alignment (PA) summarizing to a good extent the main
+Fig. \ref{fig:preferential} presents all the results for the
+PA summarizing to a good extent the main
 results of this paper.
 
-The shape alignment and the V-web (upper row, left column) give a
-different perspective. Firstly, there seems to be little evidence
+The shape alignment and the V-web (upper row, left-hand column) give a
+different perspective. First, there seems to be little evidence
 for an alignment for masses below $10^{11}-10^{12}\hMsun$, depending
@@
 
-For shape alignment and the T-web (upper row, right column) we find a strong
-preferential alignment along the third eigenvector $\hat{e}_{3}$. This
+For shape alignment and the T-web (upper row, right-hand column) we
+find a strong PA along the third eigenvector $\hat{e}_{3}$. This  
 signal increases steadily with mass and is almost independent of the
-grid resolution. At high masses between $70\%$ and $100\%$ of the
-halos have their major axis aligned along $\hat{e}_{3}$ which means
+grid resolution. At high masses between $70$ and $100$ per cent of the
+haloes have their major axis aligned along $\hat{e}_{3}$ which means
 that they mostly lie along filaments and sheets.
 
-The angular momentum in the V-web (middle row, left column) presents 
+The angular momentum in the V-web (middle row, left-hand column) presents 
 a signal of alignment along the second eigenvector $\hat{e}_{2}$;
-between $45\%$ to $60\%$ of the halos are aligned along that
-direction, while there is a minority of halos aligned with
+between $45$ to $60$ percent of the haloes are aligned along that
+direction, while there is a minority of haloes aligned with
 $\hat{e}_{1}$.  There is a clear change in trends around
-$10^{11}\hMsun-10^{12}\hMsun$ depending on the grid resolution;
+$10^{11}-10^{12}\hMsun$ depending on the grid resolution;
 below that mass range there is no evidence for alignment while at
 higher masses all the trends we describe are noticeable. This means
-that the angular momentum of halos above $10^{12}\hMsun$ tends to lie
+that the angular momentum of haloes above $10^{12}\hMsun$ tends to lie
 along walls, parallel to the vector $\hat{e}_2$; without any clear
@@
 
-For the angular momentum alignment and the T-web (middle row, right
+For the angular momentum alignment and the T-web (middle row, right-hand
 column) we find no evidence for any alignment at low masses $<10^{12}\hMsun$.
 At higher masses $>10^{12}\hMsun$ there is a weak signal
-of preferential alignment along the first and second eigenvectors;
-between $35\%$ to $45\%$ of the halos are aligned with respect to
+of PA along the first and second eigenvectors;
+between $35$ to $45$ per cent of the haloes are aligned with respect to
 $\hat{e}_1$ and $\hat{e}_2$. Correspondingly, between $10\%$ to $20\%$
-of the halos are aligned along $\hat{e}_{3}$. This means
-that most of the halos are perpendicular to the filaments and do not
+of the haloes are aligned along $\hat{e}_{3}$. This means
+that most of the haloes are perpendicular to the filaments and do not
 have a clear alignment with respect to walls.
@@
 all masses below $10^{13.0}\hMsun-10^{13.5}\hMsun$ depending on the grid
-resolution. $45\%$ of the halos are aligned this way, while only $25\%$ are
+resolution. $45\%$ of the haloes are aligned this way, while only $25\%$ are
 aligned along the first eigenvector $\hat{e}_1$. This suggests that
-halos tend to move along filaments and parallel to the walls, except
+haloes tend to move along filaments and parallel to the walls, except
 at higher masses where the alignments get randomized.  In contrast,
 the peculiar velocities with respect to the V-web show the same,
-although weaker, trend and only for low mass halos $<10^{12}$.
+although weaker, trend and only for low mass haloes $<10^{12}$.
 
@@
 
-Figure \ref{fig:shape_alignment} presents the main results for the
+Fig. \ref{fig:shape_alignment} presents the main results for the
 angles between the first and third eigenvectors and the major shape
@@
 
-In the case of the V-web (left column) we have a clear alignment with
+In the case of the V-web (left-hand column) we have a clear alignment with
 respect to the first eigenvector at high masses $>10^{12}\hMsun$, with
@@
 $<10^{12}\hMsun$ we do not detect any alignment signal. This is
-consistent with the PA results of massive halos
+consistent with the PA results of massive haloes
 perpendicular to filaments and parallel to walls.
 
-The T-web (right column) shows alignment trends starting at masses of
+The T-web (right-hand column) shows alignment trends starting at masses of
 $10^{10}$\hMsun, two orders of magnitude below than the V-web. In this
@@
 0.2$. This strong alignment/anti-alignment signal mirrors the
-interpretation from the PA results that describe halos lying parallel
+interpretation from the PA results that describe haloes lying parallel
 both to filaments and walls.
@@
 
-We now focus our attention on the angular momentum alignment. Figure
+We now focus our attention on the angular momentum alignment. Fig.
 \ref{fig:spin_alignment} shows the results as a function of halo mass
-following the same panel layout as in Figure
+following the same panel layout as in Fig.
 \ref{fig:shape_alignment}. In all cases we see that these alignment
-trends are weaker than the shape alignments. For the V-web low mass halos
-$<10^{12}$\hMsun do not show any preferential alignment with the
-cosmic web. Halos more massive than this threshold have their angular
+trends are weaker than the shape alignments. For the V-web low mass haloes
+$<10^{12}$\hMsun do not show any PA with the
+cosmic web. Haloes more massive than this threshold have their angular
 momentum slightly perpendicular to the direction defined by the first
@@
 
-In the case of the T-web, the alignment for low mass halos $<10^{12}$\hMsun
-is also absent. More massive halos present a weak alignment along
+In the case of the T-web, the alignment for low mass haloes $<10^{12}$\hMsun
+is also absent. More massive haloes present a weak alignment along
 first eigenvector and anti-alignment with the third eigenvector. This
 provides a quantitative expression of the results derived from the
-preferential alignment whereby the angular momentum is weakly
+PA whereby the angular momentum is weakly
 perpendicular to filaments.
@@
 
-Figure \ref{fig:velocity_alignment} shows the results for peculiar
+Fig. \ref{fig:velocity_alignment} shows the results for peculiar
 velocities alignments. In the case of the V-web, the peculiar
@@
 these trends remain basically unchanged at all masses and grid
-resolutions, with only minor changes for halos masses $>10^{13}$\hMsun.
+resolutions, with only minor changes for haloes masses $>10^{13}$\hMsun.
 
@@
 and peculiar velocities. We split the halo population into low and
-high mass halos imposing a cut at $M_{\rm halo}=10^{11}$\hMsun. This
+high mass haloes imposing a cut at $M_{\rm halo}=10^{11}$\hMsun. This
 allows us to have robust statistics on the high mass end. We have also
@@
 volume out to the virial radius). We measure the web alignments in two
-sets, each one including the $30\%$ of halos in the lower/higher end
+sets, each one including the $30\%$ of haloes in the lower/higher end
 of the corresponding property.
 
-Figure \ref{fig:drive} shows the results for the major axes of
+Fig. \ref{fig:drive} shows the results for the major axes of
 the V-web and T-web (left and right panels) and the shape major axis,
@@
 
-Halos with higher circularity and inner density show
+Haloes with higher circularity and inner density show
 a higher alignment with the V-web major axes.  The opposite is the case
 of haloes with higher concentration, spin and triaxiality.  This trend
-is also visible in the angular momentum vs. V-web major axis alignment only
+is also visible in the angular momentum versus V-web major axis alignment only
 for the concentration and spin, with little differences evidenced by the
@@
 
-On the right panels the trends can also be readily seen.  The T-web
-vs. major axis alignments are stronger for higher circularity,
+On the right-hand panels the trends can also be readily seen.  The T-web
+versus major axis alignments are stronger for higher circularity,
 concentration and inner density, and weaker for higher spins and
@@
 spins, and is only strengthened when the triaxiality is higher.
-Not much difference is seen in the T-web vs. halo peculiar velocity
+Not much difference is seen in the T-web versus halo peculiar velocity
 alignments, being this the only regime where there is a clear difference
 in influence of halo properties on the alignments with the T-web and V-web;
-the latter do show important changes on the lower-left panel.
+the latter do show important changes on the lower left-hand panel.
 
@@
 as well as lower spins and triaxialities, produce a similar effect on the
-T-web vs. major axis alignments to that of diminishing the mass
-of the halos.  This has also been detected in other halo properties such
+T-web versus major axis alignments to that of diminishing the mass
+of the haloes.  This has also been detected in other halo properties such
 as their clustering amplitude in what has been termed assembly bias
-\citep[][e.g.]{Gao2005,Li2008,Lacerna2011} where halos of different
+\citep[][e.g.]{Gao2005,Li2008,Lacerna2011} where haloes of different
 ages and equal mass show different clustering amplitudes, which could
@@
 shapes, higher concentrations and halo inner density.  However, in the
-assembly bias scenario of \cite{Gao2005}, these halos tend to show a clustering
+assembly bias scenario of \cite{Gao2005}, these haloes tend to show a clustering
 amplitude consistent with that of the median halo population of higher masses.
@@
   properties: circularity, concentration, halo inner density, spin and
-  triaxiality. Each subsets includes $30\%$ of halos in the lower/higher end of each
+  triaxiality. Each subsets includes $30\%$ of haloes in the lower/higher end of each
   property. The grey band indicates the region around
@@
 \caption{Median of the interweb alignment for the two grid
-  resolutions as a function of the dark matter mass corresponding to
-  the halos where the measurement was made. The error bars indicate
+  resolutions as a function of the DM mass corresponding to
+  the haloes where the measurement was made. The error bars indicate
   the lower and upper quartiles.
@@
 Perhaps the most striking result so far is that the two web algorithms give
-different results for the alignment of massive halos. This is not
+different results for the alignment of massive haloes. This is not
 completely unexpected given that the two algorithms are based on
@@
 We restrict our analysis to the grid cells that are occupied by
-halos. Otherwise, if we decided to perform this kind of analysis on
+haloes. Otherwise, if we decided to perform this kind of analysis on
 all the grid cells, the statistics would be more representative of the void
@@
 
-Figure \ref{fig:interweb} shows the values for $\muavg$ between the
+Fig. \ref{fig:interweb} shows the values for $\muavg$ between the
 two $\hat{e}_1$ eigenvectors in the T-web and the V-web.  The Figure
 shows that there is an alignment, $\muavg\approx 1.0$, for low mass
-halos and an anti-alignment, $\muavg\approx 0.2$ for massive ones.
+haloes and an anti-alignment, $\muavg\approx 0.2$ for massive ones.
 
@@
 
-On the scale where the halos more massive than $10^{13}$\hMsun are
+On the scale where the haloes more massive than $10^{13}$\hMsun are
 located, the relationship between the velocity shear and the tidal
@@
 We have examined the alignment of shape, angular momentum and peculiar
-velocity of dark matter halos with respect to the cosmic web. We use
+velocity of DM haloes with respect to the cosmic web. We use
 publicly available data from two algorithms implemented on a large
@@
 and the second the velocity shear (V-web); both include results on
-spatial scales of $0.5$\hMpc and $1.0$\hMpc.
+spatial scales of $0.5$ and $1.0$\hMpc.
 
 We quantify the alignments in two complementary ways. The first one
-measures the fraction of halos in a population that is preferentially
+measures the fraction of haloes in a population that is preferentially
 aligned with either one of the eigenvectors $\hat{e}_1$, $\hat{e}_2$
@@
 We find that the strongest alignment occurs for the halo shape with
-respect to the T-web. In this case the halos tend to align with the
+respect to the T-web. In this case the haloes tend to align with the
 third eigenvector, $\hat{e}_3$, meaning that they lie along filaments
@@
 increases and agrees with all the results published so far. Instead,
-for the momentum based V-web, there is only an anti-alignment for halos
+for the momentum based V-web, there is only an anti-alignment for haloes
 more massive than $10^{12}\hMsun$, a result that is presented here for
@@
 A much weaker alignment signal is present for the angular momentum. In
-the T-web only the most massive halos $>10^{12}$\hMsun are
+the T-web only the most massive haloes $>10^{12}$\hMsun are
 perpendicular with respect to $\hat{e}_3$ (anti-aligned to filaments),
-while for the V-web the massive halos are aligned with $\hat{e}_2$,
+while for the V-web the massive haloes are aligned with $\hat{e}_2$,
 lying along sheets. These results broadly agree with the
@@
 alignment for low mass haloes with the structure on small scales, and
-an anti-alighment at large scales (the 2-halo term). The diversity of
+an anti-alignment at large scales (the two-halo term). The diversity of
 results could be then interpreted as a high sensitivity of the
@@
 a flow parallel to walls and filaments. In the case of the V-web
-similar signal, albeit weaker, is present only for the low mass halos
+similar signal, albeit weaker, is present only for the low mass haloes
 $<10^{12}\hMsun$. A similar result was obtained by \citep{Padilla2005}
@@
 
-The different behaviour for the alignments of massive halos in the
+The different behaviour for the alignments of massive haloes in the
 T-web and the V-web is explained by an anti-alignment between the
-eigenvectors in the two web grids for massive halos
-$>10^{12}\hMsun$. For low mass halos the directions defined by the two
+eigenvectors in the two web grids for massive haloes
+$>10^{12}\hMsun$. For low mass haloes the directions defined by the two
 webs point in the same direction. This trends can be interpreted as
@@
 other than mass, in driving the alignments. We find that in the case of
-shape, high concentration halos or halos with a low value of
+shape, high concentration haloes or haloes with a low value of
 the reduced spin parameter tend to show a stronger signal. This trend is
 more pronounced in the T-web than in the V-web. Concerning angular
-momentum we find that the anti-alignment signal is stronger for halos
+momentum we find that the anti-alignment signal is stronger for haloes
 with high spin values. In the peculiar velocities we do not find any
@@
 
-Our study has shown that the alignment properties of dark matter
-halos depend on the physical definition of the cosmic web. This shows
+Our study has shown that the alignment properties of DM
+haloes depend on the physical definition of the cosmic web. This shows
 that the main aspect of non-linear gravitational collapse might be
 revealed easily depending on the choice of the physical context
-(e.g. tidal field vs. velocity shear). There is not a better method,
+(e.g. tidal field versus velocity shear). There is not a better method,
 but different perspectives. In future work we will explore the
@@
 
-\section*{Acknowledgments}
-
-J.E.F-R acknowledges the financial support by Vicerrector\'ia de
+\section*{Acknowledgements}
+
+JEF-R acknowledges the financial support by Vicerrector\'ia de
 Investigaciones at Universidad de los Andes through a FAPA grant.
 NP acknowledges support by Fondecyt Regular No. 1110328 and BASAL PFB-06 "Centro de Astronomia y Tecnologias Afines".
-S.C. acknowledges support from a PhD Fellowship from CONICYT
-N.P. and S.C. acknowledge support by the European Commissions Framework
+SC acknowledges support from a PhD Fellowship from CONICYT
+NP and SC acknowledge support by the European Commissions Framework
 Programme 7, through the Marie Curie International Research Staff
-Exchange Scheme LACEGAL (PIRSES-GA-2010-269264). N.P. thanks the
+Exchange Scheme LACEGAL (PIRSES-GA-2010-269264). NP thanks the
 hospitality of the Max Planck Institute for Astrophysics at Garching
@@
 
-We thank Kristin Riebe for her work to make the cosmic web data available in the Multidark database.
+We thank Kristin Riebe for her work to make the cosmic web data
+available in the Multidark data base.
 
@@
 $M_{\rm  vir}>12^{12.5}\hMsun$. The identification of the cosmic web
-is done on a grid of $256^3$ with a gaussian smoothing of $\sim
+is done on a grid of $256^3$ with a Gaussian smoothing of $\sim
 1$\hMpc over the velocity field. The way they compute this smoothed
@@
 eigenvector corresponding to the smallest eigenvalue is aligned with
-the major axis. This effect is stronger for more massive halos.  In
+the major axis. This effect is stronger for more massive haloes.  In
 other words the major axis of a halo is aligned with a filament, and
 lies on the plane that define a sheet. The angular momentum is
-anti-aligned with the filament for massive halos and weakly aligned
-for low mass halos.
+anti-aligned with the filament for massive haloes and weakly aligned
+for low mass haloes.
 
@@
 of $500$\hMpc on a side. This corresponds to a particle mass of
-$8.6\times 10^{8}$\hMsun. The catalog uses both halos and subhalos
-identified with SUBFIND. Only halos with more than 500 particles were
+$8.6\times 10^{8}$\hMsun. The catalog uses both haloes and subhaloes
+identified with SUBFIND. Only haloes with more than 500 particles were
 kept to get a robust computation for the spin. The angular momentum is
 defined as the sum of the angular momentum of each particle with
-respect to the center of mass.
+respect to the centre of mass.
 
@@
 eigenvalues of the hessian of the density.  However, the analysis is
-performed on a box of $300$\hMpc on a side. Four different gaussian
+performed on a box of $300$\hMpc on a side. Four different Gaussian
 smoothing scales are used: $2.0$, $3.0$ and $5.0$\hMpc.
@@
 
-When the halo sample is divided between low mass and high mass halos
+When the halo sample is divided between low mass and high mass haloes
 with a transition scale $M_{\star}=5.9\times 10^{12}$\Msun, there is
 a weak alignment signal of the angular momentum against the
-principal filament axis for halos above that mass, for halos below
+principal filament axis for haloes above that mass, for haloes below
 that scale there is a weak anti-alignment.
@@
 cubic periodic box of $2000$\hMpc on a side, which corresponds to a
-particle mass of $7.7\times 10^9$\Msun. Halos are identified
-using a FoF algorithm with a linking length of 0.2 keeping all halos
+particle mass of $7.7\times 10^9$\Msun. Haloes are identified
+using a FoF algorithm with a linking length of 0.2 keeping all haloes
 with more than 40 particles, which sets the minimum halo mass to be
 $3\times 10^{11}$\Msun. In their work the particles were sampled on a
-$2048^3$ grid and the density field was smoothed with a gaussian
+$2048^3$ grid and the density field was smoothed with a Gaussian
 fileter over a scale of $5$\hMpc corresponding to a mass of $1.9\times
@@
 The angular momentum of the halo is defined as $m_{p}\sum_{i}(r_i-\bar{r})\times
-(v_i-\bar{v})$ where $\bar{r}$ is the center of mass of the halo and
+(v_i-\bar{v})$ where $\bar{r}$ is the centre of mass of the halo and
 $\bar{v}$ is the average velocity.
@@
 algorithm with a linking length of 0.2 times the interparticle
-distance. Only halos with more than 500 particles are retained for
+distance. Only haloes with more than 500 particles are retained for
 further analysis. The angular momentum is measured with positions
-repect to the center of mass and the shape is determined using the
+repect to the centre of mass and the shape is determined using the
 non-normalized moment of inertia tensor.
@@
 eigenvalue of the hessian. The second method used a line that
-connects the two terminal halos in a filament segment.
+connects the two terminal haloes in a filament segment.
 
@@
 filament. The find an alignment signal in all mass bins, with an
-stronger effect for more massive halos.
+stronger effect for more massive haloes.
 
@@
 different samples split by the strength of the shape alignment. They
-find that halos anti-aligned in shape, show a strong angular momentum
-correlation; and a strong angular momentum anti-alignment for halos
+find that haloes anti-aligned in shape, show a strong angular momentum
+correlation; and a strong angular momentum anti-alignment for haloes
 with a strong shape alignment.
@@
 mass per particle is $2\times 10^{9}$\hMsun.  Halo identitification is
-done with the HOP algorithm. They keep halos with more than $50$
+done with the HOP algorithm. They keep haloes with more than $50$
 particles and less than $5000$, defining a mass range of$1-100\times
@@
 non-normalized inertia tensor. The inertia tensor and the angular
-momentum are computed with respect to the center of mass of the halo.
+momentum are computed with respect to the centre of mass of the halo.
 
@@
 defining the filaments and the other the walls. Their results make a
-distinction between halos of more massive and less massive than
+distinction between haloes of more massive and less massive than
 $10^{12}$\hMsun. The angular momentum tends to lie along the plane of
-the wall, with a stronger alignment for massive halos. The effect for
-filaments is weaker, low mass halos tend to align along the filament,
-while high mass halos tend to be anti-aligned.
+the wall, with a stronger alignment for massive haloes. The effect for
+filaments is weaker, low mass haloes tend to align along the filament,
+while high mass haloes tend to be anti-aligned.
 
@@
 walls the major axis lies along the wall. Both alignments are stronger
-for massive halos.
+for massive haloes.
 
@@
 algorithm with 0.2 times the interparticle distance. They considered
-halos of at least 300  particles.
+haloes of at least 300  particles.
 
@@
 \bibliographystyle{mn2e}
-\bibliography{references}
+%\bibliography{references}
+\begin{thebibliography}{}
+
+\bibitem[\protect\citeauthoryear{{Abbas} \& {Sheth}}{{Abbas} \&
+  {Sheth}}{2006}]{Abbas2006}
+{Abbas} U.,  {Sheth} R.~K.,  2006, \mnras, 372, 1749
+
+\bibitem[\protect\citeauthoryear{{Arag{\'o}n-Calvo}, {van de Weygaert}, {Jones}
+  \& {van der Hulst}}{{Arag{\'o}n-Calvo} et~al.}{2007}]{AragonCalvo2007}
+{Arag{\'o}n-Calvo} M.~A.,  {van de Weygaert} R.,  {Jones} B.~J.~T.,    {van der
+  Hulst} J.~M.,  2007, \apjl, 655, L5
+
+\bibitem[\protect\citeauthoryear{{Arag{\'o}n-Calvo} \&
+  {Yang}}{{Arag{\'o}n-Calvo} \& {Yang}}{2014}]{AragonCalvo2014}
+{Arag{\'o}n-Calvo} M.~A.,  {Yang} L.~F.,  2014, \mnras, 440, L46
+
+\bibitem[\protect\citeauthoryear{{Baldry}, {Balogh}, {Bower}, {Glazebrook},
+  {Nichol}, {Bamford} \& {Budavari}}{{Baldry} et~al.}{2006}]{Baldry2006}
+{Baldry} I.~K.,  {Balogh} M.~L.,  {Bower} R.~G.,  {Glazebrook} K.,  {Nichol}
+  R.~C.,  {Bamford} S.~P.,    {Budavari} T.,  2006, \mnras, 373, 469
+
+\bibitem[\protect\citeauthoryear{{Basilakos}, {Plionis}, {Yepes},
+  {Gottl{\"o}ber} \& {Turchaninov}}{{Basilakos} et~al.}{2006}]{Basilakos2006}
+{Basilakos} S.,  {Plionis} M.,  {Yepes} G.,  {Gottl{\"o}ber} S.,
+  {Turchaninov} V.,  2006, \mnras, 365, 539
+
+\bibitem[\protect\citeauthoryear{{Bond}, {Kofman} \& {Pogosyan}}{{Bond}
+  et~al.}{1996}]{Bond1996}
+{Bond} J.~R.,  {Kofman} L.,    {Pogosyan} D.,  1996, \nat, 380, 603
+
+\bibitem[\protect\citeauthoryear{{Codis}, {Pichon}, {Devriendt}, {Slyz},
+  {Pogosyan}, {Dubois} \& {Sousbie}}{{Codis} et~al.}{2012}]{Codis2012}
+{Codis} S.,  {Pichon} C.,  {Devriendt} J.,  {Slyz} A.,  {Pogosyan} D.,
+  {Dubois} Y.,    {Sousbie} T.,  2012, \mnras, 427, 3320
+
+\bibitem[\protect\citeauthoryear{{Colberg}, {Krughoff} \& {Connolly}}{{Colberg}
+  et~al.}{2005}]{Colberg2005}
+{Colberg} J.~M.,  {Krughoff} K.~S.,    {Connolly} A.~J.,  2005, \mnras, 359,
+  272
+
+\bibitem[\protect\citeauthoryear{{Courtois}, {Hoffman}, {Tully} \&
+  {Gottl{\"o}ber}}{{Courtois} et~al.}{2012}]{Courtois2012}
+{Courtois} H.~M.,  {Hoffman} Y.,  {Tully} R.~B.,    {Gottl{\"o}ber} S.,  2012,
+  \apj, 744, 43
+
+\bibitem[\protect\citeauthoryear{{Dekel}, {Birnboim}, {Engel}, {Freundlich},
+  {Goerdt}, {Mumcuoglu}, {Neistein}, {Pichon}, {Teyssier} \& {Zinger}}{{Dekel}
+  et~al.}{2009}]{Dekel2009}
+{Dekel} A.,  {Birnboim} Y.,  {Engel} G.,  {Freundlich} J.,  {Goerdt} T.,
+  {Mumcuoglu} M.,  {Neistein} E.,  {Pichon} C.,  {Teyssier} R.,    {Zinger} E.,
+   2009, \nat, 457, 451
+
+\bibitem[\protect\citeauthoryear{{Dressler}}{{Dressler}}{1980}]{Dressler1980}
+{Dressler} A.,  1980, \apj, 236, 351
+
+\bibitem[\protect\citeauthoryear{{Dunkley}, {Komatsu}, {Nolta}, {Spergel},
+  {Larson}, {Hinshaw}, {Page}, {Bennett}, {Gold}, {Jarosik}, {Weiland},
+  {Halpern}, {Hill}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack} \&
+  {Wright}}{{Dunkley} et~al.}{2009}]{2009ApJS..180..306D}
+{Dunkley} J.,  {Komatsu} E.,  {Nolta} M.~R.,  {Spergel} D.~N.,  {Larson} D.,
+  {Hinshaw} G.,  {Page} L.,  {Bennett} C.~L.,  {Gold} B.,  {Jarosik} N.,
+  {Weiland} J.~L.,  {Halpern} M.,  {Hill} R.~S.,  {Kogut} A.,  {Limon} M.,
+  {Meyer} S.~S.,  {Tucker} G.~S.,  {Wollack} E.,    {Wright} E.~L.,  2009,
+  \apjs, 180, 306
+
+\bibitem[\protect\citeauthoryear{{Faltenbacher}, {Li}, {White}, {Jing},
+  {Shu-DeMao} \& {Wang}}{{Faltenbacher} et~al.}{2009}]{Faltenbacher2009}
+{Faltenbacher} A.,  {Li} C.,  {White} S.~D.~M.,  {Jing} Y.-P.,  {Shu-DeMao}
+  {Wang} J.,  2009, Research in Astronomy and Astrophysics, 9, 41
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Hoffman}, {Gottl{\"o}ber},
+  {Klypin} \& {Yepes}}{{Forero-Romero} et~al.}{2009}]{Tweb}
+{Forero-Romero} J.~E.,  {Hoffman} Y.,  {Gottl{\"o}ber} S.,  {Klypin} A.,
+  {Yepes} G.,  2009, \mnras, 396, 1815
+
+\bibitem[\protect\citeauthoryear{{Gao}, {Springel} \& {White}}{{Gao}
+  et~al.}{2005}]{Gao2005}
+{Gao} L.,  {Springel} V.,    {White} S.~D.~M.,  2005, \mnras, 363, L66
+
+\bibitem[\protect\citeauthoryear{{G{\'o}mez}, {Nichol}, {Miller}, {Balogh},
+  {Goto}, {Zabludoff}, {Romer}, {Bernardi}, {Sheth}, {Hopkins}, {Castander},
+  {Connolly}, {Schneider}, {Brinkmann}, {Lamb}, {SubbaRao} \&
+  {York}}{{G{\'o}mez} et~al.}{2003}]{Gomez2003}
+{G{\'o}mez} P.~L.,  {Nichol} R.~C.,  {Miller} C.~J.,  {Balogh} M.~L.,  {Goto}
+  T.,  {Zabludoff} A.~I.,  {Romer} A.~K.,  {Bernardi} M.,  {Sheth} R.,
+  {Hopkins} A.~M.,  {Castander} F.~J.,  {Connolly} A.~J.,  {Schneider} D.~P.,
+  {Brinkmann} J.,  {Lamb} D.~Q.,  {SubbaRao} M.,    {York} D.~G.,  2003, \apj,
+  584, 210
+
+\bibitem[\protect\citeauthoryear{{Gonz{\'a}lez} \& {Padilla}}{{Gonz{\'a}lez} \&
+  {Padilla}}{2009}]{Gonzalez2009}
+{Gonz{\'a}lez} R.~E.,  {Padilla} N.~D.,  2009, \mnras, 397, 1498
+
+\bibitem[\protect\citeauthoryear{{Gonz{\'a}lez} \& {Padilla}}{{Gonz{\'a}lez} \&
+  {Padilla}}{2010}]{Gonzalez2010}
+{Gonz{\'a}lez} R.~E.,  {Padilla} N.~D.,  2010, \mnras, 407, 1449
+
+\bibitem[\protect\citeauthoryear{{Hahn}, {Carollo}, {Porciani} \&
+  {Dekel}}{{Hahn} et~al.}{2007}]{Hahn2007}
+{Hahn} O.,  {Carollo} C.~M.,  {Porciani} C.,    {Dekel} A.,  2007, \mnras, 381,
+  41
+
+\bibitem[\protect\citeauthoryear{{Hinshaw}, {Larson}, {Komatsu}, {Spergel},
+  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page} \&
+  {Smith}}{{Hinshaw} et~al.}{2013}]{2013ApJS..208...19H}
+{Hinshaw} G.,  {Larson} D.,  {Komatsu} E.,  {Spergel} D.~N.,  {Bennett} C.~L.,
+  {Dunkley} J.,  {Nolta} M.~R.,  {Halpern} M.,  {Hill} R.~S.,  {Odegard} N.,
+  {Page} L.,    {Smith} K.~M.,  2013, \apjs, 208, 19
+
+\bibitem[\protect\citeauthoryear{{Hoffman}, {Metuki}, {Yepes}, {Gottl{\"o}ber},
+  {Forero-Romero}, {Libeskind} \& {Knebe}}{{Hoffman} et~al.}{2012}]{Vweb}
+{Hoffman} Y.,  {Metuki} O.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Forero-Romero}
+  J.~E.,  {Libeskind} N.~I.,    {Knebe} A.,  2012, \mnras, 425, 2049
+
+\bibitem[\protect\citeauthoryear{{Jones}, {van de Weygaert} \&
+  {Arag{\'o}n-Calvo}}{{Jones} et~al.}{2010}]{Jones2010}
+{Jones} B.~J.~T.,  {van de Weygaert} R.,    {Arag{\'o}n-Calvo} M.~A.,  2010,
+  \mnras, 408, 897
+
+\bibitem[\protect\citeauthoryear{{Kauffmann}, {White}, {Heckman}, {M{\'e}nard},
+  {Brinchmann}, {Charlot}, {Tremonti} \& {Brinkmann}}{{Kauffmann}
+  et~al.}{2004}]{Kauffmann2004}
+{Kauffmann} G.,  {White} S.~D.~M.,  {Heckman} T.~M.,  {M{\'e}nard} B.,
+  {Brinchmann} J.,  {Charlot} S.,  {Tremonti} C.,    {Brinkmann} J.,  2004,
+  \mnras, 353, 713
+
+\bibitem[\protect\citeauthoryear{{Klypin}, {Trujillo-Gomez} \&
+  {Primack}}{{Klypin} et~al.}{2011}]{2011ApJ...740..102K}
+{Klypin} A.~A.,  {Trujillo-Gomez} S.,    {Primack} J.,  2011, \apj, 740, 102
+
+\bibitem[\protect\citeauthoryear{{Lacerna} \& {Padilla}}{{Lacerna} \&
+  {Padilla}}{2011}]{Lacerna2011}
+{Lacerna} I.,  {Padilla} N.,  2011, \mnras, 412, 1283
+
+\bibitem[\protect\citeauthoryear{{Lee} \& {Erdogdu}}{{Lee} \&
+  {Erdogdu}}{2007}]{Lee2007}
+{Lee} J.,  {Erdogdu} P.,  2007, \apj, 671, 1248
+
+\bibitem[\protect\citeauthoryear{{Lee}, {Kang} \& {Jing}}{{Lee}
+  et~al.}{2005}]{Lee2005}
+{Lee} J.,  {Kang} X.,    {Jing} Y.~P.,  2005, \apjl, 629, L5
+
+\bibitem[\protect\citeauthoryear{{Lee} \& {Pen}}{{Lee} \&
+  {Pen}}{2002}]{Lee2002}
+{Lee} J.,  {Pen} U.-L.,  2002, \apjl, 567, L111
+
+\bibitem[\protect\citeauthoryear{{Li}, {Mo} \& {Gao}}{{Li}
+  et~al.}{2008}]{Li2008}
+{Li} Y.,  {Mo} H.~J.,    {Gao} L.,  2008, \mnras, 389, 1419
+
+\bibitem[\protect\citeauthoryear{{Libeskind}, {Hoffman}, {Forero-Romero},
+  {Gottl{\"o}ber}, {Knebe}, {Steinmetz} \& {Klypin}}{{Libeskind}
+  et~al.}{2013}]{Libeskind2013}
+{Libeskind} N.~I.,  {Hoffman} Y.,  {Forero-Romero} J.,  {Gottl{\"o}ber} S.,
+  {Knebe} A.,  {Steinmetz} M.,    {Klypin} A.,  2013, \mnras, 428, 2489
+
+\bibitem[\protect\citeauthoryear{{Libeskind}, {Hoffman}, {Steinmetz},
+  {Gottl{\"o}ber}, {Knebe} \& {Hess}}{{Libeskind}
+  et~al.}{2013}]{LibeskindVorticity}
+{Libeskind} N.~I.,  {Hoffman} Y.,  {Steinmetz} M.,  {Gottl{\"o}ber} S.,
+  {Knebe} A.,    {Hess} S.,  2013, \apjl, 766, L15
+
+\bibitem[\protect\citeauthoryear{{Mu{\~n}oz-Cuartas}, {M{\"u}ller} \&
+  {Forero-Romero}}{{Mu{\~n}oz-Cuartas} et~al.}{2011}]{MunozCuartas2011}
+{Mu{\~n}oz-Cuartas} J.~C.,  {M{\"u}ller} V.,    {Forero-Romero} J.~E.,  2011,
+  \mnras, 417, 1303
+
+\bibitem[\protect\citeauthoryear{{Muldrew}, {Croton}, {Skibba}, {Pearce},
+  {Ann}, {Baldry}, {Brough}, {Choi}, {Conselice}, {Cowan}, {Gallazzi}, {Gray}
+  \& {Gr{\"u}tzbauch}}{{Muldrew} et~al.}{2012}]{Muldrew2012}
+{Muldrew} S.~I.,  {Croton} D.~J.,  {Skibba} R.~A.,  {Pearce} F.~R.,  {Ann}
+  H.~B.,  {Baldry} I.~K.,  {Brough} S.,  {Choi} Y.-Y.,  {Conselice} C.~J.,
+  {Cowan} N.~B.,  {Gallazzi} A.,  {Gray} M.~E.,    {Gr{\"u}tzbauch} R.,  2012,
+  \mnras, 419, 2670
+
+\bibitem[\protect\citeauthoryear{{Noh} \& {Cohn}}{{Noh} \&
+  {Cohn}}{2011}]{Noh2011}
+{Noh} Y.,  {Cohn} J.~D.,  2011, \mnras, 413, 301
+
+\bibitem[\protect\citeauthoryear{{Nusser}, {Branchini} \& {Davis}}{{Nusser}
+  et~al.}{2011}]{Nusser2011}
+{Nusser} A.,  {Branchini} E.,    {Davis} M.,  2011, \apj, 735, 77
+
+\bibitem[\protect\citeauthoryear{{Ocvirk}, {Pichon} \& {Teyssier}}{{Ocvirk}
+  et~al.}{2008}]{Ocvirk2008}
+{Ocvirk} P.,  {Pichon} C.,    {Teyssier} R.,  2008, \mnras, 390, 1326
+
+\bibitem[\protect\citeauthoryear{{Oemler} Jr.}{{Oemler}}{1974}]{Oemler1974}
+{Oemler} Jr. A.,  1974, \apj, 194, 1
+
+\bibitem[\protect\citeauthoryear{{O'Mill}, {Padilla} \& {Garc{\'{\i}}a
+  Lambas}}{{O'Mill} et~al.}{2008}]{OMill2008}
+{O'Mill} A.~L.,  {Padilla} N.,    {Garc{\'{\i}}a Lambas} D.,  2008, \mnras,
+  389, 1763
+
+\bibitem[\protect\citeauthoryear{{Padilla}, {Lambas} \&
+  {Gonz{\'a}lez}}{{Padilla} et~al.}{2010}]{Padilla2010}
+{Padilla} N.,  {Lambas} D.~G.,    {Gonz{\'a}lez} R.,  2010, \mnras, 409, 936
+
+\bibitem[\protect\citeauthoryear{{Padilla}, {Ceccarelli} \& {Lambas}}{{Padilla}
+  et~al.}{2005}]{Padilla2005}
+{Padilla} N.~D.,  {Ceccarelli} L.,    {Lambas} D.~G.,  2005, \mnras, 363, 977
+
+\bibitem[\protect\citeauthoryear{{Park}, {Choi}, {Vogeley}, {Gott} III,
+  {Blanton} \& {SDSS Collaboration}}{{Park} et~al.}{2007}]{Park2007}
+{Park} C.,  {Choi} Y.-Y.,  {Vogeley} M.~S.,  {Gott} III J.~R.,  {Blanton}
+  M.~R.,    {SDSS Collaboration} 2007, \apj, 658, 898
+
+\bibitem[\protect\citeauthoryear{{Paz}, {Sgr{\'o}}, {Merch{\'a}n} \&
+  {Padilla}}{{Paz} et~al.}{2011}]{Paz2010}
+{Paz} D.~J.,  {Sgr{\'o}} M.~A.,  {Merch{\'a}n} M.,    {Padilla} N.,  2011,
+  \mnras, 414, 2029
+
+\bibitem[\protect\citeauthoryear{{Paz}, {Stasyszyn} \& {Padilla}}{{Paz}
+  et~al.}{2008}]{Paz2008}
+{Paz} D.~J.,  {Stasyszyn} F.,    {Padilla} N.~D.,  2008, \mnras, 389, 1127
+
+\bibitem[\protect\citeauthoryear{{Pimbblet}, {Smail}, {Kodama}, {Couch},
+  {Edge}, {Zabludoff} \& {O'Hely}}{{Pimbblet} et~al.}{2002}]{Pimbblet2002}
+{Pimbblet} K.~A.,  {Smail} I.,  {Kodama} T.,  {Couch} W.~J.,  {Edge} A.~C.,
+  {Zabludoff} A.~I.,    {O'Hely} E.,  2002, \mnras, 331, 333
+
+\bibitem[\protect\citeauthoryear{{Riebe}, {Partl}, {Enke}, {Forero-Romero},
+  {Gottl{\"o}ber}, {Klypin}, {Lemson}, {Prada}, {Primack}, {Steinmetz} \&
+  {Turchaninov}}{{Riebe} et~al.}{2013}]{2013AN....334..691R}
+{Riebe} K.,  {Partl} A.~M.,  {Enke} H.,  {Forero-Romero} J.,  {Gottl{\"o}ber}
+  S.,  {Klypin} A.,  {Lemson} G.,  {Prada} F.,  {Primack} J.~R.,  {Steinmetz}
+  M.,    {Turchaninov} V.,  2013, Astronomische Nachrichten, 334, 691
+
+\bibitem[\protect\citeauthoryear{{Sousbie}, {Pichon}, {Colombi}, {Novikov} \&
+  {Pogosyan}}{{Sousbie} et~al.}{2008}]{Sousbie2008b}
+{Sousbie} T.,  {Pichon} C.,  {Colombi} S.,  {Novikov} D.,    {Pogosyan} D.,
+  2008, \mnras, 383, 1655
+
+\bibitem[\protect\citeauthoryear{{Sousbie}, {Pichon}, {Courtois}, {Colombi} \&
+  {Novikov}}{{Sousbie} et~al.}{2008}]{Sousbie2008}
+{Sousbie} T.,  {Pichon} C.,  {Courtois} H.,  {Colombi} S.,    {Novikov} D.,
+  2008, \apjl, 672, L1
+
+\bibitem[\protect\citeauthoryear{{Tempel}, {Stoica}, {Mart{\'{\i}}nez},
+  {Liivam{\"a}gi}, {Castellan} \& {Saar}}{{Tempel} et~al.}{2014}]{Tempel2014}
+{Tempel} E.,  {Stoica} R.~S.,  {Mart{\'{\i}}nez} V.~J.,  {Liivam{\"a}gi} L.~J.,
+   {Castellan} G.,    {Saar} E.,  2014, \mnras, 438, 3465
+
+\bibitem[\protect\citeauthoryear{{Trowland}, {Lewis} \&
+  {Bland-Hawthorn}}{{Trowland} et~al.}{2013}]{Trowland2013}
+{Trowland} H.~E.,  {Lewis} G.~F.,    {Bland-Hawthorn} J.,  2013, \apj, 762, 72
+
+\bibitem[\protect\citeauthoryear{{Tully}, {Courtois}, {Dolphin}, {Fisher},
+  {H{\'e}raudeau}, {Jacobs}, {Karachentsev}, {Makarov}, {Makarova},
+  {Mitronova}, {Rizzi}, {Shaya}, {Sorce} \& {Wu}}{{Tully}
+  et~al.}{2013}]{Tully2013}
+{Tully} R.~B.,  {Courtois} H.~M.,  {Dolphin} A.~E.,  {Fisher} J.~R.,
+  {H{\'e}raudeau} P.,  {Jacobs} B.~A.,  {Karachentsev} I.~D.,  {Makarov} D.,
+  {Makarova} L.,  {Mitronova} S.,  {Rizzi} L.,  {Shaya} E.~J.,  {Sorce} J.~G.,
+    {Wu} P.-F.,  2013, \aj, 146, 86
+
+\bibitem[\protect\citeauthoryear{{Wang}, {Szalay}, {Arag{\'o}n-Calvo},
+  {Neyrinck} \& {Eyink}}{{Wang} et~al.}{2013}]{Wang2013}
+{Wang} X.,  {Szalay} A.,  {Arag{\'o}n-Calvo} M.~A.,  {Neyrinck} M.~C.,
+  {Eyink} G.~L.,  2013, ArXiv e-prints
+
+\bibitem[\protect\citeauthoryear{{Wilman}, {Zibetti} \&
+  {Budav{\'a}ri}}{{Wilman} et~al.}{2010}]{Wilman2010}
+{Wilman} D.~J.,  {Zibetti} S.,    {Budav{\'a}ri} T.,  2010, \mnras, 406, 1701
+
+\bibitem[\protect\citeauthoryear{{Zhang}, {Yang}, {Faltenbacher}, {Springel},
+  {Lin} \& {Wang}}{{Zhang} et~al.}{2009}]{Zhang2009}
+{Zhang} Y.,  {Yang} X.,  {Faltenbacher} A.,  {Springel} V.,  {Lin} W.,
+  {Wang} H.,  2009, \apj, 706, 747
+
+\end{thebibliography}
 
